---
title: "Coding example chapter 4"
output:
  html_document:
    df_print: paged
date: "2024-07-19"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bayesian Inference for Linear Models

## Example: Normal Linear Model for Mental Impairment

Data from a study with a random sample of adults from a county in
Florida in the U.S., that investigated the relationship between certain
mental health indices and several explanatory variables.

The response variable is an index of mental impairment, which
incorporates various dimensions of psychiatric symptoms, including
aspects of anxiety and depression. This measure ranged from 17 to 41 for
the 40 observations in the data file, with $\overline{y} = 27.30$ and
$s_{y} = 5.46$. The explanatory variables are $x_1$ = life events score
and $x_2$ = socioeconomic status (SES). The life events score is a
composite measure of both the number and severity of life events the
subject experienced within the past three years, such as a death in the
family or divorce or losing a job or moving. It ranged from 3 to 97 in
the sample, with $\overline{x}_{1} = 44.42$ and $s_{x_{1}} = 22.62$. SES
is a composite index based on occupation, income, and education. It
ranged from 0 to 100, with $\overline{x}_{2} = 56.60$ and
$s_{x_{2}} = 25.28$.

\thispagestyle{plain}

In the table: Part of {\bf Mental} data file at the text website with
$y =$ mental impairment, $x_1 =$ life events, and $x_2 =$ socioeconomic
status (ses).

\begin{table}[ht] 
\begin{center}
\small{
\begin{tabular}{ccccccccccc}\hline
impair & life & ses &  & impair & life & ses & & impair & life & ses  \\ \hline
17 & 46 & 84 &  & 26 & 50 & 40 &  & 30 & 44 & 53 \\ 
19 & 39 & 97 &  & 26 & 48 & 52 &  & 31 & 35 & 38 \\ 
20 & 27 & 24 &  & 26 & 45 & 61 &  & 31 & 95 & 29 \\ 
\hline
\end{tabular}}
\end{center}
\end{table}

```{r}
 Mental <- read.table("http://stat4ds.rwth-aachen.de/data/Mental.dat", header=TRUE)
 Mental

 pairs(~impair + life + ses, data=Mental) # scatterplot matrix for pairs (not shown)
 cor(cbind(Mental$impair, Mental$life, Mental$ses)) # correlation matrix

 summary(lm(impair ~ life + ses, data=Mental)) # least squares fit of linear model (lm)
  # estimate of sigma = error std. dev.


```

The least-squares prediction equation is
$\hat{\mu}_{i} = 28.230 + 0.103x_{i1} - 0.097x_{i2}$. The $F$ statistic
for testing $H_0$: $\beta_1 = \beta_2 = 0$ is 9.495 with $df_1 = 2$ and
$df_2 = 37$, giving a $P$-value of 0.0005. The evidence is very strong
that at least one explanatory variable is associated with mental
impairment, although the overall predictive power summarized by the
adjusted $R^2 = 0.30$ is modest. The individual $t$ statistics of 3.18
and $-3.35$ with their $P$-values of 0.003 and 0.002 provide strong
evidence that each explanatory variable has an effect on mental
impairment, life events a positive effect and SES a negative effect,
adjusting for the other variable.

## Example: Bayesian Linear Model for Mental Impairment

To obtain a Bayesian fit of the model that is similar to the least
squares fit of the linear model, we select highly disperse
$\mathcal{N}(0, 100^2)$ prior distributions for $\{\beta_{j}\}$, which
resemble the uniform distribution over the region in which the
likelihood function mainly concentrates. The frequentist estimate of
$\sigma$ is 4.6, and we use an exponential prior distribution for
$\sigma$ with rate 0.01 (mean = standard deviation 100), which
practically contains little information and does not differ much from a
uniform distribution over the relevant region of $\sigma$ values. To
implement the Bayesian fit, we use the {\bf brms} package:

```{r}
 Mental <- read.table("http://stat4ds.rwth-aachen.de/data/Mental.dat", header=TRUE)
 library(brms)
 fit.bayes <- brm(
   impair ~ life + ses, data=Mental, family=gaussian,
   prior = prior(normal(0,100),class=Intercept)+prior(normal(0.2,0.1),class=b,coef=life)+
   prior(normal(-0.2,0.1),class=b,coef=ses) + prior(exponential(0.01),class=sigma)
 )
 print(fit.bayes, digits=3)
 # mean of posterior dist. of sigma is 4.716 
 beta1 <- as_draws_df(fit.bayes)$b_life   # values from posterior dist. of beta1
 beta2 <- as_draws_df(fit.bayes)$b_ses    # values from posterior dist. of beta2
 mean(beta1 <= 0); mean(beta2 >= 0)

 plot(fit.bayes) # plots posterior distributions 
 hist(beta1)     # histogram of posterior distribution of life events effect
 hist(beta1, freq=FALSE, main = "", xlab = expression(beta[1]), ylab = "Density")
                          # histogram of posterior distribution of life events effect
 dens1 <- density(beta1) # smoothed posterior distribution added on the histogram plot
 lines(dens1, lwd=2, lty=1)

```

```{r}
 hist(beta2)
 hist(beta2, freq=FALSE, main = "", xlab = expression(beta[2]), ylab = "")
                          # histogram of posterior distribution of ses effects
 dens2 <- density(beta2) # smoothed posterior distribution added on the histogram plot
 lines(dens2, lwd=2, lty=1)
```

We illustrate the analysis of separate partial effects by investigating
the effect of life events. The {\bf R} output shows a posterior interval
(0.04, 0.17) having probability 0.95. Adjusting for SES, the posterior
probability is 0.95 that the change in mean mental impairment per
one-unit increase in life events falls between 0.04 and 0.17, or
equivalently, between 4 and 17 when life-events increases from 0 to 100.
Since the interval contains only positive numbers, we infer that the
association between mental impairment and life events is positive,
adjusting for SES. From the least squares fit, the corresponding
frequentist 95% confidence interval for $\beta_1$ is

$$
\hat{\beta}_1 \pm t_{_{0.025, 37}}(se_{1}) = 0.103 \pm 2.026(0.032), \quad
\hbox{which is} \quad (0.04, 0.17).
$$

The Bayesian approach can also generate posterior probabilities, such as
$P(\beta_{1} \leq 0 \mid {\bf y})$ that life events has a nonpositive
effect on mental impairment, adjusting for SES. The {\bf R} analysis, by
finding the indicator for whether each of the elements in the simulation
for generating the posterior distribution of $\beta_{1}$ is less than 0
and then finding their mean, reports
$P(\beta_{1} \leq 0 \mid {\bf y}) = 0.002$; that is, 0 is the 0.002
quantile of the marginal posterior distribution of $\beta_{1}$. This is
very similar to the classical one-sided $P$-value for testing $H_{0}$:
$\beta_{1} = 0$ (and implicitly $H_{0}$: $\beta_{1} \leq 0$) against
$H_{a}$: $\beta_{1} > 0$, where the least squares output shows the
observed test statistic is
$t = \hat{\beta}_{1}/se_{1} = 0.103/0.032 = 3.18$, with
$df = n - (p+1) = 40 - (2+1) = 37$ has one-sided $P$-value 0.0015.
Similarly, the Bayesian posterior $P(\beta_{2} \geq 0) = 0.0007$ is
similar to the frequentist $P$-value for testing $H_{0}$:
$\beta_{2} = 0$ (and implicitly $H_{0}$: $\beta_{2} \geq 0$) against
$H_{a}$: $\beta_{2} < 0$, which is 0.0009. The Bayesian interpretations
are simpler. From $P(\beta_{1} \leq 0 \mid {\bf y}) = 0.002$, we
conclude that the probability is 0.998 that life effects has a positive
effect on mental impairment, adjusting for SES.

In using {\ttfamily brms}, when one enters
`summary(fit.bayes)' to describe a Bayesian fit called`fit.bayes', it
shows results to their default printing of two decimal places.

## Bayesian Inference about the Correlation

Suppose we want to construct a Bayesian posterior interval for the
population value $\rho$ of a correlation between random variables $X$
and $Y$. If you do an Internet search, you will not find a
straightforward way to do this. However, you could construct the
standard frequentist confidence interval for $\rho$ based on the normal
linear model, but treat it as a Bayesian posterior interval for improper
priors and then apply the simpler Bayesian interpretation. For the
frequentist approach, the sampling distribution of the correlation $r$
is not symmetric unless $\rho = 0$, but R. A. Fisher showed that the
transformation $T = (1/2)\log[(1 + r)/(1 - r)]$ has an approximately
normal sampling distribution about
$\tau = (1/2)\log[(1 + \rho)/(1 - \rho)]$, with standard error
$1/\sqrt{n - 3}$. We can use the normal distribution to find the
confidence interval for $\tau$ and then substitute each of its endpoints
in the inverse transformation $\rho = (e^{2\tau} - 1)/(e^{2\tau} + 1)$
to find the confidence interval for $\rho$ and interpret it as a
Bayesian posterior interval based on improper priors.

To illustrate, for 100 home sales in Gainesville, Florida, the
{\ttfamily Houses} data file at the book's website lists the selling
price and size of the house. The correlation between them is
$r = 0.8338$. Fisher's transformation
$T = (1/2)\log[(1 + 0.8338)/(1 - 0.8338)] = 1.2004$ has standard error
$1/\sqrt{100 - 3} = 0.1015$. The 95% confidence interval for $\tau$ is
$1.2004 \pm 1.96(0.1015)$. Using the inverse transformation on its
endpoints yields the 95% confidence interval for $\rho$, which
{\ttfamily R} reports as (0.762, 0.885) and is available in an
{\ttfamily R} package.

```{r}

 Houses <- read.table("http://stat4ds.rwth-aachen.de/data/Houses.dat", header=TRUE)
 T <- (1/2)*log((1 + cor(Houses$price,Houses$size))/(1 - cor(Houses$price,Houses$size)))
 L <- T - 1.96/sqrt(100-3); U <- T + 1.96/sqrt(100-3) # endpoints of CI for tau
 (exp(2*L) - 1)/(exp(2*L) + 1); (exp(2*U) - 1)/(exp(2*U) + 1)
     # Frequentist CI for rho based on Fisher's transformation
 library(confintr)  # R package that can provide CI for correlation
 ci_cor(Houses$price, Houses$size, probs = c(0.025, 0.975)) 
 # This is also a Bayesian posterior interval, for improper priors


```

For the improper prior distributions or very highly disperse proper
prior distributions for the parameters of the normal linear model, it
follows that (0.76, 0.89) is a Bayesian posterior interval for the
population correlation $\rho$. We conclude that the probability is 0.95
that $\rho$ falls between 0.76 and 0.89.

Since the correlation is merely a standardized slope, $H_0$: $\rho = 0$
is equivalent to $H_0$: $\beta_{1} = 0$ in the model
$E(Y) = \beta_{0} + \beta_{1}x$. So, regardless of the selected prior
distributions for Bayesian fitting of the model, the estimates of
$P(\rho > 0 \mid {\bf y})$ and $P(\rho < 0 \mid {\bf y})$ are identical
to the posterior probabilities $P(\beta_{1} > 0 \mid {\bf y})$ and
$P(\beta_{1} < 0 \mid {\bf y})$ obtained from the Bayesian fit.

## Example: Comparing Mean Fertility for Natives and Migrants

A recent study of factors associated with fertility (a woman's number of
children) in a Latin American city focused on whether migrants from
other cities or migrants from rural areas differ from natives of the
city in their family sizes. For a random sample of married women above
age 45, the groups compared were urban natives, urban migrants, and
rural migrants. Since fertility is typically negatively related to
educational level and since that level might differ among the three
groups, the {\ttfamily Fertility} data file at the book's website
contains data on $y$ = fertility, $x$ = number of years of education,
and the group ID. In the following code, software uses indicator
variables $z_{i1} = 1$ for urban migrants and 0 otherwise and
$z_{i2} = 1$ for urban natives and 0 otherwise, with
$z_{i1} = z_{i2} = 0$ for rural migrants.

The code shows shows a Bayesian fit of the model % $$
E(Y_{i}) = \beta_{0} + \beta_1 x_{i} + \beta_2 z_{i2} + \beta_{3}z_{i3},
$$ % using highly disperse prior distributions that provide similar
results to least squares:

```{r}

 Fertility <- #read.table("https://stat4ds.rwth-aachen.de/data/Fertility.dat", header=TRUE)
  read.table("../Data/Fertility.dat", header=TRUE)
 tail(Fertility, 3)
# 52 observations in Fertility data file
 library(brms)                                         
 fit.bayes <- brm(
   fertility ~ education + group, data=Fertility, family=gaussian,
   prior = prior(normal(0,100), class=Intercept) + prior(normal(0,100), class=b) +                    prior(exponential(0.01), class=sigma)
 )
 summary(fit.bayes)                           

```

For identifiability, not including an indicator for rural migrants,
$\beta_2$ and $\beta_3$ provide comparisons of the other two groups with
them. For example, $\tilde{\beta}_{2} = -1.41$ is the estimated
difference between the mean fertility of urban migrants and rural
migrants at each fixed level of education. For each group, mean
fertility is estimated to decrease by 0.24 for each additional year of
education.

## Example: Linear Model for Scottish Hill Races

Each year the Scottish Hill Runners Association publishes a list of hill
races in Scotland for the
year.\footnote{See \url{https://scottishhillrunners.uk}}. Table
\ref{tab4-races} shows the record times (in minutes) for men and for
women for some of the races, as of January 2021, and the
{\ttfamily ScotsRaces} data file at the text website has data for 68
races. Explanatory variables listed are the distance of the race and the
climb in elevation (in kilometers).

In the table: Record time to complete Scottish hill race (in minutes),
by distance and climb in elevation of the course (in kilometers).

\\begin{table} \label{tab4-races}}{%

\begin{tabular}{@{}lcccc@{}}

\hline
Race & Distance & Climb & Record Time Men & Record Time Women \\
\hline
Ben Lomond     &   12.0  &  0.97  &   \phantom{1}62.27 & \phantom{1}71.95 \\
Craig Dunain     &   9.0   &  0.27  &   \phantom{1}39.23 & \phantom{1}45.76 \\
Greenmantle &   3.2  &  0.20  &   \phantom{1}15.10 & \phantom{1}18.75 \\ 
Highland Fling & 85.0 & 1.20 & 439.15 & 490.05 \\
Isle of Jura  &  28.0   &  2.37  &  185.23 & 218.72 \\ 
Lairig Ghru  &  43.0 & 0.64  &  178.17 & 212.63 \\
\hline
%\ \\
\end{tabular}

 \\ The data for all 68 races are in the {\ttfamily ScotsRaces} data
file at the book's website.} \\end{table}

Here, we use Bayesian fitting of linear models to describe the effects
of distance and climb on the the record times for women. We do not
conduct statistical inference, because the races are not in any sense a
random sample of possible races. Here are some summary statistics:

```{r}

 Races <- read.table("http://stat4ds.rwth-aachen.de/data/ScotsRaces.dat", header=TRUE)
 head(Races, 3)                         # timeM for men, timeW for women


 matrix(cbind(mean(Races$timeW), sd(Races$timeW), mean(Races$climb), sd(Races$climb), 
              mean(Races$distance), sd(Races$distance)), nrow=2)
  # timeW has mean = 100.7, standard deviation = 72.6 minutes
  # climb has mean = 0.89, standard deviation = 0.54 km
                            # distance has mean = 16.6, standard deviation = 11.8 km

  pairs(~timeW + distance + climb, data=Races) # scatterplot matrix (Figure 4.1) 

```

The scatterplot for record time and distance reveals a strong linear
trend. The scatterplot of record time and climb shows a rather severe
outlier.

It is plausible that the effect of $d$ = distance on record time is
greater when $c$ = climb in elevation is greater. To allow the effect of
distance to depend on the climb, we include an interaction term in the
fitted model. Moreover, so that the predicted record time is 0 when
$d = c = 0$, we constrain the $y$-intercept term to equal 0.

```{r}
 library(brms) # no intercept specified by -1 at beginning of linear predictor
 fit.bayes <- brm(timeW ~ -1 + distance + climb + distance:climb, data=Races,
                  family=gaussian, prior = prior(normal(0,100), class=b) + 
                    prior(exponential(0.01), class=sigma))
 summary(fit.bayes) 

```

The prediction equation is
$\hat{\mu} = 4.09 d + 18.63 c + 0.92(d \times c)$. For a fixed value of
$c$, the coefficient of $d$ in the prediction equation is 4.09 +
0.92$c$. Between the minimum climb of $c$ = 0.185 \textit{km} and the
maximum climb of $c$ = 2.40 \textit{km}, the effect on record time of a
1 \textit{km} increase in distance changes from 4.09 + 0.92(0.185) =
4.26 minutes to 4.09 + 0.92(2.40) = 6.30 minutes.

The outlier that we observe in the scatterplots is the Highland Fling
race. It is a highly influential observation, having much greater
distance than the others but not an extreme climb.
\textit{Cook's distance} is a diagnostic based on the change in the
least squares estimates $\{\hat{\beta}_{j}\}$ when the observation is
removed from the data set. We use this diagnostic here, since the
Bayesian fit with highly disperse priors is very similar to the least
squares fit. For the Highland Fling observation, which is observation 41
in the data file, Cook's distance equals 9.13 and is 33 times the next
largest value. When we remove Highland Fling from the data file, the
estimated effects change considerably.

```{r}
 fit.LS <- lm(timeW ~ -1+distance+climb+distance:climb, data=Races) # least squares
 cooks.ds <-cooks.distance(fit.LS); tail(sort(cooks.ds), 3)
                  # 3 largest Cook's distance values
                  # Cook's distance = 9.13 for observ. 41
 fit.bayes2 <- brm(timeW ~ -1+distance+climb+distance:climb,data=Races[-41,],family=gaussian,
                   prior=prior(normal(0,100),class=b)+prior(exponential(0.01),class=sigma))
 summary(fit.bayes2)
  
```

For a fixed value of $c$, the coefficient of $d$ in the prediction
equation is now 3.706 + 0.469$c$. Between the minimum climb of 0.185
\textit{km} and the maximum climb of 2.40 \textit{km}, the effect on
record time of a 1 \textit{km} increase in distance changes from 3.706 +
0.469(0.185) = 3.79 minutes to 3.706 + 0.469(2.40) = 4.83 minutes. The
difference is not nearly as great as when the outlying observation is
included in the analysis.

## Collinearity and its Effects

In observational studies, the explanatory variables are often so
correlated that they \`\`overlap'' considerably in the following sense:
Each explanatory variable is nearly redundant, as it can be predicted
well using the others. Because of this, standard deviations for the
estimates generated from posterior distributions can be inflated, making
it difficult to interpret individual effects. Deleting one or more
explanatory variables that are nearly redundant can help to reduce
standard deviations of the remaining estimated effects.

Let $R^{2}_{j}$ denote $R^2$ from least squares regression of $x_j$ on
the other explanatory variables from the model. Then, the
\textit{variance inflation factor} $VIF_{j} = 1/(1 - R_{j}^{2})$
represents the multiplicative increase in var($\hat{\beta}_{j}$) due to
$x_j$ being correlated with the other explanatory variables. As
$R^{2}_{j}$ and hence $VIF$ increases, var($\hat{\beta}_{j}$) increases.
When $VIF$ values are large, standard errors are relatively large and
estimates of the partial effects are imprecise and may themselves be
highly correlated. This condition is called
\\textbf{\textit{collinearity}.

When it occurs in multiple regression modeling, usually we can attain
nearly as large an $R^2$ value in predicting $Y$ with a reduced set of
explanatory variables. \index{s}{Overfitting} We run the risk of
\textit{overfitting} the data if we try to use several highly
intercorrelated explanatory variables, one impact being that estimates
of individual effects can have large standard deviations and be quite
poor.

We illustrate collinearity with a simple simulation. Suppose that $Y$ is
a continuous variable that measures a person's intelligence, but it is
unobservable, called a \textit{latent variable}.\
In a population of interest, suppose that $Y$ has a
$\mathcal{N}(100, 16^{2})$ distribution. To approximate it, suppose
there are four versions of an IQ test, where, conditional on $Y=y$, each
one has a $\mathcal{N}(y, 2^{2})$ distribution. If we could observe $y$,
we now analyze how well we can estimate the effect of $x_{1}$ as a
predictor of $y$, when it is the sole predictor and when the model
contains all four predictors. Here we show least squares results, but
similar results occur with Bayesian analyses:

```{r}
 y <- rnorm(100, 100, 16)
 x1 <- rnorm(100,y,2); x2 <- rnorm(100,y,2); x3 <- rnorm(100,y,2); x4 <- rnorm(100,y,2)
 summary(lm(y ~ x1))
 cor(cbind(y, x1, x2, x3, x4))
 summary(lm(y ~ x1 + x2 + x3 + x4))

```

The model with $x_1$ alone gives a very precise estimate of $y$ and of
the true effect of $x_1$. With all four predictors, the effects change
as they are now partial effects, and the standard errors are much
larger. The correlation is about 0.99 between $y$ and each predictor and
about 0.98 between each pair of predictors. We can predict $y$ nearly as
well with the simpler model, and the interpretation of its effect is
simpler.

## Example: Modeling Selling Price of a Home

The {\bf Houses} data file analyzed the correlation between the selling
price and the size of the house lists $y$ = selling price (in thousands
of dollars) of 100 homes in Gainesville, Florida, together with several
explanatory variables --- the size of the house (in square feet), the
annual tax bill (in dollars), the number of bedrooms, the number of
bathrooms, and an indicator variable for whether the home is new (1 =
yes, 0 = no).

```{r}
 Houses <- read.table("http://stat4ds.rwth-aachen.de/data/Houses.dat", header=TRUE)
 library(brms)
 fit.bayes <- brm(
   price ~ size+taxes+new+bedrooms+baths, family=gaussian, data=Houses,
   prior = prior(normal(0,1000), class="b") + 
     prior(normal(0,1000), class="Intercept") + 
     prior(exponential(0.001), class=sigma)
 )
 summary(fit.bayes)
 
 BIC(lm(price~size + taxes + new + bedrooms + baths, data=Houses))


```

In the table: Results of Bayesian fitting of linear models to predict
home selling prices, selecting explanatory variables using backward
elimination beginning with all the main effects or using forward
selection

\begin{table} 
\label{tab4-models} 
\begin{center}
\begin{tabular}{llccllc}
  \hline
  \multicolumn{3}{c}{Backward elimination} && \multicolumn{3}{c}{Forward selection} \\
Step  & \multicolumn{1}{l}{Explanatory Variables} & BIC &&
Step  & \multicolumn{1}{l}{Explanatory Variables} & BIC \\ \hline
1 & $S$, $T$, $N$, $Be$, $Ba$ & 1162.0    &&   1 & $T$ & 1177.8 \\
2 & $S$, $T$, $N$, $Be$ & 1157.4          &&  2 & $S$, $T$ & 1157.9 \\
3 & $S$, $T$, $N$  & 1154.6               &&  3 & $S$, $T$, $N$ & 1154.6 \\
%4 & $S$, $T$  & 1157.9                    &&  4 & $S$, $T$, $N$, $Be$ & 1157.4\\
%4 & $S$, $T$, $N$, $S$$\times$$N$ & 1145.4 && 4 & $S$, $T$, $N$, $S$$\times$$N$ & 1145.4\\ 
%4b & $S$, $T$, $N$, $S$$\times$$T$ & 1151.2  \\
%4c & $S$, $T$, $N$, $T$$\times$$N$ & 1158.3  \\
%5 & $S$, $T$, $N$, $S$$\times$$N$, $T$$\times$$N$ & 1130.3 && 5 & $S$, $T$, $N$, $S$$\times$$N$, $T$$\times$$N$ & 1130.3 \\
%6 & $S$, $T$, $N$, $S$$\times$$N$, $T$$\times$$N$, $S$$\times$$T$ & 1125.2 \\
\hline 
\end{tabular}
\end{center}
\footnotesize \textit{Note:} $S$ = size, $T$ = taxes, $N$ = whether new, $Ba$ = number of bathrooms, $Be$ = number of bedrooms  \\ \end{table}

Table \ref{tab4-models} also shows results with a forward selection
process. Beginning with the null model and its BIC of 1296.6, one adds
taxes, then size, then whether new, and then BIC increases with other
additions. Here is the Bayesian fit of the simpler model, again with
highly disperse prior distributions:

```{r}
 fit.bayes2 <- brm(
   price ~ size + taxes + new, family=gaussian, data=Houses,
   prior = prior(normal(0,1000), class="b") + 
     prior(normal(0,1000), class="Intercept") + 
     prior(exponential(0.001), class=sigma))
 summary(fit.bayes2)


```

The posterior means for the effects are similar to the more complex
model.

In practical terms, do we lose much by removing the information about
bedrooms and bathrooms? For the frequentist fits that are essentially
the same as the Bayesian fits, the multiple correlation between the
observed selling prices and the fitted values is 0.891 for the model
with all the predictors and 0.889 for the simpler model.

```{r}

 fit1 <- lm(price ~ taxes + size + new + baths + bedrooms, data=Houses)
 fit2 <- lm(price ~ taxes + size + new, data=Houses)
 cor(Houses$price, fitted(fit1)); cor(Houses$price, fitted(fit2))

```

The adjusted $R^2$ values are 0.782 with all the predictors and 0.783
for the simpler model, so it makes sense to continue the model-building
and checking with the simpler model.

At the next stage we could consider potential interaction terms, and in
fact BIC improves with some such additions to the model. Howover, basic
diagnostic analyses with the working main effects model make additional
model-fitting questionable, because of possible violations of the linear
modeling assumptions. For example we could look at a scatterplot between
price and size, distinguishing between the 11 new homes and 89 older
ones. The scatterplot suggests that the variability in selling prices
values may be greater at higher house sizes, whereas the ordinary linear
model assumes constant variability. The figure also shows that one older
home is a clear outlier, having a very large size but relatively low
selling price, yet this observation might not be an outlier for a linear
model that permits the variance of the response variable to increase as
its mean increases. We leave further model building for these data to
the next chapter, where we shall find that more appropriate models can
yield somewhat different conclusions, such as suggesting that
interaction terms are not needed.

## Posterior Predictive Distribution and Its Use for Model Checking

For the {\bf Students} data two %shows responses to a questionnaire by
60 social science graduate students in an introductory Statistics course
at the %University of Florida. Two of the variables observed were $x$ =
high school GPA and $y$ = college GPA. We construct a 95% prediction
interval at the mean high school GPA value of 3.3.

```{r}

 Students <- read.table("http://stat4ds.rwth-aachen.de/data/Students.dat", header=TRUE)
 newdata <- data.frame(hsgpa = 3.3)
 fit <- lm(cogpa ~ hsgpa, data=Students)
 predict(fit, newdata, interval = "predict")


```

The predicted college GPA is 3.45, and we can be 95% sure that it falls
between 2.76 and 4.14 in the corresponding population that this sample
represents. The relatively wide interval reflects that the sample size
is not very large and the sample correlation is only 0.28.

## Regularization for Large p - Lasso Shrinkage to 0. Example: Predicting GPA with Student Survey Data

We use the {\bf Students} data file. We use the 14 binary and
quantitative variables to predict a subject's college GPA. When we use
all 14 explanatory variables as main effects in a linear model and
obtain a Bayesian fit using highly disperse prior distributions, none of
the explanatory variables have posterior means that are more than 2
standard deviations from 0.

```{r}

 Students <- read.table("http://stat4ds.rwth-aachen.de/data/Students.dat", header=TRUE)
 library(brms)
 fit.bayes <- brm(
   cogpa ~ hsgpa + relig + ideol + gender + age + abor + dhome + dres + 
     tv + sport + news + aids + veg + affirm, family=gaussian,
   data=Students,
   prior = prior(normal(0,1000), class=Intercept) +  
     prior(normal(0,1000), class=b) + 
     prior(exponential(0.001), class=sigma)
 )
 print(fit.bayes, digits=3)

```

When we consider each variable by itself as a predictor, \textit{hsgpa}
(high-school GPA) has the highest correlation with the response, but
only 0.278, and it has $t = \tilde{\beta}_{1}/se_{1} = 2.2$. Otherwise,
only \textit{gender} and \textit{relig} (how often attend religious
services, with 0 = never, 1 = occasionally, 2 = most weeks, 3 = every
week) have moderately large $t$ ratios of the estimate divided by its
standard deviation (about 1.5 and 1.8). We next use the lasso,
implemented in {\ttfamily R} with the {\bf glmnet} package applied with
standardized variables.

```{r}

 attach(Students)
 x <- cbind(gender, age, hsgpa, abor, dhome, dres, tv, sport, news,
            aids, veg, ideol, relig, affirm)
 library(glmnet)
 fit.lasso <- glmnet(x, cogpa, alpha=1, family="gaussian") 
 plot(fit.lasso, "lambda")
 set.seed(3)
 cv <- cv.glmnet(x, cogpa, alpha=1, family="gaussian") 
 cv$lambda.min
 cv$lambda.1se
 coef(glmnet(x, cogpa, alpha=1, family="gaussian", lambda=0.097))

```

The fit using the smoothing parameter value of $\lambda = 0.097$
suggested by cross-validation for minimizing prediction error with the
one-standard-error rule has only \textit{hsgpa} as a predictor, and its
estimated effect is only 0.000041. Figure in the book / slides shows how
the lasso estimates change as the smoothing parameter $\lambda$
increases, on the log scale. The values at the left end of the plot,
with the smallest shown value for $\log(\lambda)$, are very close to the
least squares estimates, for which $\lambda = 0$. The \textit{hsgpa}
estimate shrinks toward 0 from the least squares value of 0.148,
becoming 0 when $\log(\lambda) \geq -2.33$ (i.e., $\lambda \geq 0.097$).
