---
title: "Coding Examples Chapter 2"
output:
  html_document:
    df_print: paged
date: "2024-07-16"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## *DO NOT CIRCULATE*

These examples and code are taken from the upcoming book 'Bayesian
Statistics: A Primer for Data Scientists, with R and Python' by Agresti,
Kateri and Mira.

## Chapter 2

### Example: Bayes Estimates with Three Prior Distributions and the Same Data

In this illustration we find Bayesian posterior mean estimates of the
probability $\pi$ of success for each of three binomial experiments that
have the same data, $y = 10$ successes in $n = 10$ trials: (1) a British
woman claims that in tasting a cup of tea with milk, she can tell
whether the milk was poured before or after the tea was poured; (2) A
professor of 18th century musicology claims to be able to tell for any
pair of pages of music, one composed by Mozart and one by Haydn, who
composed each. (3) A person in a drunken state claims to be able to
predict whether your flip of a balanced coin will result in a head or in
a tail. In each case, the frequentist ML estimate of the probability
$\pi$ of a correct prediction is $\hat{\pi} = y/n = 10/10 = 1$. With the
Bayesian approach, however, we may obtain different estimates by
incorporating prior opinion/belief for each scenario. We shall next find
Bayesian posterior mean estimates of $\pi$ based on three separate prior
distributions.

For the tea taster, if we have no *a priori* reason to expect any
particular value for $\pi$, we could select a uniform prior
distribution, which is the Beta(1, 1) distribution. This prior
distribution has mean 0.50 and standard deviation $1/\sqrt{12} = 0.29$.
By contrast, for the other two , our prior beliefs might be easier to
specify in terms of an average chance of success (the mean) and
reasonable variation from the average (the standard deviation). For coin
flips we may be highly skeptical of any claim about predictions and
decide to use a beta prior distribution with mean 0.50 but with small
standard deviation, say 0.03, so that the beta distribution is highly
concentrated near 0.50. We might have greater faith in the
musicologist's claim, perhaps using a beta prior distribution with a
mean of 0.90 and standard deviation 0.10. We need now to solve for the
$\alpha_1$ and $\alpha_2$ values that identify the beta distributions
having these means and standard deviations. For a chosen mean $\mu$,
from the formula $\mu = \alpha_{1}/(\alpha_{1} + \alpha_{2})$ for a beta
distribution, any particular value $\alpha_{1}$ has a corresponding
$\alpha_{2} = \alpha_{1}(1 - \mu)/\mu$. By trial and error for a
particular value of $\mu$ we can find a pair of
($\alpha_{1}, \alpha_{2}$) values that have a particular standard
deviation $\sigma$, or we could solve simultaneously for
($\alpha_{1}, \alpha_{2}$) based on ($\mu, \sigma$). The following *R*
code shows that for a beta prior distribution with ($\mu, \sigma$) =
(0.50, 0.03) for the coin-tossing predictions, we can take
hyperparameter values ($\alpha_{1}, \alpha_{2}$) $\approx$ (138, 138),
and for ($\mu, \sigma$) = (0.90, 0.10) for the musicologist, we can take
($\alpha_{1}, \alpha_{2}$) $\approx$ (7, 7/9).

```{r}
alpha1 = 138; alpha2 = 138 # beta hyperparameters for predictor of coin flips
alpha1/(alpha1+alpha2) # mean of beta prior distribution
sqrt((alpha1*alpha2)/((alpha1+alpha2)^2 * (alpha1+alpha2+1)))
# standard deviation of beta prior distribution 

alpha1 = 7; alpha2 = 7/9 # beta hyperparameters for musicologist
alpha1/(alpha1+alpha2) # mean of beta prior distribution
sqrt((alpha1*alpha2)/((alpha1+alpha2)^2 * (alpha1+alpha2+1)))  
# standard deviation of beta prior distribution
```

With $y=10$ successes in $n=10$ trials, the posterior beta distribution
has hyperparameter values
$\alpha_{1}^* = y + \alpha_{1} = 10 + \alpha_{1}$ and
$\alpha_{2}^* = n - y + \alpha_{2} = 10 - 10 + \alpha_{2} = \alpha_{2}$.
The posterior mean is
$\tilde{\pi} = \alpha_{1}^*/(\alpha_{1}^* + \alpha_{2}^*) = (10 + \alpha_{1})/(10 + \alpha_{1} + \alpha_{2})$.
We now find $\tilde{\pi}$ for the three chosen prior distributions:

```{r}
alpha1 <- 1; alpha2 <- 1  # hyperparameter values for uniform prior distribution
alpha1post <- 10 + alpha1; alpha2post <- alpha2 # hyperpara's for posterior when y=n=10
alpha1post/(alpha1post + alpha2post) # beta posterior mean for British tea taster
qbeta(0.5, alpha1post, alpha2post) # posterior median for British tea taster
alpha1 = 138; alpha2 = 138 # beta hyperparameters with mean 0.50, standard dev. 0.03
alpha1post <- 10 + alpha1; alpha2post <- alpha2 # hyperpara's for posterior when y=n=10
alpha1post/(alpha1post + alpha2post) # beta posterior mean for predictor of coin flips

alpha1 = 7; alpha2 = 7/9 # beta hyperparameters with mean 0.90, standard dev. 0.10
alpha1post <- 10 + alpha1; alpha2post <- alpha2 # hyperpara's for posterior when y=n=10
alpha1post/(alpha1post + alpha2post) # beta posterior mean for musicologist 
qbeta(0.5, alpha1post, alpha2post) # posterior median for musicologist 
```

With these prior distributions, the posterior mean estimates of $\pi$
are 0.917 for the tea taster and 0.956 for the musicologist but only
0.517 for the predictor of coin flips. The posterior mean for coin
flipping is very close to the prior mean of 0.50, the data having
relatively little influence because the prior beliefs express a high
degree of certainty.

The **LearnBayes** package in R has a useful function for approximating
hyperparameter values for a beta distribution having a specified
probability in a particular range. For instance, the following code
finds the beta distribution that has probability 0.95 between 0.10 and
0.30:

```{r}
library(LearnBayes)
quantile1 <- list(p = .025, x = 0.10); quantile2 <- list(p = .975, x = 0.30)
shape <- beta.select(quantile1, quantile2)
cat("shape parameters", shape)
```

### Example: Do you believe in hell?

The 2018 General Social Survey in the U.S. asked “Do you believe in
hell?” The percentage who responded *yes* was 74.0% for the 727 subjects
with a high school education or less, 70.1% for the 304 subjects with a
junior college or bachelor's degree, and 56.8% for the 111 subjects with
a graduate degree. We shall find posterior intervals for the population
proportion $\pi$ of those with a graduate degree who would respond
*yes*. For the counts of 63 for the *yes* response and 48 for the *no*
response, the ML estimate of $\pi$ is $\hat{\pi} = 63/111 = 0.568$, and
the 95% Wald confidence interval
$\hat{\pi} \pm 1.96\sqrt{\hat{\pi}(1 - \hat{\pi})/n}$ is (0.475, 0.660).
For the uniform Beta(1, 1) prior distribution with $y=63$ and
$n-y = 48$, the posterior distribution is
Beta($\alpha_{1}^*, \alpha_{2}^*$) with
$\alpha_{1}^* = y + \alpha_{1} = 64$ and
$\alpha_{2}^* = n - y + \alpha_{2} = 49$. The posterior mean estimate of
$\pi$ is
$\alpha_{1}^{*}/(\alpha_{1}^{*} + \alpha_{2}^{*}) = 64/(64 + 49) = 0.566$,
and the 0.025 and 0.975 quantiles of the beta posterior distribution are
(0.474, 0.656). Software reports that the 95% HPD interval is (0.475,
0.657). Very similar results occur for the Jeffreys prior distribution,
which is the Beta(0.5, 0.5) distribution.

```{r}
qbeta(c(0.025, 0.975), 63 + 1, 48 + 1)
# quantiles of beta posterior dist. for 95% equal-tail percentile int. with uniform prior

qbeta(c(0.025, 0.975), 63.5, 48.5) 
# quantiles of beta posterior dist. for 95% equal-tail percentile int. with Jeffreys prior

library(binom)
binom.bayes(63, 111, conf.level=0.95, type="central", alpha1=1, alpha2=1)
# 95% equal-tail percentile int. for uniform prior dist.

binom.bayes(63, 111, conf.level=0.95, alpha1=1, alpha2=1)
# 95% HPD interval for uniform prior dist.

binom.bayes(63, 111, conf.level=0.95, alpha1=0.5, alpha2=0.5)
# 95% HPD interval for Jeffreys prior dist.

binom.confint(63, 111, conf.level=0.95, method="asymptotic") # 95% Wald confidence int.

binom.confint(63, 111, conf.level=0.95, method="wilson")  
# 95% score confidence int. (better than Wald CI if n small or pi near 0 or 1)
```

### Influence of Sample Size and Prior Distribution on Posterior Intervals

As the sample size $n$ increases, the influence of the prior
distribution weakens and the posterior distribution has appearance
closer to that of the likelihood function. As $n$ increases, Bayesian
posterior mean estimates of $\pi$ become more similar to the ML estimate
and Bayesian posterior intervals become more similar to frequentist
confidence intervals.

We illustrate this with a sequence of cases in which $\hat{\pi} = 0.70$,
computing for increasing values of n the frequentist Wald confidence
interval and the Bayesian HPD interval obtained with uniform prior
distribution ($\alpha_1 = \alpha_2 = 1$):

```{r}
library(binom)
binom.confint(7, 10, conf.level=0.95, method="asymptotic") # n = 10
# frequentist Wald CI

binom.bayes(7, 10, conf.level=0.95, alpha1=1, alpha2=1) 
# Bayesian HPD interval for uniform prior distribution
                                              
binom.confint(70, 100, conf.level=0.95, method="asymptotic") # n = 100
# frequentist Wald CI

binom.bayes(70, 100, conf.level=0.95, alpha1=1, alpha2=1)
# Bayesian HPD interval

binom.confint(7000, 10000, conf.level=0.95, method="asymptotic") # n=10000
# frequentist Wald CI

binom.bayes(7000, 10000, conf.level=0.95, alpha1=1, alpha2=1)
# Bayesian HPD interval
```

For a particular sample size n (set to 100 in the R code below), a
Bayesian interval is more similar to the frequentist confidence interval
as the prior distribution is more diffuse, that is, as
$\alpha_1 = \alpha_2  = \alpha$ decreases toward 0:

```{r}
library(binom)
binom.bayes(70, 100, conf.level=0.95, alpha1=100, alpha2=100)  # beta hyperpara's=100
# narrow interval when prior dist. has small variance

binom.bayes(70, 100, conf.level=0.95, alpha1=10, alpha2=10)    # beta hyperpara's=10

binom.bayes(70, 100, conf.level=0.95, alpha1=1, alpha2=1)      # beta hyperpara's=1

binom.bayes(70, 100, conf.level=0.95, alpha1=0.1, alpha2=0.1)  # beta hyperpara's=0.1

binom.bayes(70, 100, conf.level=0.95, alpha1=0.01, alpha2=0.01) # beta hyperpara's=0.01

binom.confint(70, 100, conf.level=0.95, method="asymptotic") # frequentist Wald CI
```

## Posterior Probability Analogs of P-values

With the uniform prior, the posterior distribution is beta with
hyperparameters $\alpha_{1}^* = y + 1 = 64$ and
$\alpha_{2}^* = n - y + 1 = 49$. We next use this posterior distribution
to find $P(\pi < 0.50 \mid y)$ and $P(\pi > 0.50 \mid y)$:

```{r}
pbeta(0.50, 64, 49) # cumulative probability at 0.50 for beta posterior distribution

1 - pbeta(0.50, 64, 49) # posterior P(pi > 0.50 | y)

```

The posterior $P(\pi > 0.50 \mid y) = 0.922$ and
$P(\pi < 0.50 \mid y) = 0.078$ provide substantial but not overly strong
evidence that the majority believe in hell.

A corresponding frequentist statistical inference reports the $P$-value
for testing $H_0$: $\pi = 0.50$ (implicitly $\pi \leq 0.50$) against
$H_{1}$: $\pi > 0.50$. Since $y = 63$, the $P$-value is the binomial
probability of observing $Y \geq 63$ in $n=111$ trials when actually
$H_0$ is true, that is, $1 - P(Y \leq 62 \mid \pi = 0.50) = 0.092$. It
is plausible that this particular $H_0$ is true (i.e., $\pi = 0.50$),
because the $P$-value is small but not overly so, and we would not
reject $H_0$ at the usual significance levels such as 0.05.

```{r}
1 - pbinom(62, 111, 0.50) # one-sided (right-tail) P-value for Binom(111, 0.50) dist.
```

### Bayesian Prediction of Future Observations

Returning to the example of the British tea taster we illustrate the
concept of Bayesian prediction of future observations. After observing
10 successful guesses in 10 cups, combined with a uniform prior
distribution we obtained a posterior beta distribution for the
probability of a successful prediction, with $\alpha_{1}^{*} = 11$ and
$\alpha_{2}^{*} = 1$, for which the posterior mean is
$\mu^{*} = 11/12 = 0.9167$. For the next $n_{_{f}} = 5$ cups, here is
the beta-binomial distribution for the number of correct guesses
$Y_{_f}$:

```{r}
#install.packages("extraDistr")
library(extraDistr)
dbbinom(c(0,1,2,3,4,5), 5, alpha = 11, beta = 1) 
# predictive probabilities P(Y_f = 0), P(Y_f = 1), ... , P(Y_f = 5)

```

For the five future guesses, the expected number of correct guesses is
$E(Y_{_{f}}) = n_{_{f}}\mu^{*} = 5(11/12) = 4.58$, and the probability
is 0.6875 that all five will be correct.

### Example: Do you believe in hell? - continued

With independent binomial samples, we can construct a Bayesian posterior
interval for $\pi_{1} - \pi_{2}$ by selecting independent beta prior
distributions for $\pi_{1}$ and $\pi_{2}$. When $\alpha_1 = \alpha_2$
for each beta prior distribution, the prior distribution of
$\pi_1 - \pi_2$ is symmetric around 0.

We illustrate Bayesian inference for $\pi_1 - \pi_2$ by comparing the
proportions of females and of males who believe in hell, again using
data from the 2018 General Social Survey. The sample proportions are
$\hat{\pi}_{1} = 498/674 = 0.739$ for females and
$\hat{\pi}_{2} = 316/468 = 0.675$ for males. When we use uniform prior
distributions for $\pi_1$ and $\pi_2$, the posterior distribution is
Beta($y_{1} + 1, n_{1} - y_{1} + 1$) = Beta(499, 177) for $\pi_1$ and
Beta($y_{2} + 1, n_{2} - y_{2} + 1$) = Beta(317, 153) for $\pi_2$. A
simple way to construct a posterior interval for $\pi_{1} - \pi_{2}$ is
by simulating from the posterior distributions of $\pi_1$ and $\pi_2$
and using those values to approximate the posterior distribution of
$\pi_1 - \pi_2$ and its quantiles; that is, generate a very large number
of beta random variables from the posterior beta densities of $\pi_1$
and $\pi_2$ and approximate the relevant posterior quantiles of
$\pi_1 - \pi_2$ for the posterior interval.\
The following **R** code shows a posterior 95% percentile interval based
on simulating 50 million random draws from each posterior beta density.
We also show results using **R** functions to simulate the HPD interval
and to construct the frequentist 95% Wald and score confidence
intervals:

```{r}
pi1 <- rbeta(5000000, 499, 177) # simulating from posterior dist. of pi_1
pi2 <- rbeta(5000000, 317, 153) # simulating from posterior dist. of pi_2 
quantile(pi1 - pi2, c(0.025, 0.975)) # 0.025 and 0.975 quantiles of simulated difference
# simulated 95% percentile interval for pi1 - pi2

hist(pi1 - pi2)                  # posterior distribution is bell-shaped
plot(density(pi1 - pi2), ylab="Density", xlab="Difference of Probabilities", main="")

#install.packages('HDInterval')
library(HDInterval)
hdi(pi1 - pi2, credMass=0.95) # simulated 95% HPD interval for pi1 - pi2

prop.test(c(498, 316), c(674, 468), correct=FALSE) # data c(y1, y2), c(n1, n2) 
# frequentist 95% Wald CI for pi1 - pi2

#install.packages('PropCIs')
library(PropCIs)
diffscoreci(498, 674, 316, 468, conf.level=0.95) # arguments y1, n1, y2, n2
# frequentist 95% score CI for pi1 - pi2

quantile(pi1/pi2, c(0.025, 0.975)) # simulated 95% percentile interval for risk ratio
```

With such large sample sizes, the Bayesian and frequentist intervals are
all very similar.

For comparing two proportions, another useful summary measure is the
ratio $\pi_{1}/\pi_{2}$. This is called the
\textbf{\textit{relative risk}} or \textbf{\textit{risk ratio}}. It is
often used in medical research to compare the probability of a certain
undesirable outcome for two treatments, because the ratio can be more
relevant than the difference when both probabilities are close to 0. We
can simulate the posterior distribution of $\pi_{1}/\pi_{2}$ and form
posterior intervals using the simulated values from the beta posterior
distributions of $\pi_{1}$ and $\pi_{2}$. For example, the posterior
probability is 0.95 that the population proportion in the U.S. who
believe in hell is between 1.01 and 1.18 times as high for women as for
men:

```{r}
quantile(pi1/pi2, c(0.025, 0.975)) # using values simulated in previously shown output
# simulated 95% percentile interval for risk ratio
```

## Analogs of Significance Tests about Difference of Proportions

Using a simulated posterior distribution for $\pi_1 - \pi_2$, we can
precisely approximate posterior probabilities such as
$P(\pi_{1} > \pi_{2} \mid y_{1}, y_{2})$ by the proportion of the
simulated joint distribution for which $\pi_1 > \pi_2$. For analyzing
belief in hell by gender, we used uniform prior distributions. As seen
in the following **R** code, the posterior probability that females are
more likely than males to believe in hell is 0.990. It seems highly
likely that $\pi_1 > \pi_2$.

```{r}
pi1 <- rbeta(5000000, 499, 177) 
pi2 <- rbeta(5000000, 317, 153) 
mean(pi1 < pi2); mean(pi1 > pi2) # simulated posterior P(pi1 < pi2), P(pi1 > pi2)
prop.test(c(498, 316), c(674, 468), correct=FALSE) # data c(y1, y2), c(n1, n2) 
# X-squared = chi-squared statistic = square of z test stat; doesn't show direction
```

The R output also shows the result of the frequentist significance test
of $H_0: \pi_1 = \pi_2$. It is a chi-squared statistic that is the
square of the $z$ test statistic.

## Multiple Comparisons of Several Binomial Parameters

In practice, the number of groups to be compared often exceeds two. We
can construct the inferences so that the error probability applies to
the entire family of inferences rather than to each individual one. The
method for constructing simultaneous posterior intervals is called the
Bonferroni method. To illustrate, for the 2018 General Social Survey
responses to “Do you believe in hell?” by education level, the (yes, no)
totals were (538, 189) for those with at most a high-school education,
(213, 91) for those with a junior college or bachelor’s degree, and (63,
48) for those with a graduate degree. When we use posterior probability
0.98 for each of the 3 comparisons of pairs of education levels, the
entire set of 3 posterior intervals holds with probability at least
1-3(0.02) = 0.94. We next simulate percentile intervals to do this,
using the posterior distributions generated with uniform prior
distributions:

```{r}
pi1 <- rbeta(5000000, 600+1, 1635-600+1) # posterior dist. with uniform prior for white
pi2 <- rbeta(5000000, 100+1, 368-100+1)  # posterior dist. with uniform prior for black
pi3 <- rbeta(5000000, 54+1, 277-54+1)    # posterior dist. with uniform prior for other
quantile(pi1 - pi2, c(0.01, 0.99)) # posterior probability = 0.99 - 0.01 = 0.98
quantile(pi1 - pi3, c(0.01, 0.99))
quantile(pi2 - pi3, c(0.01, 0.99))
```

At this probability level, we conclude that belief in hell is less
common for those with a graduate degree than for the other two education
levels, because the posterior intervals for $\pi_1 - \pi_3$ and for
$\pi_2 - \pi_3$ contain only positive values. For example, we infer that
the population proportion believing in hell is between 0.06 and 0.29
higher for those with at most a high school degree than for those with a
graduate degree. The intervals are wide, and belief in hell could be
substantially less common for those with a graduate degree. However, it
is plausible that the proportions believing in hell are equal for the
first two education levels, because the posterior interval for
$\pi_1 - \pi_2$ contains 0.

### Example: What percentage of people are very happy?

The 2021 General Social Survey asked respondents whether they considered
themselves to be very happy, pretty happy, or not too happy. The sample
counts of the 4003 respondents in the (very happy, pretty happy, not too
happy) categories were (778, 2304, 921), for percentages (19.4, 57.6,
23.0). We shall find posterior intervals for the proportions of adults
in the U.S. who characterize themselves in each category.

With such a large sample size and the small values of $\{\alpha_{j}\}$
typically selected, the prior distribution has little impact. We use a
uniform Dirichlet distribution over the probability simplex, for which
$\alpha_1 = \alpha_2 =\alpha_3 = 1$ and
$\alpha_{0} = \sum_{k=1}^{3}\alpha_{k} = 3$. The beta posterior
distribution of $\pi_1$ for the very happy category has hyperparameters
$y_{1} + \alpha_{1} = 779$ and
$(y_{2} + y_{3}) + (\alpha_{2} + \alpha_{3}) = (2304 + 921) + (1 + 1) = 3227$.
Similarly, hyperparameters are (2305, 1701) for the pretty happy
category and (922, 3084) for the not too happy category. Here are 99%
equal-tail percentile intervals for $\pi_{1}$, $\pi_{2}$, and $\pi_{3}$:

```{r}
qbeta(c(0.005, 0.995), 779, 3227)  # quantiles, beta hyperparameters for very happy  
#   99% posterior percentile interval

qbeta(c(0.005, 0.995), 2305, 1701) # quantiles, beta hyperparameters for pretty happy  
#   99% posterior percentile interval

qbeta(c(0.005, 0.995), 922, 3084)  # quantiles, beta hyperparameters for not too happy  
#   99% posterior percentile interval
```

For example, the probability is 0.99 that the population proportion who
would report being very happy is between 0.179 and 0.211. By the
Bonferroni method, all three posterior intervals contain the true
population proportion values with probability at least 1-3(0.01) = 0.97.

### Frequentist Test of Independence of Two Categorical Variables

Another topic for which the multinomial distribution applies is the
study of association between two categorical variables. Besides asking
about happiness, the 2021 General Social Survey asked respondents about
their relative family income. How can we analyze whether an association
exists between happiness and family income, that is, whether the chance
of being in a particular happiness category such as *very happy* depends
on the family income level?

Column are Very happy & Pretty happy & Not too happy. While rows here
are showing their incomes, as above average, average and below average.

```{r}
data <- matrix(c(282,324,172,670,966,668,198,301,422),c(3,3)) # 3 rows and 3 columns
data
chisq.test(data) # Pearson chi-squared test
```

### Bayes Factor for Evaluating Plausibility of Independence

Bayesian methods also apply for evaluating $H_0$: independence. The
Bayes factor is the ratio $m_{1}(y)/m_{0}(y)$ of the marginal
probability functions of the observed data under the two hypotheses,
which is the likelihood ratio. We can use a Bayes factor to compare the
evidence supporting the hypothesis $H_0$ of statistical independence of
two categorical variables with the general alternative hypothesis $H_1$
that permits the categorical variables to be statistically dependent. We
do this based on models expressed in terms of Dirichlet distributions
for the joint probabilities.

For the assumption of joint multinomial sampling over the 9 cells, one
model permitting statistical dependence assumes a joint uniform
Dirichlet prior distribution over the space of $rc$ cell probabilities
$\{P(X = i, \, Y=j)\}$ that sum to 1. An independence model assumes a
marginal uniform Dirichlet prior distribution for $\{P(X=i)\}$ that sum
to 1 and another independent marginal uniform Dirichlet prior
distribution for $\{P(Y=j)\}$. The Bayes factor in favor of the
statistical dependence model over the independence one has a complex
expression involving several gamma functions. Its formula does not
provide intuition and we omit it, but it is provided by **R** as shown
in the following code:

```{r}
#install.packages("BayesFactor")
library(BayesFactor)
BF <- contingencyTableBF(data, priorConcentration = 1, sampleType = "jointMulti")
# priorConcentration = 1 is default uniform Dirichlet dist's encoding independence
# use sampleType = "indepMulti" for independent multinomial sampling in the rows
BF
```

We estimate that the data would be 3.3 $\times 10^{23}$ times more
likely under the dependence model than under the independence one. This
is extremely strong evidence against the hypothesis that happiness and
income are statistically independent. This Bayes factor approach, unlike
the frequentist chi-squared test, has differing results when we instead
assume independent multinomial samples in the three rows:

```{r}
 contingencyTableBF(data, sampleType = "indepMulti", fixedMargin = "rows")
```

In practice, neither these Bayes factors nor the frequentist chi-squared
test are sufficient to give us the sort of information that is
especially informative. We rarely expect a null hypothesis of
independence to be plausible, and whether we obtain a small $P$-value
and a large Bayes factor mainly reflects whether $n$ is sufficiently
large to have good power. Of greater interest in most practical
applications is the nature and the strength of the association between
the variables. For example, we could focus on the difference in the
population proportions that are very happy between those with family
income above average and those with family income below average. We next
find a Bayesian posterior interval for this difference, using simulation
for the beta posterior distributions implied by binomial counts of (very
happy, not very happy) and uniform prior distributions for the
population proportions:

```{r}
piVH1 <- rbeta(50000000, shape1 = 282 + 1, shape2 = 670 + 198 + 1) 
 # simulating posterior beta dist. for P(very happy) for above average income
# for above average income, 282 very happy, 670 + 198 not in very happy category
# adding + 1 for each posterior beta hyperparameter results from uniform prior dist.
piVH3 <- rbeta(50000000, shape1 = 172 + 1, shape2 = 668 + 422 + 1) 
# simulating posterior beta dist. for P(very happy) for below average income
quantile(piVH1 - piVH3, c(0.025,0.975))
```

We estimate that the probability of being very happy is between 0.08 and
0.14 higher for the above average income group than the below average
income group.

### Example: Estimating Biden/Trump Presidential Election Results

This example simulates a sample of 1000 people to mimic a poll taken
before the 2020 U.S. presidential election, in which the Democratic
candidate Joseph Biden faced the Republican candidate Donald Trump. Let
$\pi_i$ be the population proportion in the actual election that voted
for Biden in state $i$ ($i = 1, \dots , 51$, where $i = 8$ is District
of Columbia), out of those that voted for Biden or Trump. We take the
number of observations $n_i$ in the simulated sample from state i
proportional to the number of people in state i who voted in that
election, subject to $\sum_i n_i = 1000$. The simulated number $y_i$
voting for Biden is the outcome of a Binom($n_i,\pi_i$) random variable.

Many states have small $n_i$, and we can obtain better estimates by
borrowing from the whole data set. The essence of the empirical Bayes
approach with a beta prior distribution is that we regard the data as
being generated in the following way: 51 randomly generated values from
a Beta($\alpha_1,\alpha_2$) distribution determine the population
proportions $\{\pi_i\}$ voting for Biden. Then, a randomly generated
value from the Binom($n_i,\pi_i$) distribution yields the number $y_i$
in the sample of size $n_i$ from state $i$ voting for Biden,
$i = 1, \dots , 51$. The sample proportions $\{\hat{\pi}_i = y_i/n_i\}$
exhibit greater variability than if the $\{y_i\}$ came from outcomes of
{Binom($n_i,\pi$)} binomial random variables that all had the same
success probability $\pi$. We do not know $\alpha_1$ and $\alpha_2$ for
the beta distribution that generated the $\{\pi_j\}$, but once we
observe the counts $\{y_i\}$ and sample size indices $\{n_i\}$, software
can use iterative methods to find marginal ML estimates $\alpha_1$ and
$\alpha_2$ by maximizing the beta-binomial likelihood function for the
data. Then we perform ordinary Bayesian inference using the
Beta($\hat{\alpha}_1,\hat{\alpha}_2$) prior distribution. The posterior
mean estimate of a population proportion $\pi_i$ is a weighted average
of the sample proportion $\hat{\pi}_i$ and the mean
$\hat{\alpha}_1/(\hat{\alpha}_1+\hat{\alpha}_2)$ of the estimated beta
prior distribution.

For the election polling data, the following R code shows that
maximizing the marginal beta-binomial likelihood yields estimated
hyperparameters for the beta distribution of $\hat{\alpha}_1 = 32.49$
and $\hat{\alpha}_2 = 29.39$. The following code shows results for the
first five states in the list.

```{r}
Election <- read.table("https://bayes4ds.rwth-aachen.de/data/Election2020.dat", header=TRUE)
head(Election, 5)
#install.packages("VGAM")
library(VGAM)                  # package that can find ML fit of beta-binomial dist.
fit.bb <- vglm(cbind(y, n-y) ~ 1, betabinomialff, data=Election) # Fits beta binomial
Coef(fit.bb)                   #    to find marginal ML estimates of beta hyperpara's
#   for empirical Bayes approach
#Estimated beta hyperparameters
Popul.prop <- Election$pi; State <- Election$state
Sample.prop <- Election$y/Election$n
Emp.Bayes.est <- (Election$y+Coef(fit.bb)[1])/(Election$n+Coef(fit.bb)[1]+Coef(fit.bb)[2])
Results <- data.frame(State, Popul.prop, Sample.prop, Emp.Bayes.est)
head(Results, 5)
sqrt((sum(Election$n*(Sample.prop - Popul.prop)^2))/1000)
#root mean square of sample proportions around population proportions
sqrt((sum(Election$n*(Emp.Bayes.est - Popul.prop)^2))/1000)
#root mean square of empirical Bayes estimates around population prop's

```

### Normal Distribution for Logit Transformation of a Probability (Example: Do you believe in hell? - continued Part 2)

The normal distribution has a bell-shaped pdf that is symmetric. We
denote the normal distribution with mean $\mu$ and variance $\sigma^2$
by $N(\mu,\sigma^2)$, where $\mu$ can be any real number and
$\sigma > 0$. When we use the normal distribution as a prior
distribution for $\log[\pi/(1 - \pi)]$, we refer to the distribution for
$\pi$ itself as the logit-normal distribution. When we take $\mu = 0$
for the normal distribution, the corresponding logit-normal distribution
on the $\pi$ scale has pdf with a symmetric shape around 0.50. It is
unimodal when $\sigma^2 \leq 2$ and bimodal when $\sigma^2 > 2$, but
always tapering off toward 0 as $\pi$ approaches 0 or 1. Specifically,
it is mound-shaped for $\sigma = 1$, roughly uniform except near the
boundaries when $\sigma \approx 1.5$, and with more pronounced peaks for
the modes when $\sigma$ is about 2 or larger.

We will not consider here the methodology for finding the posterior
distribution for the logit parameter, $L = \log[\pi/(1 - \pi)]$,.
However, it is simple to construct it using software. Once we do this, a
posterior interval for $L$ yields a posterior interval for $\pi$ using
the inverse transformation, $$
\pi = e^L/(1 + e^L).
$$

To illustrate, the same GSS that asked about belief in hell also asked
respondents if they believed in an afterlife. Of 1129 respondents, 904
said yes and 225 said no. We next find posterior intervals for the
population proportion $\pi$ saying yes using Bayesian approaches with
(i) a uniform prior distribution for $\pi$, and (ii) a $N(0,\sigma^2)$
prior distribution for $\log[\pi/(1 - \pi)]$ with $\sigma = 2$. Here, we
first use the binom package in R with the uniform prior, and then the
brms (Bayesian Regression Models using ’Stan’) package. The brms package
uses ‘bernoulli’ to specify the binomial with a single trial and uses
‘normal(mu, sigma)’ to specify a normal distribution, with the standard
deviation rather than the variance in the second argument.

```{r}
library(binom)
binom.bayes(904, 1129, conf.level=0.95, type="central", alpha1=1, alpha2=1)
# 95% posterior interval for pi for uniform prior

y <- c(rep(1, 904), rep(0, 225)) # the sample of 904 `yes' and 225 `no' outcomes 
Results <- data.frame(y) 
library(brms)
fit.bayes <- brm(y ~ 1, family=bernoulli(link=identity), refresh = 0, data=Results, prior = prior(uniform(0,1), lb=0, ub=1, class=Intercept), silent = 2)
print(fit.bayes, digits=3)
# 95% post. int. for pi for uniform prior
```

With the $\mathcal{N}(0, 2^2)$ prior distribution for the logit, the
posterior probability is 0.95 that $L = \log[\pi/(1 - \pi)]$ falls
between 1.249 and 1.544. These endpoints yield the corresponding
endpoints % $$
\bigg(\frac{e^{1.249}}{1 + e^{1.249}}, \ \frac{e^{1.544}}{1 + e^{1.544}}\bigg) = (0.777, \, 0.824) 
$$ % for $\pi$. These endpoints are very similar to those of (0.776,
0.823) for the 95% equal-tail percentile interval using a uniform prior
distribution for $\pi$. In fact, we can also use the {\ttfamily brms}
package to obtain the posterior interval for a uniform prior
distribution:

```{r}
fit.bayes2 <- brm(y ~ 1, family=bernoulli(link=logit), refresh = 0, data=Results, prior = prior(normal(0,2), class=Intercept), silent = 2)
print(fit.bayes2, digits=3)
# 95% posterior interval for logit using normal prior

exp(fixef(fit.bayes2))/(1 + exp(fixef(fit.bayes2)))
# 95% post. interval for proportion using normal prior for logit

```

### Example: Election - continued

Rather than use noninformative normal priors with large $\sigma$, we
could select a relatively small $\sigma$ based on historical
information. Past elections suggest that all (or nearly all) states tend
to have proportion $\pi_i$ favoring the Democratic candidate between
about 0.25 and 0.75, for which logit($\pi_i$) falls between -1.1 and
+1.1. Since nearly the entire normal distribution falls within 3
standard deviations of its mean, we could take the normal prior to have
$\mu \pm 3\sigma$ equal to $\pm1.1$, or $\mu = 0$ and
$\sigma \approx 1.1/3 = 0.37$. To obtain posterior intervals, we use the
brms package in R to model the logit transform of $\pi$ in terms of the
state identification.

```{r}
Election <- read.table("https://bayes4ds.rwth-aachen.de/data/Election2020ungrouped.dat", header=TRUE)
head(Election)
library(brms)
fit.bayes <- brm(y ~ -1 + factor(state), family=bernoulli(link=logit), data=Election,
                 refresh = 0, prior = prior(normal(0,0.37), class=b))
print(fit.bayes, digits=3) # Alaska posterior mean logit = -0.129
exp(fixef(fit.bayes))/(1 + exp(fixef(fit.bayes)))# Alaska estimated Biden proportion = 0.468
```

The posterior means $\{L_{i}^{*}\}$ for the logits transform to the
Bayesian proportion estimates
$\{\pi_{i}^{*}= \exp(L_{i}^{*})/[1 + \exp(L_{i}^{*})]\}$, such as shown
here. The Bayesian estimates tend to be closer than the sample
proportions to the true values. The square root of the MSE about the
true proportions, weighted by the per-state sample sizes, is 0.078 for
the Bayesian estimates and 0.097 for the sample proportions.
