--- 
title: "Harmonized Finnish National Bibliography"
author: "Helsinki Computational History Group (COMHIS)"
date: "`r Sys.Date()`"
site: "bookdown::bookdown_site"
output:
  bookdown::gitbook: default
documentclass: book
---

# Preface

Placeholder



<!--chapter:end:index.Rmd-->

# Author's lifetime

```{r source-author-date, include=FALSE}
# author_date field
source("author_date.R")
```

[Author date accepted](output.tables/auhtor_date_accepted.csv)

[Author date discarded](output.tables/auhtor_date_discarded.csv)

Author's lifetime is available for `r sum(!is.na(df$author_age))` authors (`r round(100*mean(!is.na(df$author_age)))`%).The lifetime years span `r range(na.omit((df$author_age)))`.





<!--chapter:end:author_date.Rmd-->


# Author's name

Placeholder


## Authors
### Auxiliary files
### Author productivity

<!--chapter:end:author_name.Rmd-->

# Corporate

```{r setup-corporate, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

```{r source-corporate, include=FALSE}
# corporate field
source("corporate.R")
```

Corporate-field contains names of the printing houses ("kirjapaino" in Finnish), manufactures, companies or institutions involved in printing of the books.

[Accepted corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)

[Discarded corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_discarded.csv)

* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)


 Top-`r ntop` titles and their title counts.
 
```{r summarytitle-corporate, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "corporate", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
``` 

Frequency of unique titles:
  
```{r uniquetitles-corporate, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$corporate)
d <- data.frame(title = names(tab), n = as.numeric(tab))

library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- ggplot(d, aes(x = n)) +
  geom_histogram(color="black", fill="white") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```





<!--chapter:end:corporate.Rmd-->


# Language summaries

Placeholder


## Top languages

<!--chapter:end:language.Rmd-->


# Holder

Placeholder



<!--chapter:end:holder.Rmd-->


# Note 510C

Placeholder



<!--chapter:end:note_510c.Rmd-->


# Note dissertation

Placeholder



<!--chapter:end:note_dissertation.Rmd-->


# Note granter

Placeholder



<!--chapter:end:note_granter.Rmd-->


# Note source

Placeholder



<!--chapter:end:note_source.Rmd-->


# Publisher preprocessing summary

Placeholder



<!--chapter:end:publisher.Rmd-->

```{r source-publication-interval, include=FALSE, eval=knit_bookdown}
#publication_interval field
source("publication_interval.R")
```

# Publication interval summaries

Publication interval is available for `r sum(!is.na(df$publication_interval_from) | !is.na(df$publication_interval_till))` documents (`r round(100*mean(!is.na(df$publication_interval_from) | !is.na(df$publication_interval_till)))`%). 

[Publication interval accepted](output.tables/publication_interval_accepted.csv)

[Publication interval conversions](output.tables/publication_interval_conversion_nontrivial.csv)

[Publication interval discarded](output.tables/publication_interval_discarded.csv)



<!--chapter:end:publication_interval.Rmd-->


# Publication place preprocessing summary

Placeholder


## Publication countries	
## Geocoordinates

<!--chapter:end:publication_place.Rmd-->

```{r source-publication-time, include=FALSE, eval=knit_bookdown}
# Publication place field and derived country- and geoinformation
source("publication_time.R")
```

# Publication year summaries (publication time)

[Publication year conversions](output.tables/publication_year_conversion.csv)

[Publication year discarded](output.tables/publication_year_discarded.csv)

Publication year is available for `r sum(!is.na(df$publication_year))` documents (`r round(100*mean(!is.na(df$publication_year)))`%). The publication years span `r paste(range(na.omit(df$publication_year)), collapse = "-")`.

```{r summarypublicationyear, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
# Title count per decade
df2 <- df %>% group_by(publication_decade) %>% filter(publication_decade < 2010) 
p <- ggplot(df2, aes(publication_decade)) +
     geom_bar() + scale_y_log10() +
     ggtitle("Title count timeline")
print(p)
```



<!--chapter:end:publication_time.Rmd-->


# Subject topic

Placeholder



<!--chapter:end:subject_topic.Rmd-->

```{r source-subject-geography, include=FALSE, eval=knit_bookdown}
# note_subject_topic field
source("subject_geography.R")
```

# Subject geography preprocessing summary (Subject geographical places)

```{r geo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
tab <- rev(sort(table(unlist(strsplit(as.character(df$subject_geography), ";")))))
```

Top-`r ntop` geographical places are shown together with the number of documents assigned to that region. Geography information is available for `r sum(!is.na(df$subject_geography))` documents (`r round(100*mean(!is.na(df$subject_geography)))`%). There are `r length(tab)` unique geographical places.

```{r geo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10, eval=FALSE}
ntop <- 50
par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common geographic places")
```

```{r geo3, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/geoplaces.csv"
write.table(cbind(Geography = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
```

[Complete geoplace listing](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/geoplaces.csv)



<!--chapter:end:subject_geography.Rmd-->


# Successor

Placeholder



<!--chapter:end:successor.Rmd-->


# Title field: summary

Placeholder



<!--chapter:end:title.Rmd-->


# Title uniform

Placeholder



<!--chapter:end:title_uniform.Rmd-->


# Uncontrolled

Placeholder



<!--chapter:end:uncontrolled.Rmd-->


# Fennica preprocessing summary

Placeholder



<!--chapter:end:overview.Rmd-->

