--- 
title: "Harmonized Finnish National Bibliography"
author: "Turku Data Science Group"
date: "`r Sys.Date()`"
site: "bookdown::bookdown_site"
output:
  bookdown::gitbook: default
documentclass: book
---

# Preface chapter

Placeholder



<!--chapter:end:index.Rmd-->

# Author's lifetime

```{r source-author-date, include=FALSE}
# author_date field
source("author_date.R")
```

[Author date accepted](output.tables/auhtor_date_accepted.csv)

[Author date discarded](output.tables/auhtor_date_discarded.csv)

Author's lifetime is available for `r sum(!is.na(df$author_age))` authors (`r round(100*mean(!is.na(df$author_age)))`%).The lifetime years span `r range(na.omit((df$author_age)))`. The youngest being 17 years old and the oldest 99 years old as at this stage of research.





<!--chapter:end:author_date.Rmd-->

# Author's name

```{r setup-author-name, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

```{r source-author-name, include=FALSE}
# author_name field
source("author_name.R")
```

* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)
 
 Top-`r ntop` titles and their title counts.
 
```{r summarytitle-author-name, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "author_name", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
``` 

Frequency of unique titles:
  
```{r uniquetitles-author-name, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$author_name)
d <- data.frame(title = names(tab), n = as.numeric(tab))

library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- ggplot(d, aes(x = n)) +
  geom_histogram(color="black", fill="white") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```


## Authors

* `r length(unique(df$author_name))` [unique authors](output.tables/author_accepted.csv) These final names capture all name variants from the custom [author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv), and exclude known pseudonymes (see below). If multiple names for the same author are still observed on this list, they should be added on the [author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv).
 * `r sum(!is.na(df$author_name))` documents have unambiguous author information (`r round(100*mean(!is.na(df$author_name)))`%). 
 * `r length(readLines(paste0(getwd(),"/output.tables/pseudonyme_accepted.csv")))-2` [unique pseudonymes](output.tables/pseudonyme_accepted.csv) are recognized based on [custom pseudonyme lists](https://github.com/COMHIS/fennica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv).
 * `r length(readLines(paste0(getwd(),"/output.tables/author_discarded.csv")))-2` [discarded author names](output.tables/author_discarded.csv) This list should not include any real authors (if it does, please send a note to the admin). The stopword lists are considered when discarding names.
 * [Author name conversions](output.tables/author_conversion_nontrivial.csv) Non-trivial conversions from the original raw data to final names.
 
### Auxiliary files

 * [Author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv)
 * [Stopwords for names](https://github.com/COMHIS/fennica/blob/master/inst/extdata/stopwords_for_names.csv)
 * [Stopwords for titles](https://github.com/COMHIS/fennica/blob/master/inst/extdata/stopwords_titles.csv)
 * [Custom pseudonyme lists](https://github.com/COMHIS/fennica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv)
 
Top-`r ntop` uniquely identified authors and their productivity (title count).

```{r summaryauthorsnames, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
knitr::opts_chunk$set(fig.path = "figure/", dev="CairoPNG")
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- NULL
p <- top_plot(df, "author_name", ntop) +
     		  ggtitle(paste("Top authors' names")) +
		  ylab("Documents")
print(p)
```


### Author productivity

Title count in relation to the paper consumed in their books(all authors):

```{r authortitlespapers, fig.height=8, fig.width=18, echo=FALSE, warning=FALSE}
library(dplyr)
library(gridExtra)
library(grid)
library(ggplot2)
library(lattice)

theme_set(theme_bw(base_size = 12))
res1 <- compare_title_paper(df, "author_name", plot.mode = "text")
res2 <- compare_title_paper(df, "author_name", plot.mode = "point")
grid.arrange(res2$plot, res1$plot, nrow = 1)
#kable(res1$table)
```



<!--chapter:end:author_name.Rmd-->


# Corporate

Placeholder



<!--chapter:end:corporate.Rmd-->


# Language summaries

Placeholder


## Top languages

<!--chapter:end:language.Rmd-->


# Holder

Placeholder



<!--chapter:end:holder.Rmd-->


# Note 510C

Placeholder



<!--chapter:end:note_510c.Rmd-->


# Note dissertation

Placeholder



<!--chapter:end:note_dissertation.Rmd-->


# Note granter

Placeholder



<!--chapter:end:note_granter.Rmd-->


# Note source

Placeholder



<!--chapter:end:note_source.Rmd-->


# Publisher preprocessing summary

Placeholder



<!--chapter:end:publisher.Rmd-->

```{r source-publication-interval, include=FALSE, eval=knit_bookdown}
#publication_interval field
source("publication_interval.R")
```

# Publication interval summaries

Publication interval is available for `r sum(!is.na(df$publication_interval_from) | !is.na(df$publication_interval_till))` documents (`r round(100*mean(!is.na(df$publication_interval_from) | !is.na(df$publication_interval_till)))`%). 

[Publication interval accepted](output.tables/publication_interval_accepted.csv)

[Publication interval conversions](output.tables/publication_interval_conversion_nontrivial.csv)

[Publication interval discarded](output.tables/publication_interval_discarded.csv)



<!--chapter:end:publication_interval.Rmd-->


# Publication place preprocessing summary

Placeholder


## Publication countries	
## Geocoordinates

<!--chapter:end:publication_place.Rmd-->

```{r source-publication-time, include=FALSE, eval=knit_bookdown}
# Publication place field and derived country- and geoinformation
source("publication_time.R")
```

# Publication year summaries (publication time)

[Publication year conversions](output.tables/publication_year_conversion.csv)

[Publication year discarded](output.tables/publication_year_discarded.csv)

Publication year is available for `r sum(!is.na(df$publication_year))` documents (`r round(100*mean(!is.na(df$publication_year)))`%). The publication years span `r paste(range(na.omit(df$publication_year)), collapse = "-")`.

```{r summarypublicationyear, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
# Title count per decade
df2 <- df %>% group_by(publication_decade) %>% filter(publication_decade < 2010) 
p <- ggplot(df2, aes(publication_decade)) +
     geom_bar() + scale_y_log10() +
     ggtitle("Title count timeline")
print(p)
```



<!--chapter:end:publication_time.Rmd-->


# Subject topic

Placeholder



<!--chapter:end:subject_topic.Rmd-->

```{r source-subject-geography, include=FALSE, eval=knit_bookdown}
# note_subject_topic field
source("subject_geography.R")
```

# Subject geography preprocessing summary (Subject geographical places)

```{r geo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
tab <- rev(sort(table(unlist(strsplit(as.character(df$subject_geography), ";")))))
```

Top-`r ntop` geographical places are shown together with the number of documents assigned to that region. Geography information is available for `r sum(!is.na(df$subject_geography))` documents (`r round(100*mean(!is.na(df$subject_geography)))`%). There are `r length(tab)` unique geographical places.

```{r geo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10, eval=FALSE}
ntop <- 50
par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common geographic places")
```

```{r geo3, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/geoplaces.csv"
write.table(cbind(Geography = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
```

[Complete geoplace listing](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/geoplaces.csv)



<!--chapter:end:subject_geography.Rmd-->


# Successor

Placeholder



<!--chapter:end:successor.Rmd-->


# Title field: summary

Placeholder



<!--chapter:end:title.Rmd-->


# Title uniform

Placeholder



<!--chapter:end:title_uniform.Rmd-->


# Uncontrolled

Placeholder



<!--chapter:end:uncontrolled.Rmd-->


# Fennica preprocessing summary

Placeholder



<!--chapter:end:overview.Rmd-->

