---
title: "Author's info: name, dates, gender, profession"
hide-description: false
description: ""
---
```{r}
#| include = FALSE

library(devtools)
library(dplyr)
library(tidyr)
library(tm)
library(stringr)
library(knitr)
library(R.utils)
library(ggplot2)
library(Cairo)
library(purrr)
library(stringi)
library(parallel)
library(qdapRegex)
library(readxl)
library(arrow)
library(textutils)
library(data.table)
library(brms)
library(rnaturalearth)

# source("author_info_data-scripts.R") run this to construct the author_database from scratch
# or read existing one 

author_database <- read.delim(
  "author_database.csv",
  stringsAsFactors = FALSE
)

```
# Author Database

## Description

The author database was created by combining author information from MARC 100 (main authors) and MARC 700 (added authors) fields. Authors were identified primarily through Asteri authority identifiers when available. Records lacking authority identifiers were retained using harmonized author names.

The resulting database represents unique authors appearing in the Fennica dataset and serves as a foundation for author-level analyses and metadata enrichment. Author records were enriched using information obtained from Kanto authority data, including birth and death years, profession, language, country, field of activity, place associations, and related persons. Additional variables include inferred gender, publication activity measures, and the number of Fennica records associated with each author.

Publication activity was calculated from publication years recorded in Fennica and includes the first observed publication year, last observed publication year, mean publication year, and activity span.

## Complete Dataset Overview

Unique authors: `r nrow(author_database)`.

Authors with Asteri identifier: `r sum(!is.na(author_database$asteri_id))` (`r round(mean(!is.na(author_database$asteri_id))*100,1)`%).

Authors without Asteri identifier: `r sum(is.na(author_database$asteri_id))` (`r round(mean(is.na(author_database$asteri_id))*100,1)`%).

Authors with birth year information: `r sum(!is.na(author_database$from))`.

Authors with death year information: `r sum(!is.na(author_database$till))`.

Authors with calculated age: `r sum(!is.na(author_database$author_age))`.

Authors with gender information: `r sum(!is.na(author_database$gender))`.

Authors with profession information: `r sum(!is.na(author_database$profession))`.

Authors with field of activity information: `r sum(!is.na(author_database$field_activity))`.

Authors with language information: `r sum(!is.na(author_database$language))`.

Authors with country information: `r sum(!is.na(author_database$country))`.

Authors with place information: `r sum(!is.na(author_database$place))`.

### Metadata Coverage

```{r}
summary_table <- tibble(
  metric = c(
    "Unique authors",
    "Authors with Asteri ID",
    "Authors without Asteri ID",
    "Authors with birth year",
    "Authors with death year",
    "Authors with age",
    "Authors with gender",
    "Authors with profession",
    "Authors with field of activity",
    "Authors with place",
    "Authors with language"
  ),
  n = c(
    nrow(author_database),
    sum(!is.na(author_database$asteri_id)),
    sum(is.na(author_database$asteri_id)),
    sum(!is.na(author_database$from)),
    sum(!is.na(author_database$till)),
    sum(!is.na(author_database$author_age)),
    sum(!is.na(author_database$gender)),
    sum(!is.na(author_database$profession)),
    sum(!is.na(author_database$field_activity)),
    sum(!is.na(author_database$place)),
    sum(!is.na(author_database$language))
  )
)

summary_table
```

### Top 20 Authors by Number of Associated Records

```{r}
  ## 2. Top authors by number of records
  
  top_authors <- author_database %>%
  arrange(desc(n_records)) %>%
  select(author_name, n_records) %>%
  slice_head(n = 20)

top_authors
```

### Authority Control Coverage

```{r}
  ## 3. Authors with and without authority control
  

author_database %>%
  summarise(
    with_asteri = sum(!is.na(asteri_id)),
    without_asteri = sum(is.na(asteri_id))
  )

author_database %>%
  summarise(
    pct_with_asteri =
      round(mean(!is.na(asteri_id))*100,1)
  )
```

### Gender Distribution

```{r}

  ## 4. Gender distribution
  

gender_table <- author_database %>%
  count(gender, sort = TRUE) %>%
  mutate(
    pct = round(100*n/sum(n),1)
  )

gender_table

```

### Age Statistics

```{r}
  ## 5. Age statistics
  

author_database %>%
  summarise(
    n = sum(!is.na(author_age)),
    mean = mean(author_age, na.rm=TRUE),
    median = median(author_age, na.rm=TRUE),
    min = min(author_age, na.rm=TRUE),
    max = max(author_age, na.rm=TRUE)
  )

```

### Birth Decades

```{r}
  ## 6. Birth year coverage
  

author_database %>%
  mutate(
    birth_decade = floor(as.numeric(from)/10)*10
  ) %>%
  count(birth_decade, sort=TRUE)
```

### Most Common Professions

```{r}
professions <- author_database %>%
  separate_rows(profession, sep=",\\s*") %>%
  filter(!is.na(profession)) %>%
  count(profession, sort=TRUE)

head(professions,20)
```

### Most Common Fields of Activity

```{r}
activities <- author_database %>%
  separate_rows(field_activity, sep=";\\s*") %>%
  filter(!is.na(field_activity)) %>%
  count(field_activity, sort=TRUE)

head(activities,20)
```

### Languages

```{r}
languages <- author_database %>%
  separate_rows(language, sep=";\\s*") %>%
  filter(!is.na(language)) %>%
  count(language, sort=TRUE)

head(languages,20)
```

### Countries

```{r}
 ## 10. Countries
  

countries <- author_database %>%
  separate_rows(country, sep=";\\s*") %>%
  filter(!is.na(country)) %>%
  count(country, sort=TRUE)

head(countries,20)
```

### Places Associated with Authors

```{r}
places <- author_database %>%
  separate_rows(place, sep=";\\s*") %>%
  filter(!is.na(place)) %>%
  count(place, sort=TRUE)

head(places,20)
```

### Metadata Completeness by Authority Status

```{r}
author_database %>%
  mutate(
    authority =
      ifelse(is.na(asteri_id),
             "No Asteri",
             "Asteri")
  ) %>%
  group_by(authority) %>%
  summarise(
    birth = mean(!is.na(from))*100,
    age = mean(!is.na(author_age))*100,
    gender = mean(!is.na(gender))*100,
    profession = mean(!is.na(profession))*100,
    language = mean(!is.na(language))*100,
    activity = mean(!is.na(field_activity))*100
  )
```

### Record Count Distribution

```{r}
author_database %>%
  mutate(
    records_group = case_when(
      n_records == 1 ~ "1",
      n_records <= 5 ~ "2-5",
      n_records <= 10 ~ "6-10",
      n_records <= 20 ~ "11-20",
      TRUE ~ "20+"
    )
  ) %>%
  count(records_group)
```

### Authors with Richest Metadata

```{r}
author_database %>%
  mutate(
    metadata_score =
      rowSums(!is.na(across(
        c(
          gender,
          profession,
          language,
          country,
          field_activity,
          place,
          from,
          till
        )
      )))
  ) %>%
  arrange(desc(metadata_score))
```


