---
title: "Author's info: lifespan"
hide-description: false
description: ""
---

```{r}
#| include = FALSE
source("init.R")
source("publication_time.R")
source("author_date.R")
```

MARC: [100d](https://www.loc.gov/marc/bibliographic/bd100.html)

The author's lifetime section furnishes concise summaries following an extensive cleaning process, delineating the accepted and discarded years pertaining to each author.The accepted years signify the refined and validated data, while insights into the discarded years offer valuable context, shedding light on the challenges encountered and decisions made during the cleaning procedure.

## Complete Dataset Overview
The field has `r sum(is.na(df[[field]]))` / (`r round(100*mean(is.na(df[[field]])), 1)`%) missing values and  `r sum(!is.na(df[[field]]))` / (`r round(100*mean(!is.na(df_19[[field]])), 1)`%) with non-missing lifetime information.

[Author date accepted for the complete Fennica](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_date_accepted.csv)

[Author date discarded for the complete Fennica](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_date_discarded.csv)

## Subset Analysis: 1809-1917

[Author date accepted for 1809-1917](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_date_accepted_19.csv)

[Author date discarded for 1809-1917](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_date_discarded_19.csv)

```{r}
#| label = "summarytitle-author-date",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 8,
#| fig.height = 6

library(dplyr)
library(ggplot2)

# Step 1: Filter out rows without a known age

author_df$age <- df$author_age
author_df_clean <- author_df %>%
  filter(!is.na(age), publication_decade >= 1800)

# Step 2: For each author, get their first publication and corresponding age
first_pub <- author_df_clean %>%
  group_by(melinda_id) %>%
  arrange(publication_year, .by_group = TRUE) %>%
  summarise(
    first_pub_year = first(publication_year),
    first_pub_age  = first(age),
    .groups = "drop"
  )

# Step 3: Compute the average (and median) age of debut by year
avg_age_by_year <- first_pub %>%
  group_by(first_pub_year) %>%
  summarise(
    mean_age = mean(first_pub_age, na.rm = TRUE),
    median_age = median(first_pub_age, na.rm = TRUE),
    n_authors = n(),
    .groups = "drop"
  )

ggplot(avg_age_by_year, aes(x = first_pub_year, y = mean_age)) +
  geom_point(color = "steelblue", size = 1.5, alpha = 0.6) +
  geom_smooth(
    method = "loess",    # local polynomial smoothing
    se = FALSE,          # remove grey confidence band (set to TRUE if you want it)
    color = "darkred",
    linewidth = 1.2
  ) +
  labs(
    x = "Year of First Publication",
    y = "Average Age at First Publication",
    title = "Smoothed Trend in Average Age at First Publication (1800–Present)"
  ) +
  theme_minimal(base_size = 13)

```

