---
title: "Author's info"
hide-description: false
description: ""
---

```{r}
#| include = FALSE
source("init.R")
source("publication_time.R")
source("author_name.R")
```

## Author name Fennica

MARC: [100a](https://www.loc.gov/marc/bibliographic/bd100.html)

Author's name section's summary tables offer insights into the dataset's integrity, illustrating the accepted and discarded author names. An examination of missing values in the original dataset provides transparency regarding data completeness. The inclusion of information on name variants and pseudonyms enriches the analysis, addressing nuances in authorship representation. This comprehensive approach ensures a thorough understanding of the dataset's composition and the intricacies associated with author identification.

### Complete Dataset Overview

-   [Unique accepted entries in original data](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_name_accepted.csv): `r length(unique(df[[field]]))`
-   [Unique discarded entries in original data](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_name_discarded.csv) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
-   Original documents with non-NA titles `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
-   Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)

#### Authors

-   `r length(unique(df$author_name))` [unique authors](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_name_accepted.csv) These final names capture all name variants from the custom [author synonyme table](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/ambiguous-authors.csv), and exclude known pseudonymes (see below). If multiple names for the same author are still observed on this list, they should be added on the [author synonyme table](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/ambiguous-authors.csv).

-   `r sum(!is.na(df$author_name_h))` documents have unambiguous author information (`r round(100*mean(!is.na(df$author_name_h)))`%).

-   [Author name conversions](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_conversion_nontrivial.csv) Non-trivial conversions from the original raw data to final names.

#### Auxiliary files

-   [Author synonyme table](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/ambiguous-authors.csv)
-   [Stopwords for names](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/stopwords_for_names.csv)
-   [Stopwords for titles](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/stopwords_titles.csv)
-   [Custom pseudonyme lists](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/custom_pseudonymes.csv)

### Subset Analysis: 1809-1917

-   [Unique accepted entries for for 1809-1917 years](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_name_accepted_19.csv): `r length(unique(df_19[[field]]))`

-   [Unique discarded entries in original data](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_name_discarded_19.csv) (excluding NA cases): `r as.vector(countLines(file_discarded_19) - 1)`

Top-`r ntop` titles and their title counts for period 1809-1917.

The accompanying plot visually underscores the prominence of these authors, emphasizing the metric of the number of unique titles published by each author.

```{r}
#| label = "summarytitle-author-name",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 8,
#| fig.height = 6
library(ggplot2)
#library(comhis)

theme_set(theme_bw(base_size = 12))
p <- top_plot(df_19, "author_name", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

## Gender

Gender information is not originally included in Fennica. We enriched the data by linking author names with gender information from various sources, including the HENKO project, the Genderize dataset, and additional records provided by the National Library of Finland. The full list of names and genders can be found
[here](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/fennica_name_genders.csv)

```{r}
#| include: false
#| message: false
source("gender.R")
```

In total N = `r nrow(df)` records. After enrichmnet in total there are records `r sum(!is.na(df[[field]]))` / (`r round(100*mean(!is.na(df[[field]])), 1)`%) with assigned gender. There are `r sum(df[[field]] == "female", na.rm = TRUE)` (`r round(100*mean(df[[field]] == "female", na.rm = TRUE), 1)`%) female names, `r sum(df[[field]] == "male", na.rm = TRUE)` (`r round(100*mean(df[[field]] == "male", na.rm = TRUE), 1)`%) male names and `r sum(df[[field]] == "unisex", na.rm = TRUE)` (`r round(100*mean(df[[field]] == "unisex", na.rm = TRUE), 1)`%) unisex names. 

### Genres over Time
```{r}
#| label = "summary_gender",
#| echo = FALSE,
#| warning = FALSE,
# Join publication_decade from df_pubtime to df by melinda_id
df$publication_decade <- df_pubtime$publication_decade[match(df$melinda_id, df_pubtime$melinda_id)]

# Filter your data to only include those genres
df_selected <- df%>%
  filter(!is.na(publication_decade), 
         !is.na(df$gender),
         publication_decade <= 1950)

# Summarize counts by decade and genre
df_summary <- df_selected %>%
  group_by(publication_decade, gender) %>%
  summarise(n = n(), .groups = "drop")

ggplot(df_summary, aes(x = publication_decade,y = n, fill = gender)) +
  geom_col(position = "stack", width = 8) +  # width makes bars a bit narrower
  labs(x = "Publication Decade", y = "Gender count", fill = "Gender") +
  scale_fill_brewer(palette = "Set2") +
  scale_x_continuous(limits = c(1600, 1950),breaks = seq(1600, 1950, by = 50)) +
  theme_minimal()

```
