---
title: "Author's info: profession"
hide-description: false
description: ""
---

```{r}
#| include: FALSE
source("init.R")
source("publication_time.R")
source("author_profession.R")
```

## Author profession

Author profession information in Fennica is derived from the KANTO authority database. The field records occupational information linked to authors when such information is available.

The dataset contains N = `r nrow(df)` records. Profession information is missing for `r sum(is.na(df[[field]]))` / (`r round(100*mean(is.na(df[[field]])), 1)`%) of the dataset. 

[Accepted entries and their count](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_profession_accepted.csv): `r as.character(countLines(file_accepted) - 1)`.

[Discarded entries and their count](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_profession_discarded.csv) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`.

[List of unique professions](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_profession_unique.csv):`r as.vector(countLines(file_unique) - 1)`. 

```{r}
#| label = "summaryproffesion",
#| echo = FALSE,
#| results = "asis"
x <- top(df, "author_profession")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("Profession", "Entries (n)", "Fraction (%)")
kable(head(tab, 15))
```