---
title: "Author's info: name, dates, gender, profession"
hide-description: false
description: ""
---


```{r}
#| include: false
#| echo: false
#| message: false
#| warning: false

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

source("init.R")
```



```{r}
# # Download the csv file
url <- "https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/all_author_info.csv"

author_database <- read.delim(
  url,
  quote = "",
  fill = TRUE,
  stringsAsFactors = FALSE,
  check.names = FALSE
)

author_database <- author_database %>%
  mutate(
    across(
      where(is.character),
      ~ {
        x <- trimws(.x)
        x[x %in% c("", "NA", "N/A", "NULL", "-")] <- NA_character_
        x
      }
    )
  )

author_database <- author_database %>%
  mutate(
    gender = trimws(gender),
    gender = na_if(gender, ""),
    gender = na_if(gender, "Unknown"),

    # Take the first value from semicolon-separated gender values
    gender_primary = trimws(sub("[|/].*$", "", gender)),
    gender_primary = na_if(gender_primary, ""),
    gender_primary = na_if(gender_primary, "Unknown")
  )
```


# Author Database

## Description

The author database was created by combining author information from MARC 100 (main authors) and MARC 700 (added authors) fields. Authors were identified primarily through Asteri authority identifiers when available. Records lacking authority identifiers were retained using harmonized author names.

The resulting database represents unique authors appearing in the Fennica dataset and serves as a foundation for author-level analyses and metadata enrichment. Author records were enriched using information obtained from Kanto authority data, including birth and death years, profession, language, country, field of activity, place associations, and related persons. Additional variables include inferred gender, publication activity measures, and the number of Fennica records associated with each author.

Publication activity was calculated from publication years recorded in Fennica and includes the first observed publication year, last observed publication year, mean publication year, and activity span.

## Complete Dataset Overview

Unique authors: `r unique(author_database$all_names)` (`r round(mean(!is.na(author_database$all_names)) * 100, 1)`%)

Authors with Asteri identifier: `r sum(!is.na(author_database$all_asteri))` (`r round(mean(!is.na(author_database$all_asteri)) * 100, 1)`%).

Authors with birth year information: `r sum(!is.na(author_database$all_dates))` (`r round(mean(!is.na(author_database$all_dates)) * 100, 1)`%).

Authors with death year information: `r sum(!is.na(author_database$till))` (`r round(mean(!is.na(author_database$till)) * 100, 1)`%).

Authors with calculated age: `r sum(!is.na(author_database$author_age))` (`r round(mean(!is.na(author_database$author_age)) * 100, 1)`%).

Authors with gender information: `r sum(!is.na(author_database$gender_primary))` (`r round(mean(!is.na(author_database$gender_primary)) * 100, 1)`%).

Authors with profession information: `r sum(!is.na(author_database$profession))` (`r round(mean(!is.na(author_database$profession)) * 100, 1)`%).

Authors with field of activity information: `r sum(!is.na(author_database$fieldOfActivityOfPerson))` (`r round(mean(!is.na(author_database$fieldOfActivityOfPerson)) * 100, 1)`%).

Authors with language information: `r sum(!is.na(author_database$language))` (`r round(mean(!is.na(author_database$language)) * 100, 1)`%).

Authors with country information: `r sum(!is.na(author_database$country))` (`r round(mean(!is.na(author_database$country)) * 100, 1)`%).

Authors with place information: `r sum(!is.na(author_database$place))` (`r round(mean(!is.na(author_database$place)) * 100, 1)`%).




# Top Authors' names

```{r}
#| label = "top_author_name",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 8,
#| fig.height = 6
library(ggplot2)
#library(comhis)

theme_set(theme_bw(base_size = 12))
p <- top_plot(author_database, "all_names", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top author names (Log values)")
print(p)
```

```{r}
#| label = "adb_profession",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 8,
#| fig.height = 6
library(ggplot2)
#library(comhis)

theme_set(theme_bw(base_size = 12))
p <- top_plot(author_database, "profession", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top author professions (Log values)")
print(p)
```


```{r}
#| label = "adb_title",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 8,
#| fig.height = 6
library(ggplot2)
#library(comhis)

theme_set(theme_bw(base_size = 12))
p <- top_plot(author_database, "title", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top author title (Log values)")
print(p)
```

```{r}
#| label = "adb_language",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 12,
#| fig.height = 6
library(ggplot2)
#library(comhis)

theme_set(theme_bw(base_size = 12))
p <- top_plot(author_database, "language", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top  author language (Log values)")
print(p)
```
```{r}
#| label = "adb_field_activity",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 12,
#| fig.height = 6
library(ggplot2)
#library(comhis)

theme_set(theme_bw(base_size = 12))
p <- top_plot(author_database, "fieldOfActivityOfPerson", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top  author field activity (Log values)")
print(p)
```
```{r}
#| label = "adb_country",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 12,
#| fig.height = 6
library(ggplot2)
#library(comhis)

theme_set(theme_bw(base_size = 12))
p <- top_plot(author_database, "country", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top  author country (Log values)")
print(p)
```

[Download author database dataset for all authors in Fennica](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_database.csv)

```{r}
author_database <- author_database[author_database$id %in% ids_19,]
```


## Authors 1809-1917

Unique authors: `r unique(author_database$all_names)` (`r round(mean(!is.na(author_database$all_names)) * 100, 1)`%)

Authors with Asteri identifier: `r sum(!is.na(author_database$all_asteri))` (`r round(mean(!is.na(author_database$all_asteri)) * 100, 1)`%).

Authors without Asteri identifier: `r sum(is.na(author_database$all_dates))` (`r round(mean(is.na(author_database$all_dates)) * 100, 1)`%).

Authors with birth year information: `r sum(!is.na(author_database$from))` (`r round(mean(!is.na(author_database$from)) * 100, 1)`%).

Authors with death year information: `r sum(!is.na(author_database$till))` (`r round(mean(!is.na(author_database$till)) * 100, 1)`%).

Authors with calculated age: `r sum(!is.na(author_database$author_age))` (`r round(mean(!is.na(author_database$author_age)) * 100, 1)`%).

Authors with gender information: `r sum(!is.na(author_database$gender_primary))` (`r round(mean(!is.na(author_database$gender_primary)) * 100, 1)`%).

Authors with profession information: `r sum(!is.na(author_database$profession))` (`r round(mean(!is.na(author_database$profession)) * 100, 1)`%).

Authors with field of activity information: `r sum(!is.na(author_database$field_activity))` (`r round(mean(!is.na(author_database$field_activity)) * 100, 1)`%).

Authors with language information: `r sum(!is.na(author_database$language))` (`r round(mean(!is.na(author_database$language)) * 100, 1)`%).

Authors with country information: `r sum(!is.na(author_database$country))` (`r round(mean(!is.na(author_database$country)) * 100, 1)`%).

Authors with place information: `r sum(!is.na(author_database$place))` (`r round(mean(!is.na(author_database$place)) * 100, 1)`%).



### Top-Authors' names 1809-1917

```{r}
#| label: top_authors_1809_1917
#| echo: false
#| results: asis

theme_set(theme_bw(base_size = 12))
p <- top_plot(author_database, "all_names", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top  author names 1809-1917 (Log values)")
print(p)
```

# Authors by gender 1809-1917

```{r}

tab <- author_database %>%
  filter(!is.na(gender_primary)) %>%
  count(gender_primary, sort = TRUE) %>%
  mutate(
    `Fraction (%)` = round(100 * n / sum(n), 1)
  )

kable(tab)
```

```{r}
#| label = "adb_profession19",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 8,
#| fig.height = 6
library(ggplot2)
#library(comhis)

theme_set(theme_bw(base_size = 12))
p <- top_plot(author_database, "profession", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top  author professions 1809-1917 (Log values)")
print(p)
```
```{r}
#| label = "adb_language19",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 12,
#| fig.height = 6
library(ggplot2)
#library(comhis)

theme_set(theme_bw(base_size = 12))
p <- top_plot(author_database, "language", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top  author language 1809-1917 (Log values)")
print(p)
```

[Download author database dataset for authors in Fennica for years 1809-1917 ](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_database_19.csv)


