---
title: "Author's name"
hide-description: false
description: "statistics about the authors and their productivity"
---

```{r}
#| include = FALSE
source("init.R")
source("author_name.R")
```

Author's name section

## Complete Dataset Overview

-   Unique accepted entries in original data (dataTable/data_table.html?path=../output.tables/author_name_accepted.csv): `r length(unique(df.orig[[field]]))`
-   [Unique discarded entries in original data](dataTable/data_table.html?path=../output.tables/author_name_accepted.csv) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
-   Original documents with non-NA titles `r sum(!is.na(df.orig[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
-   Original documents with missing (NA) titles `r sum(is.na(df.orig[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)

### Authors

-   `r length(unique(df$author_name))` [unique authors](dataTable/data_table.html?path=../output.tables/author_accepted.csv) These final names capture all name variants from the custom [author synonyme table](dataTable/data_table.html?path=../output.tables/ambiguous-authors.csv), and exclude known pseudonymes (see below). If multiple names for the same author are still observed on this list, they should be added on the [author synonyme table](dataTable/data_table.html?path=../output.tables/ambiguous-authors.csv).
-   `r sum(!is.na(df$author_name))` documents have unambiguous author information (`r round(100*mean(!is.na(df$author_name)))`%).
-   `r length(readLines(paste0(getwd(),"/output.tables/pseudonyme_accepted.csv")))-2` [unique pseudonymes](dataTable/data_table.html?path=../output.tables/pseudonyme_accepted.csv) are recognized based on [custom pseudonyme lists](dataTable/data_table.html?path=../output.tables/custom_pseudonymes.csv).
-   `r length(readLines(paste0(getwd(),"/output.tables/author_discarded.csv")))-2` [discarded author names](dataTable/data_table.html?path=../output.tables/author_discarded.csv) This list should not include any real authors (if it does, please send a note to the admin). The stopword lists are considered when discarding names.
-   [Author name conversions](dataTable/data_table.html?path=../output.tables/author_conversion_nontrivial.csv) Non-trivial conversions from the original raw data to final names.

### Auxiliary files

-   [Author synonyme table](dataTable/data_table.html?path=../output.tables/ambiguous-authors.csv)
-   [Stopwords for names](dataTable/data_table.html?path=../output.tables/stopwords_for_names.csv)
-   [Stopwords for titles](dataTable/data_table.html?path=../output.tables/stopwords_titles.csv)
-   [Custom pseudonyme lists](dataTable/data_table.html?path=../output.tables/custom_pseudonymes.csv)

## Subset Analysis: 1809-1917

-   [Unique accepted entries for for 1809-1917 years](dataTable/data_table.html?path=../output.tables/author_name_accepted_19.csv): `r length(unique(df[[field]]))`

Top-`r ntop` titles and their title counts. 1809-1917

```{r}
#| label = "summarytitle-author-name",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 8,
#| fig.height = 6
library(ggplot2)
library(comhis)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "author_name", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

Frequency of unique titles 1809-1917:

```{r}
#| label = "uniquetitles-author-name",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 8,
#| fig.height = 6
tab <- table(df$author_name)
d <- data.frame(title = names(tab), n = as.numeric(tab))

library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- ggplot(d, aes(x = n)) +
  geom_histogram(color="black", fill="white") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```

