---
title: "Author's info: name, dates, gender, profession"
hide-description: false
description: ""
---

```{r}
#| include = FALSE
source("init.R")
source("publication_time.R")
source("author_name.R")
```

```{r}
#| include = FALSE
author_df <- df
author_df$publication_year <- df_pubtime$publication_year
author_df$publication_decade <- df_pubtime$publication_decade
```

## Author name Fennica

MARC: [100a](https://www.loc.gov/marc/bibliographic/bd100.html)

Author's name section's summary tables offer insights into the dataset's integrity, illustrating the accepted and discarded author names. An examination of missing values in the original dataset provides transparency regarding data completeness. The inclusion of information on name variants and pseudonyms enriches the analysis, addressing nuances in authorship representation. This comprehensive approach ensures a thorough understanding of the dataset's composition and the intricacies associated with author identification.

### Complete Dataset Overview

-   [Unique accepted entries in original data](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_name_accepted.csv): `r length(unique(df[[field]]))`
-   [Unique discarded entries in original data](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_name_discarded.csv) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
-   Original documents with non-NA titles `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
-   Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)

#### Authors

-   `r length(unique(df$author_name))` [unique authors](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_name_accepted.csv) These final names capture all name variants from the custom [author synonyme table](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/ambiguous-authors.csv), and exclude known pseudonymes (see below). If multiple names for the same author are still observed on this list, they should be added on the [author synonyme table](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/ambiguous-authors.csv).

-   `r sum(!is.na(df$author_name_h))` documents have unambiguous author information (`r round(100*mean(!is.na(df$author_name_h)))`%).

-   [Author name conversions](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_conversion_nontrivial.csv) Non-trivial conversions from the original raw data to final names.

#### Auxiliary files

-   [Author synonyme table](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/ambiguous-authors.csv)
-   [Stopwords for names](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/stopwords_for_names.csv)
-   [Stopwords for titles](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/stopwords_titles.csv)
-   [Custom pseudonyme lists](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/custom_pseudonymes.csv)

### Subset Analysis: 1809-1917

-   [Unique accepted entries for for 1809-1917 years](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_name_accepted_19.csv): `r length(unique(df_19[[field]]))`

-   [Unique discarded entries in original data](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_name_discarded_19.csv) (excluding NA cases): `r as.vector(countLines(file_discarded_19) - 1)`

Top-`r ntop` titles and their title counts for period 1809-1917.

The accompanying plot visually underscores the prominence of these authors, emphasizing the metric of the number of unique titles published by each author.

```{r}
#| label = "summarytitle-author-name",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 8,
#| fig.height = 6
library(ggplot2)
#library(comhis)

theme_set(theme_bw(base_size = 12))
p <- top_plot(df_19, "author_name", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```
# Author's name after integration

```{r}
#| include = FALSE
#source("author_date.R")
```

# Author's date

```{r}
#| include = FALSE
source("author_date.R")
```

## Author's lifetime
MARC: [100d](https://www.loc.gov/marc/bibliographic/bd100.html)

The author's lifetime section furnishes concise summaries following an extensive cleaning process, delineating the accepted and discarded years pertaining to each author.The accepted years signify the refined and validated data, while insights into the discarded years offer valuable context, shedding light on the challenges encountered and decisions made during the cleaning procedure.

## Complete Dataset Overview
The field has `r sum(is.na(df[[field]]))` / (`r round(100*mean(is.na(df[[field]])), 1)`%) missing values and  `r sum(!is.na(df[[field]]))` / (`r round(100*mean(!is.na(df_19[[field]])), 1)`%) with non-missing lifetime information.

[Author date accepted for the complete Fennica](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_date_accepted.csv)

[Author date discarded for the complete Fennica](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_date_discarded.csv)

## Subset Analysis: 1809-1917

[Author date accepted for 1809-1917](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_date_accepted_19.csv)

[Author date discarded for 1809-1917](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/author_date_discarded_19.csv)


```{r}
#| label = "summarytitle-author-date",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 8,
#| fig.height = 6

library(dplyr)
library(ggplot2)

# Step 1: Filter out rows without a known age

author_df$age <- df$author_age
author_df_clean <- author_df %>%
  filter(!is.na(age), publication_decade >= 1800)

# Step 2: For each author, get their first publication and corresponding age
first_pub <- author_df_clean %>%
  group_by(melinda_id) %>%
  arrange(publication_year, .by_group = TRUE) %>%
  summarise(
    first_pub_year = first(publication_year),
    first_pub_age  = first(age),
    .groups = "drop"
  )

# Step 3: Compute the average (and median) age of debut by year
avg_age_by_year <- first_pub %>%
  group_by(first_pub_year) %>%
  summarise(
    mean_age = mean(first_pub_age, na.rm = TRUE),
    median_age = median(first_pub_age, na.rm = TRUE),
    n_authors = n(),
    .groups = "drop"
  )

ggplot(avg_age_by_year, aes(x = first_pub_year, y = mean_age)) +
  geom_point(color = "steelblue", size = 1.5, alpha = 0.6) +
  geom_smooth(
    method = "loess",    # local polynomial smoothing
    se = FALSE,          # remove grey confidence band (set to TRUE if you want it)
    color = "darkred",
    linewidth = 1.2
  ) +
  labs(
    x = "Year of First Publication",
    y = "Average Age at First Publication",
    title = "Smoothed Trend in Average Age at First Publication (1800–Present)"
  ) +
  theme_minimal(base_size = 13)



```


## Gender

Gender information is not originally included in Fennica. We enriched the data by linking author names with gender information from various sources, including the HENKO project, the Genderize dataset, manual curation and search, and additional records provided by the National Library of Finland. The full list of names and genders can be found
[here](https://github.com/fennicahub/fennica/blob/master/inst/extdata/fennica_name_genders.csv).

```{r}
#| include: false
#| message: false
source("gender.R")
```

In total N = `r nrow(df)` records. After enrichmnet in total there are records `r sum(!is.na(df[[field]]))` / (`r round(100*mean(!is.na(df[[field]])), 1)`%) with assigned gender. There are `r sum(df[[field]] == "female", na.rm = TRUE)` (`r round(100*mean(df[[field]] == "female", na.rm = TRUE), 1)`%) female names, `r sum(df[[field]] == "male", na.rm = TRUE)` (`r round(100*mean(df[[field]] == "male", na.rm = TRUE), 1)`%) male names and `r sum(df[[field]] == "unisex", na.rm = TRUE)` (`r round(100*mean(df[[field]] == "unisex", na.rm = TRUE), 1)`%) unisex names. 

### Genres over Time (1600-1950)
```{r}
#| label = "summary_gender",
#| echo = FALSE,
#| warning = FALSE,
# Join publication_decade from df_pubtime to df by melinda_id
df$publication_decade <- df_pubtime$publication_decade[match(df$melinda_id, df_pubtime$melinda_id)]

# Filter your data to only include those genres
df_selected <- df%>%
  filter(!is.na(publication_decade), 
         !is.na(df$gender),
         publication_decade <= 1950)

# Summarize counts by decade and genre
df_summary <- df_selected %>%
  group_by(publication_decade, gender) %>%
  summarise(n = n(), .groups = "drop")

ggplot(df_summary, aes(x = publication_decade,y = n, fill = gender)) +
  geom_col(position = "stack", width = 8) +  # width makes bars a bit narrower
  labs(x = "Publication Decade", y = "Gender count", fill = "Gender") +
  scale_fill_brewer(palette = "Set2") +
  scale_x_continuous(limits = c(1600, 1950),breaks = seq(1600, 1950, by = 50)) +
  theme_minimal()

```

### Gender in 1809-1917
In total N = `r nrow(df_19)` records. After enrichmnet in total there are records `r sum(!is.na(df_19[[field]]))` / (`r round(100*mean(!is.na(df_19[[field]])), 1)`%) with assigned gender. There are `r sum(df_19[[field]] == "female", na.rm = TRUE)` (`r round(100*mean(df_19[[field]] == "female", na.rm = TRUE), 1)`%) female names, `r sum(df_19[[field]] == "male", na.rm = TRUE)` (`r round(100*mean(df_19[[field]] == "male", na.rm = TRUE), 1)`%) male names and `r sum(df_19[[field]] == "unisex", na.rm = TRUE)` (`r round(100*mean(df_19[[field]] == "unisex", na.rm = TRUE), 1)`%) unisex names. 

#### Genres over Time (1809-1917)
```{r}
#| label = "summary_gender_19",
#| echo = FALSE,
#| warning = FALSE,
# Join publication_decade from df_pubtime to df by melinda_id
df_19$publication_decade <- df_pubtime19$publication_decade[match(df_19$melinda_id, df_pubtime19$melinda_id)]

# Filter your data to only include those genres
df_selected <- df_19%>%
  filter(!is.na(publication_decade), 
         !is.na(df_19$gender))

# Summarize counts by decade and genre
df_summary <- df_selected %>%
  group_by(publication_decade, gender) %>%
  summarise(n = n(), .groups = "drop")

ggplot(df_summary, aes(x = publication_decade,y = n, fill = gender)) +
  geom_col(position = "stack", width = 8) +  # width makes bars a bit narrower
  labs(x = "Publication Decade", y = "Gender count", fill = "Gender") +
  scale_fill_brewer(palette = "Set2") +
  scale_x_continuous(limits = c(1800, 1920),breaks = seq(1800, 1920, by = 10)) +
  theme_minimal()

```

## Author's profession

```{r}
#| include: false
#| message: false
source("author_profession.R")
```

Auhtor profession in fennica is depicted in 700,e field. We enrich it with information from Kanto. 
In total N = `r nrow(df)` records. Before enrichment 700,e has `r sum(is.na(df[[field]]))` / (`r round(100*mean(is.na(df[[field]])), 1)`%) missing values. After enrichmnet in total there are records `r sum(!is.na(df[[field]]))` / (`r round(100*mean(!is.na(df_19[[field]])), 1)`%) with assigned profession. There are `r length(unique(na.omit(df[[field]])))` professions.

```{r}
#| label = "summaryproffesion",
#| echo = FALSE,
#| results = "asis"
x <- top(df, "author_profession")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("Profession", "Entries (n)", "Fraction (%)")
kable(head(tab, 15))
```