---
title: "Author's name"
hide-description: false
description: ""
---

```{r}
#| include = FALSE
source("init.R")
source("author_name.R")
```

Author's name section's summary tables offer insights into the dataset's integrity, illustrating the accepted and discarded author names. An examination of missing values in the original dataset provides transparency regarding data completeness. The inclusion of information on name variants and pseudonyms enriches the analysis, addressing nuances in authorship representation. This comprehensive approach ensures a thorough understanding of the dataset's composition and the intricacies associated with author identification.

## Complete Dataset Overview

-   [Unique accepted entries in original data](dataTable/data_table.html?path=../output.tables/author_name_accepted.csv): `r length(unique(df[[field]]))`
-   [Unique discarded entries in original data](dataTable/data_table.html?path=../output.tables/author_name_discarded.csv) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
-   Original documents with non-NA titles `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
-   Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)

### Authors

-   `r length(unique(df$author_name))` [unique authors](dataTable/data_table.html?path=../output.tables/author_accepted.csv) These final names capture all name variants from the custom [author synonyme table](dataTable/data_table.html?path=../output.tables/ambiguous-authors.csv), and exclude known pseudonymes (see below). If multiple names for the same author are still observed on this list, they should be added on the [author synonyme table](dataTable/data_table.html?path=../output.tables/ambiguous-authors.csv).
-   `r sum(!is.na(df$author_name))` documents have unambiguous author information (`r round(100*mean(!is.na(df$author_name)))`%).
-   `r length(readLines(paste0(getwd(),"/output.tables/pseudonyme_accepted.csv")))-2` [unique pseudonymes](dataTable/data_table.html?path=../output.tables/pseudonyme_accepted.csv) are recognized based on [custom pseudonyme lists](dataTable/data_table.html?path=../output.tables/custom_pseudonymes.csv).
-   `r length(readLines(paste0(getwd(),"/output.tables/author_discarded.csv")))-2` [discarded author names](dataTable/data_table.html?path=../output.tables/author_discarded.csv) This list should not include any real authors (if it does, please send a note to the admin). The stopword lists are considered when discarding names.
-   [Author name conversions](dataTable/data_table.html?path=../output.tables/author_conversion_nontrivial.csv) Non-trivial conversions from the original raw data to final names.

### Auxiliary files

-   [Author synonyme table](dataTable/data_table.html?path=../output.tables/ambiguous-authors.csv)
-   [Stopwords for names](dataTable/data_table.html?path=../output.tables/stopwords_for_names.csv)
-   [Stopwords for titles](dataTable/data_table.html?path=../output.tables/stopwords_titles.csv)
-   [Custom pseudonyme lists](dataTable/data_table.html?path=../output.tables/custom_pseudonymes.csv)

## Subset Analysis: 1809-1917

-   [Unique accepted entries for for 1809-1917 years](dataTable/data_table.html?path=../output.tables/author_name_accepted_19.csv): `r length(unique(df_19[[field]]))`

-   [Unique discarded entries in original data](dataTable/data_table.html?path=../output.tables/author_name_discraded_19.csv) (excluding NA cases): `r as.vector(countLines(file_discarded_19) - 1)`

Top-`r ntop` titles and their title counts for period 1809-1917.

The accompanying plot visually underscores the prominence of these authors, emphasizing the metric of the number of unique titles published by each author.

```{r}
#| label = "summarytitle-author-name",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 8,
#| fig.height = 6
library(ggplot2)
library(comhis)

theme_set(theme_bw(base_size = 12))
p <- top_plot(df_19, "author_name", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

Frequency of unique titles 1809-1917.

The plot adds a historical dimension to the analysis. By visualizing how the number of unique titles evolves over this time span, it provides insights into the literary landscape and publishing trends during the 19th and early 20th centuries.

```{r}
#| label = "uniquetitles-author-name",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 8,
#| fig.height = 6
tab <- table(df_19$author_name)
d <- data.frame(title = names(tab), n = as.numeric(tab))

library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- ggplot(d, aes(x = n)) +
  geom_histogram(color="black", fill="white") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```