---
title: "Genre/form 655"
hide-description: false
description: ""
---

```{r}
#| include = FALSE
source("init.R")
source("genre_655.R")
```

MARC: [655,a](https://www.loc.gov/marc/bibliographic/bd655.html)

## Description

## Description

Field 655 (Genre/Form) contains genre and form descriptors recorded as free text in the bibliographic metadata. These entries are heterogeneous: multiple values may occur within a single record (typically separated by delimiters such as `|`), and labels vary in spelling, formatting, and level of standardization.

To enable consistent analysis, the field was harmonized using a controlled vocabulary:

* **Controlled vocabulary matching**: extracted values were matched against a curated list derived from [**SLM – Suomalainen lajityyppi- ja muotosanasto**](https://finto.fi/slm/en/), a Finnish genre and form thesaurus maintained within the Finto ontology service. This provides a standardized set of genre terms in Finnish.

* **Filtering of unmatched values**: only values that could be directly matched to SLM labels were retained. All other entries were classified as *unrecognized* and excluded from the harmonized field. These discarded values are reported separately for transparency and quality assessment.

* **Reconstruction of harmonized field**: validated labels were recombined into a semicolon-separated string (`harmonized`) per record. As SLM is a Finnish-language vocabulary, all retained genre labels are treated as Finnish, and no additional language assignment was required.

* **Missing data handling**: records without valid matches were set to `NA`. The proportion of missing values reflects both absence of genre information and limitations in mapping to the controlled vocabulary.

This workflow produces a standardized and reproducible representation of genre/form information, enabling reliable aggregation and comparison across records while preserving information about discarded and ambiguous cases.


## Complete Dataset Overview

[Unique genre/form](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/genre_655_accepted.csv):  `r length(unique(unlist(strsplit(as.character(df$harmonized), ";"))))-1` 

There are `r sum(is.na(df$harmonized))` missing values in the dataset,accounting for (`r round(100*mean(is.na(df$harmonized)), 2)`%) of the total. 

[Unrecognized genre_655s](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/genre_655_discarded.csv) provides details of Genre/Form that were discarded, in total: `r sum(!is.na(tmp))`. 


```{r}
#| label = "genre655",
#| echo = FALSE,
#| results = "asis"
x <- top(df, "harmonized")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("Genre/Form", "Entries (n)", "Fraction (%)")
kable(head(tab, 10))
```

[Download genre_655 harmonized dataset](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/genre_655.csv)

## Subset Analysis: 1809-1917

[Unique genre_655s (1809-1917)](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/genre_655_accepted_19.csv): `r length(unique(unlist(strsplit(as.character(df_19$harmonized), ";"))))-1`

There are `r sum(is.na(df_19$harmonized))` missing values in the dataset,accounting for (`r round(100*mean(is.na(df_19$harmonized)), 2)`%) of the total. 

[Download genre_655 harmonized dataset (1809-1917)](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/genre_655_19.csv)

### Top Genre/Form for 1809-1917

[Accepted Genre/Form (1809-1917)](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/genre_655_accepted_19.csv).

```{r}
#| label = "genre655_19",
#| echo = FALSE,
#| results = "asis"
x <- top(df_19, "harmonized")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df_19)), 1))
colnames(tab) <- c("Genre/Form", "Entries (n)", "Fraction (%)")
kable(head(tab, 10))
```
