---
title: "Genre 008/33"
hide-description: false
description: ""
---

```{r}
#| include: FALSE
#| warning: FALSE
#| message: FALSE
source("init.R")
source("publication_time.R")
source("008_33.R")
```


MARC: [008](https://www.loc.gov/marc/bibliographic/bd008.html)

## Description
MARC21 field 008 contains fixed-length data elements that encode various bibliographic details. In this context, we focus specifically on books—that is, records where the Type of Record is language material. From this field, we extract and interpret the genre information as encoded in position 33 of the 008 field.

This analysis is based on `r sum(nrow(df))` book records in the Fennica database.

## Complete Dataset Overview

[Unique genre 008](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/genre_008_accepted.csv):  `r length(unique(unlist(strsplit(as.character(df$converted_008_33), ";"))))-1`.

There are `r sum(is.na(df$converted_008_33))` missing values in the dataset, accounting for (`r round(100*mean(is.na(df$converted_008_33)), 2)`%) of the total. Also, there `r sum(df$converted_008_33 == "Ei koodattu", na.rm = TRUE)` "Not coded" genres in the field 008/33, accounting for (`r round(100*mean(df$converted_008_33 == "Ei koodattu", na.rm = TRUE), 2)`%) of the total.

[Unrecognized genre 088](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/genre_008_discarded.csv) provides details of Genre 008 that were discarded, in total: `r sum(!is.na(tmp))`. 

### Top `r ntop` Genre Count in Fennica 
```{r}
#| label = "genre008_full",
#| echo = FALSE,
#| results = "asis"

# Remove "Ei koodattu" before tabulation
df_filtered <- df[df$converted_008_33 != "Ei koodattu", ]

x <- top(df_filtered, "converted_008_33")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("Genre for Books", "Entries (n)", "Fraction (%)")
ntop <- 15
kable(head(tab, ntop))
```

### Fiction VS Non-Fiction over Time (log10)
```{r}
#| label = "summary_008_genre_pic",
#| echo = FALSE,
#| warning = FALSE,
# Join publication_decade from df_pubtime to df by melinda_id
df$publication_decade <- df_pubtime$publication_decade[match(df$melinda_id, df_pubtime$melinda_id)]

# Define the genres you're interested in
selected_genres <- c("Tietokirjallisuus", "Kaunokirjallisuus", "Draama", "Runot", "Romaanit", "Novellit, kertomukset", "Puheet, esitelmät", "Kirjeet", "Esseet", "Huumori, satiiri")

fiction_genres <- c("Kaunokirjallisuus", "Draama", "Runot", "Romaanit",
  "Novellit, kertomukset", "Puheet, esitelmät", "Kirjeet", "Esseet", "Huumori, satiiri")

df_selected <- df %>%
  filter(
    converted_008_33 %in% c(fiction_genres, "Tietokirjallisuus"),
    !is.na(publication_decade),
    publication_decade >= 1500
  ) %>%
  mutate(
    genre_group = ifelse(
      converted_008_33 == "Tietokirjallisuus",
      "Non-Fiction",
      "Fiction"
    )
  )


# Plot
ggplot(df_selected, aes(x = publication_decade, fill = genre_group)) +
  geom_bar(position = "stack", width = 8) +
   scale_y_log10() +
  labs(x = "Publication Decade", y = "Number of Books (log10)", fill = "Genre Group") +
  scale_fill_manual(values = c("Fiction" = "darkgray", "Non-Fiction" = "lightgrey")) +  # Optional: custom colors
  scale_x_continuous(breaks = seq(1500, 2030, by = 100)) +
  theme_minimal()

```

## Subset Analysis: 1809-1917

[Unique genre 008](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/genre_008_accepted_19.csv):  `r length(unique(unlist(strsplit(as.character(df_19$converted_008_33), ";"))))-1`.

There are `r sum(is.na(df_19$converted_008_33))` missing values in the dataset, accounting for (`r round(100*mean(is.na(df_19$converted_008_33)), 2)`%) of the total. Also, there `r sum(df_19$converted_008_33 == "Ei koodattu", na.rm = TRUE)` "Not coded" genres in the field 008/33, accounting for (`r round(100*mean(df_19$converted_008_33 == "Ei koodattu", na.rm = TRUE), 2)`%) of the total.


### Top `r ntop` Genre Count in Fennica (1809-1917) 
```{r}
#| label = "genre008_19",
#| echo = FALSE,
#| results = "asis"

# Remove "Ei koodattu" before tabulation
df_filtered1 <- df_19[df_19$converted_008_33 != "Ei koodattu", ]

x <- top(df_filtered1, "converted_008_33")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("Genre for Books (1809-1917)", "Entries (n)", "Fraction (%)")
ntop <- 15
kable(head(tab, ntop))
```

### Certain Genres over Time
```{r}
#| label = "summary_008_genre_pic2",
#| echo = FALSE,
#| warning = FALSE,
# Join publication_decade from df_pubtime to df by melinda_id
df_19$publication_decade <- df_pubtime19$publication_decade[match(df_19$melinda_id, df_pubtime19$melinda_id)]

# Define the genres you're interested in
selected_genres <- c(
  "Kaunokirjallisuus"= "Fiction",
  "Draama" = "Drama",
  "Runot" = "Poetry",
  "Romaanit" = "Novels",
  "Novellit, kertomukset" = "Short stories",
  "Puheet, esitelmät" = "Speeches & lectures",
  "Kirjeet" = "Letters",
  "Esseet" = "Essays",
  "Huumori, satiiri" = "Humor & satire"
)

df_selected <- df_19 %>%
  filter(
    !is.na(publication_decade), 
    !is.na(converted_008_33),
    publication_decade <= 1920,
    converted_008_33 %in% names(selected_genres)
  ) %>%
  mutate(
    genre_en = selected_genres[converted_008_33]
  )

df_summary <- df_selected %>%
  group_by(publication_decade, genre_en) %>%
  summarise(n = n(), .groups = "drop")

grey_vals <- grDevices::grey.colors(
  n = length(unique(df_summary$genre_en)),
  start = 0.85,   # lightest, not white
  end = 0.15      # darkest
)

ggplot(df_summary, aes(x = publication_decade, y = n + 1, fill = genre_en)) +
  geom_col(position = "stack", width = 8, color = "grey70", linewidth = 0.2) +
  scale_y_log10() +
  scale_fill_manual(values = grey_vals) +
  labs(
    x = "Publication decade",
    y = "Number of books (log10)",
    fill = "Genre"
  ) +
  scale_x_continuous(
    limits = c(1790, 1930),
    breaks = seq(1800, 1910, by = 10)
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1),
    axis.title.x = element_text(margin = margin(t = 15))
  )

```

