--- 
title: "Harmonized Finnish National Bibliography"
author: "Turku Data Science Group"
date: "`r Sys.Date()`"
site: "bookdown::bookdown_site"
output:
  output: bookdown::gitbook
github-repo: fennicahub/fennica
url: https://github.com/fennicahub/fennica
  
documentclass: book
---

# Preface chapter

As part of the Metadata Harmonization And Analysis work package, we use the Finnish national bibliography (FNB) Fennica dataset to create a harmonized dataset that can be used for research purposes as well as provide the groundwork for infrastructure that can be iterated further. 

The FNB contains metadata for 71,919 documents and spans over 450 years, more specifically consisting of records printed between 1488 and 1955. There are 28 data fields in raw data in machine-readable cataloguing (MARC) format, which provide information on the document, for example, language, author name, author lifetime, publication title, publication place, publisher, and page count. Through harmonization and enriching the dataset with data from other sources, the abovementioned 28 fields can result in 96 data fields per document. (Tolonen, et al 2019.)

An important output of our work is a harmonized version of the FNB. The FNB metadata is an example of a dataset consisting of structured data. The FNB dataset is not created for research purposes and needs refining before it can be used. Tools are needed for accessing, cleaning, refining, enriching and analysing this type of data, and printing documentation of this process.

In this bookdown project we will disseminate the FNB dataset cleaning process.


```{r}
#| label = "source-index",
#| include = FALSE
source("init.R")
# knit_bookdown <- TRUE in init.R
```

This document was generated with the following packages:

```{r}
#| label = "system-information"
sessionInfo()
```
