---
title: "Language"
hide-description: false
description: ""
---

```{r}
#| include = FALSE
source("init.R")
source("language.R")
```

MARC: [041a](https://www.loc.gov/marc/bibliographic/bd041.html)

## Complete Dataset Overview

-   `r length(unique(unlist(strsplit(as.character(df$languages), ";"))))-1` [unique languages](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/languages_accepted.csv)
-   `r length(unique(df$language_primary))-1` [unique primary languages](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/language_primary_accepted.csv)\
-   `r sum(!df$multilingual, na.rm = TRUE)` single-language documents (`r round(100 * mean(!df$multilingual, na.omit = TRUE), 2)`%)
-   `r sum(df$multilingual, na.rm = TRUE)` multilingual documents (`r round(100 * mean(df$multilingual, na.omit = TRUE), 2)`%)
-   [Conversions from raw to preprocessed language entries](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/language_conversions.csv)
-   `r sum(is.na(df$languages) | df$language_primary == "Undetermined")` documents (`r round(100*mean(is.na(df$languages) | df$language_primary == "Undetermined"), 2)`%) with [unrecognized language](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/language_discarded.csv)

[Language discarded with melinda id](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/language_discarded_id.csv)

Language codes are from [MARC](https://www.loc.gov/marc/languages/language_code.html); new custom abbreviations can be added in [this table](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/language_abbreviations.csv).

## Subset Analysis: 1809-1917

-   `r length(unique(unlist(strsplit(as.character(df_19$languages), ";"))))-1` [unique languages](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/languages_accepted_19.csv)
-   `r sum(!df_19$multilingual, na.rm = TRUE)` single-language documents (`r round(100 * mean(!df_19$multilingual, na.omit = TRUE), 2)`%)
-   `r sum(df_19$multilingual, na.rm = TRUE)` multilingual documents (`r round(100 * mean(df_19$multilingual, na.omit = TRUE), 2)`%)
-   `r sum(is.na(df_19$languages) | df_19$language_primary == "Undetermined")` documents (`r round(100*mean(is.na(df_19$languages) | df_19$language_primary == "Undetermined"), 2)`%) with [unrecognized language](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/language_discarded_19.csv)

### Top languages for 1809-1917

Number of titles assigned with each language (top-10). For a complete list, see [accepted languages](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/language_accepted_19.csv).

```{r}
#| label = "summarylang2",
#| echo = FALSE,
#| results = "asis"
x <- top(df_19, "languages")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("Language", "Documents (n)", "Fraction (%)")
kable(head(tab, 10))
```

Title count per language (including multi-language documents; note the log10 scale):

```{r}
#| label = "summarylang",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 7,
#| fig.height = 5
top_plot(df_19, "languages", ntop = ntop, log10 = TRUE) + labs(y = "Entries (n)")
```

## Scripts 

Polish language field: [language.R](https://github.com/fennicahub/fennica/blob/master/inst/examples/language.R)

Harmonize language data function: [polish_languages.R](https://github.com/fennicahub/fennica/blob/master/R/polish_languages.R)

Render publication time field: [language.qmd](https://github.com/fennicahub/fennica/blob/master/inst/examples/language.qmd)
