---
title: "Bayes Multinomial Logistic Regression"
format: pdf
editor: visual
---

```{r}
#| echo: true
#| warning: false
```

# Introduction


This Quarto notebook documents a step-by-step workflow for assessing whether **genre** from a fiction group is associated with selected bibliographic metadata variables before fitting a full multivariable model. The response variable is **genre**, and the predictors are **gender** and **language**. All variables are categorical.

The workflow is intentionally staged. First, simple descriptive summaries and association tests are used to evaluate whether relationships are present at all. Next, models are introduced only after basic structure has been established. The final stage estimates genre probabilities under a Bayesian framework, enabling probabilistic interpretation and uncertainty quantification.

Criteria: books published in 1809-1917.
Genre (outcome)	Nominal categorical (K>2)
Gender	Categorical(Male or Female or Unknown)
Language	Categorical (Finnish or Swedish or Unknown)

Multinomial logistic regression for each genre (Esseet, Huumori/satiiri, Kaunokirjallisuus, Kirjeet, Novellit/kertomukset, Puheet/esitelmät, Romaanit, Runot, Yhdistelmä)


```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(brms)
library(rstan)
library(Rcpp)
library(nnet)
library(forcats)
library(bayesplot)
```


# Load and prepare the data
```{r}
url <- "https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/harmonized/books_19th.tsv"

df <- read.table(
file = url,
sep = "\t",
header = TRUE,
colClasses = "character",
fileEncoding = "UTF-8",
quote = "\"",
comment.char = "",
stringsAsFactors = FALSE
)

df$genre <- gsub("Puheet, esitelmät", "Puheetesitelmat",df$genre)
df$genre <- gsub("Novellit, kertomukset", "Novellitkertomukset",df$genre)
df$genre <- gsub("Yhdistelmä", "Yhdistelma",df$genre)

df <- df %>%
mutate(
gender_primary = factor(gender_primary, levels = c("male", "female")),
language = factor(language_primary, levels = c("Finnish", "Swedish")),
publisher_size = factor(publisher_size, levels = c("group_1", "group_2", "group_3")),
)

nrow(df)
```


```{r}
df_fiction <- df %>%
  filter(genre != "Tietokirjallisuus") %>%
  droplevels()

df_fiction$publication_place <- fct_lump_n(
  factor(df_fiction$publication_place),
  n = 10,
  other_level = "Other"
)

df_fiction$publication_place  <- fct_na_value_to_level(df_fiction$publication_place,  level = "Unknown")
df_fiction$publication_decade <- fct_na_value_to_level(df_fiction$publication_decade, level = "Unknown")
df_fiction$gender_primary     <- fct_na_value_to_level(factor(df_fiction$gender_primary), level = "Unknown")
df_fiction$language           <- fct_na_value_to_level(factor(df_fiction$language),   level = "Unknown")
df_fiction$publisher_size     <- fct_na_value_to_level(factor(df_fiction$publisher_size), level = "Unknown")
df_fiction$genre              <- fct_na_value_to_level(factor(df_fiction$genre),      level = "Unknown")

nrow(df_fiction)
```


```{r}
library(tidyr)
library(ggplot2)
library(scales)
library(forcats)
library(patchwork)

# ----------------------------
# 1) FREQUENTIST: same layout as Bayes
#    (Observed proportions + 95% CI) within (gender x language)
# ----------------------------

df_f <- df_fiction %>%
  mutate(
    gender = factor(gender_primary, levels = c("male","female")),
    language = factor(language_primary, levels = c("Finnish","Swedish")),
    genre = factor(genre)
  ) %>%
  filter(!is.na(genre), !is.na(gender), !is.na(language)) %>%
  droplevels()

# order genres once, use same ordering for both plots
genre_order <- df_f %>% count(genre, name = "N") %>% arrange(desc(N)) %>% pull(genre)
df_f <- df_f %>% mutate(genre = factor(genre, levels = genre_order))

freq_df <- df_f %>%
  count(language, gender, genre, name = "k") %>%
  group_by(language, gender) %>%
  mutate(
    n = sum(k),
    p = k / n,
    se = sqrt(p * (1 - p) / n),
    lo = pmax(0, p - 1.96 * se),
    hi = pmin(1, p + 1.96 * se),
    method = "Frequentist"
  ) %>%
  ungroup() %>%
  transmute(method, language, gender, genre, probability = p, lo, hi)

plot_prob_ci <- function(dat, title) {
  ggplot(dat, aes(x = genre, y = probability, color = gender, group = gender)) +
    geom_point(position = position_dodge(width = 0.6), size = 2) +
    geom_errorbar(
      aes(ymin = lo, ymax = hi),
      position = position_dodge(width = 0.6),
      width = 0.2
    ) +
    facet_wrap(~ language) +
    scale_y_continuous(labels = percent_format(), limits = c(0, 1)) +
    labs(
      title = title,
      x = "Genre",
      y = "Probability",
      color = "Gender"
    ) +
    theme_minimal(base_size = 13) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

p_freq  <- plot_prob_ci(freq_df,  "Frequentist: osuudet + 95% luottamusvälit")

```


```{r}
gp <- get_prior(
    genre ~ gender_primary + language,
     family = categorical(),
     data = df_fiction
 )
gp
```


```{r}
priors <- c(
  prior(normal(0, 1), class = "b", dpar = "muEsseet"),
  prior(normal(0, 1), class = "b", dpar = "muHuumorisatiiri"),
  prior(normal(0, 1), class = "b", dpar = "muKaunokirjallisuus"),
  prior(normal(0, 1), class = "b", dpar = "muKirjeet"),
  prior(normal(0, 1), class = "b", dpar = "muNovellitkertomukset"),
  prior(normal(0, 1), class = "b", dpar = "muPuheetesitelmat"),
  prior(normal(0, 1), class = "b", dpar = "muRomaanit"),
  prior(normal(0, 1), class = "b", dpar = "muRunot"),
  prior(normal(0, 1), class = "b", dpar = "muYhdistelma"))
```


```{r}
fit.bayes <- brms::brm(
  genre ~ gender_primary + language,
  family = categorical(),
  data = df_fiction,
  prior = priors,
  chains = 4,
  cores = 2,
  iter = 2000,
  control = list(adapt_delta = 0.95)
)
```

```{r}
summary(fit.bayes)
     
pp_check(fit.bayes)         

```

```{r}
nuts <- nuts_params(fit.bayes)
summary(nuts$Value[nuts$Parameter == "accept_stat__"])
```

```{r}
newdata <- expand.grid(
  gender_primary = levels(df_fiction$gender_primary),
  language       = levels(df_fiction$language)
)

fit_prob <- fitted(
  fit.bayes,
  newdata = newdata,
  scale = "response",   # probabilities
  summary = TRUE,
  probs = c(0.005, 0.5, 0.995)
)


rownames(fit_prob) <- apply(newdata, 1, paste, collapse = " | ")
fit_prob
```

```{r}
# convert fitted() output to tidy df
plot_df <- as.data.frame(as.table(fit_prob[, "Estimate", ]))
colnames(plot_df) <- c("group", "genre", "probability")

# split group into gender + language
plot_df <- plot_df %>%
  separate(group, into = c("gender", "language"), sep = " \\| ")

s <- ggplot(plot_df %>% 
         filter(gender != "Unknown", language != "Unknown"),
       aes(x = genre, y = probability, fill = gender)) +
  geom_col(position = "dodge") +
  facet_wrap(~ language) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    x = "Genre",
    y = "Predicted probability",
    fill = "Gender",
    title = "Predicted genre probabilities by gender and language"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


plot_df2 <- plot_df %>%
  mutate(genre = str_replace(genre, "^P\\(Y = (.*)\\)$", "\\1"))

d <- plot_df2 %>%
  filter(
    genre %in% c("Romaanit", "Runot"),
    gender != "Unknown",
    language != "Unknown"
  ) %>%
  ggplot(aes(x = genre, y = probability, fill = gender)) +
  geom_col(position = "dodge") +
  facet_wrap(~ language) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    x = NULL, y = "Predicted probability", fill = "Gender",
    title = "Contrasting genre specialization: novels vs poetry"
  ) +
  theme_minimal()

s
d

```

### Analysis

Several genres (*Esseet*, *Huumori/satiiri*, *Kirjeet*) are extremely rare in the corpus, with predicted probabilities well below 1% across all gender–language groups. Due to these very small base rates and relatively wide credible intervals, no substantive conclusions can be drawn for these genres.

Clear and systematic differences emerge for the major genres. Women exhibit higher predicted probabilities of writing both **novels (*Romaanit*)** and **short prose (*Novellit, kertomukset*)** than men in both language groups. Among Finnish-language publications, the posterior mean probability of novels is approximately **13 percentage points higher** for women than for men, while among Swedish-language publications the corresponding difference is about **11 percentage points**. Similar for short prose. 

In contrast, **poetry (*Runot*)** is more strongly associated with male authors in both languages, with consistently higher predicted probabilities for men than for women. This pattern is particularly pronounced in Swedish-language publications. Thus, poetry is associated with male authors and Swedish-language publications (both true).

**Drama (*Draama*)** also appears to be more strongly associated with male authors, especially in Finnish-language publications. However, this result should be interpreted with caution, as the drama category contains a relatively large proportion of records with missing or uncertain metadata, which may influence the estimated probabilities.

Overall, the results indicate a clear gendered pattern in genre specialization, with women concentrating more heavily in long and short prose forms, while men are relatively more represented in poetry and drama. Language effects are substantial and often comparable in magnitude to gender effects, highlighting the importance of considering both dimensions jointly.





```{r}
# side-by-side (best for slides)
p_freq + p_bayes + plot_layout(guides = "collect")
```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)

# --- BAYES: make a df with Estimate + credible interval ---
plot_df <- as.data.frame(as.table(fit_prob[, c("Estimate", "Q0.5", "Q99.5"), ]))
colnames(plot_df) <- c("group", "stat", "genre", "value")

plot_df <- plot_df %>%
  pivot_wider(names_from = stat, values_from = value) %>%
  transmute(
    group,
    genre = genre,
    probability = as.numeric(Estimate),
    lo = as.numeric(Q0.5),
    hi = as.numeric(Q99.5)
  ) %>%
  separate(group, into = c("gender", "language"), sep = " \\| ") %>%
  filter(gender != "Unknown", language != "Unknown") %>%
  mutate(
    gender = factor(gender, levels = c("male", "female")),
    language = factor(language, levels = c("Finnish", "Swedish")),
    # clean labels: "P(Y = Draama)" -> "Draama"
    genre = gsub("^P\\(Y = ", "", genre),
    genre = gsub("\\)$", "", genre),
    genre = factor(genre)
  )

# --- (optional) order genres by average probability (nice for slides) ---
genre_order <- plot_df %>%
  group_by(genre) %>%
  summarise(m = mean(probability), .groups = "drop") %>%
  arrange(desc(m)) %>%
  pull(genre)

plot_df <- plot_df %>%
  mutate(genre = factor(genre, levels = genre_order))

# --- BAYES plot (same visual style as your frequentist plot should use) ---
p_bayes <- ggplot(plot_df, aes(x = genre, y = probability, fill = gender)) +
  geom_col(position = position_dodge(width = 0.9), width = 0.8) +
  geom_errorbar(
    aes(ymin = lo, ymax = hi),
    position = position_dodge(width = 0.9),
    width = 0.2
  ) +
  facet_wrap(~ language) +
  scale_y_continuous(
  limits = c(0, 0.65),
  labels = scales::percent_format(),
  breaks = seq(0, 0.75, by = 0.15)
) +
  labs(
    x = "Genre",
    y = "Predicted probability",
    fill = "Gender",
    title = "Bayes: ennustetut genre-todennäköisyydet (Q0.5–Q99.5)"
  ) +
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p_bayes
```

```{r}
df_f <- df_fiction %>%
  mutate(
    gender = factor(gender_primary, levels = c("male","female")),
    language = factor(language_primary, levels = c("Finnish","Swedish")),
    genre = factor(genre, levels = levels(plot_df$genre))
  ) %>%
  filter(!is.na(gender), !is.na(language), !is.na(genre)) %>%
  droplevels()

freq_df <- df_f %>%
  count(language, gender, genre, name = "k") %>%
  group_by(language, gender) %>%
  mutate(
    n = sum(k),
    probability = k / n,
    se = sqrt(probability * (1 - probability) / n),
    lo = pmax(0, probability - 2.576 * se),
    hi = pmin(1, probability + 2.576 * se)
  ) %>%
  ungroup()

p_freq <- ggplot(freq_df, aes(x = genre, y = probability, fill = gender)) +
  geom_col(position = position_dodge(width = 0.9), width = 0.8) +
  geom_errorbar(
    aes(ymin = lo, ymax = hi),
    position = position_dodge(width = 0.9),
    width = 0.2
  ) +
  facet_wrap(~ language) +
  scale_y_continuous(
  limits = c(0, 0.65),
  labels = scales::percent_format(),
  breaks = seq(0, 0.75, by = 0.15)
) +
  labs(
    x = "Genre",
    y = "Observed proportion",
    fill = "Gender",
    title = "Frequentist: havaitut osuudet (99% luottamusvälit)"
  ) +
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p_freq

```


```{r}
p_freq + p_bayes + plot_layout(guides = "collect")
```

