---
title: "Physical dimensions"
hide-description: false
description: ""
---

```{r}
#| include = FALSE
source("init.R")
source("physical_dimensions.R")
```

MARC: [300c](https://www.loc.gov/marc/bibliographic/bd300.html)

Polish physical dimensions field: [physical_dimensions.R](https://github.com/fennicahub/fennica/blob/master/inst/examples/physical_dimensions.R)

Harmonize physical attributes data function: [polish_dimensions.R](https://github.com/fennicahub/fennica/blob/master/R/polish_dimensions.R)

Render physical dimensions field: [physical_dimensions.qmd](https://github.com/fennicahub/fennica/blob/master/inst/examples/physical_dimensions.qmd)



## Complete Dataset Overview

-   [Accepted dimension info](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/physical_dimensions_accepted.csv)

-   [Discarded dimension info](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables//physical_dimensions_discarded.csv)


```{r}
#| include = FALSE

library(dplyr)

field <- "physical_dimensions"

is_nonempty <- function(x) {
  !is.na(x) & trimws(as.character(x)) != "" & trimws(as.character(x)) != "NA"
}

pct <- function(n, d) {
  round(100 * n / d, 1)
}

dimension_summary <- function(df) {

  n_total <- nrow(df)

  original_nonempty <- is_nonempty(df$original)

  any_harmonized <-
    is_nonempty(df$gatherings) |
    is_nonempty(df$width) |
    is_nonempty(df$height) 

  complete_dimensions <-
    is_nonempty(df$width) &
    is_nonempty(df$height)

  partial_dimensions <- xor(
    is_nonempty(df$width),
    is_nonempty(df$height)
  )

  n_original <- sum(original_nonempty)

  n_any_harmonized <- sum(any_harmonized)

  n_interpreted_from_nonempty <- sum(
    original_nonempty & any_harmonized
  )

  n_uninterpreted_from_nonempty <- sum(
    original_nonempty & !any_harmonized
  )

  n_area <- sum(is_nonempty(df$area))

  n_complete_dimensions <- sum(complete_dimensions)
  n_partial_dimensions <- sum(partial_dimensions)

  n_gatherings_original <- sum(is_nonempty(df$gatherings.original))
  n_gatherings_final <- sum(is_nonempty(df$gatherings))

  n_height_original <- sum(is_nonempty(df$height.original))
  n_height_final <- sum(is_nonempty(df$height))

  n_width_original <- sum(is_nonempty(df$width.original))
  n_width_final <- sum(is_nonempty(df$width))

  list(
    n_total = n_total,

    n_original = n_original,
    p_original = pct(n_original, n_total),

    n_any_harmonized = n_any_harmonized,
    p_any_harmonized = pct(n_any_harmonized, n_total),

    n_interpreted_from_nonempty = n_interpreted_from_nonempty,
    p_interpreted_from_nonempty = pct(
      n_interpreted_from_nonempty,
      n_original
    ),

    n_uninterpreted_from_nonempty = n_uninterpreted_from_nonempty,

    n_complete_dimensions = n_complete_dimensions,
    p_complete_dimensions = pct(n_complete_dimensions, n_total),

    n_partial_dimensions = n_partial_dimensions,
    p_partial_dimensions = pct(n_partial_dimensions, n_total),

    n_area = n_area,
    p_area = pct(n_area, n_total),
    n_area_missing = n_total - n_area,

    n_gatherings_original = n_gatherings_original,
    p_gatherings_original = pct(n_gatherings_original, n_total),
    n_gatherings_final = n_gatherings_final,
    p_gatherings_final = pct(n_gatherings_final, n_total),
    n_gatherings_gain = n_gatherings_final - n_gatherings_original,

    n_height_original = n_height_original,
    p_height_original = pct(n_height_original, n_total),
    n_height_final = n_height_final,
    p_height_final = pct(n_height_final, n_total),
    n_height_gain = n_height_final - n_height_original,

    n_width_original = n_width_original,
    p_width_original = pct(n_width_original, n_total),
    n_width_final = n_width_final,
    p_width_final = pct(n_width_final, n_total),
    n_width_gain = n_width_final - n_width_original

  )
}

ds <- dimension_summary(df.tmp)
```


The original physical-dimensions field is available for `r ds$n_original` records (`r ds$p_original`%) and missing for `r ds$n_total - ds$n_original` records. It contains `r dplyr::n_distinct(df.tmp$original[is_nonempty(df.tmp$original)])` unique non-missing values.

Gatherings information is available in the extracted original data for `r ds$n_gatherings_original` records (`r ds$p_gatherings_original`%) and in the harmonized data for `r ds$n_gatherings_final` records (`r ds$p_gatherings_final`%). Harmonization therefore added gatherings information for `r ds$n_gatherings_gain` records. The original and harmonized variables contain `r dplyr::n_distinct(df.tmp$gatherings.original[is_nonempty(df.tmp$gatherings.original)])` and `r dplyr::n_distinct(df.tmp$gatherings[is_nonempty(df.tmp$gatherings)])` unique non-missing values, respectively.

Height information is available in the extracted original data for `r ds$n_height_original` records (`r ds$p_height_original`%) and in the harmonized data for `r ds$n_height_final` records (`r ds$p_height_final`%). Harmonization therefore added height information for `r ds$n_height_gain` records. The original and harmonized variables contain `r dplyr::n_distinct(df.tmp$height.original[is_nonempty(df.tmp$height.original)])` and `r dplyr::n_distinct(df.tmp$height[is_nonempty(df.tmp$height)])` unique non-missing values, respectively.

Width information is available in the extracted original data for `r ds$n_width_original` records (`r ds$p_width_original`%) and in the harmonized data for `r ds$n_width_final` records (`r ds$p_width_final`%). Harmonization therefore added width information for `r ds$n_width_gain` records. The original and harmonized variables contain `r dplyr::n_distinct(df.tmp$width.original[is_nonempty(df.tmp$width.original)])` and `r dplyr::n_distinct(df.tmp$width[is_nonempty(df.tmp$width)])` unique non-missing values, respectively.


## Harmonization outcomes

Both height and width are available for `r ds$n_complete_dimensions` records (`r ds$p_complete_dimensions`%), allowing document area to be calculated. Only one of these two measurements is available for `r ds$n_partial_dimensions` records (`r ds$p_partial_dimensions`%).

Document area was calculated for `r ds$n_area` records (`r ds$p_area`%). Area remains unavailable for `r ds$n_area_missing` records because height, width, or both could not be reliably interpreted. These cases are listed in the [entries where document surface could not be estimated](https://github.com/fennicahub/fennica/blob/master/inst/extdata/physical_dimension_incomplete.csv). The harmonized area variable contains `r dplyr::n_distinct(df.tmp$area[is_nonempty(df.tmp$area)])` unique non-missing values.


- The complete original physical-dimensions field contains `r sum(is.na(df.tmp$original) | trimws(as.character(df.tmp$original)) %in% c("", "NA"))` missing values and `r length(unique(df.tmp$original[!is.na(df.tmp$original) & !trimws(as.character(df.tmp$original)) %in% c("", "NA")]))` unique non-missing values.

- Original gatherings contain `r sum(is.na(df.tmp$gatherings.original) | trimws(as.character(df.tmp$gatherings.original)) %in% c("", "NA"))` missing values and `r length(unique(df.tmp$gatherings.original[!is.na(df.tmp$gatherings.original) & !trimws(as.character(df.tmp$gatherings.original)) %in% c("", "NA")]))` unique non-missing values. Harmonized gatherings contain `r sum(is.na(df.tmp$gatherings) | trimws(as.character(df.tmp$gatherings)) %in% c("", "NA"))` missing values and `r length(unique(df.tmp$gatherings[!is.na(df.tmp$gatherings) & !trimws(as.character(df.tmp$gatherings)) %in% c("", "NA")]))` unique non-missing values.

- Original width values contain `r sum(is.na(df.tmp$width.original) | trimws(as.character(df.tmp$width.original)) %in% c("", "NA"))` missing values and `r length(unique(df.tmp$width.original[!is.na(df.tmp$width.original) & !trimws(as.character(df.tmp$width.original)) %in% c("", "NA")]))` unique non-missing values. Harmonized width values contain `r sum(is.na(df.tmp$width) | trimws(as.character(df.tmp$width)) %in% c("", "NA"))` missing values and `r length(unique(df.tmp$width[!is.na(df.tmp$width) & !trimws(as.character(df.tmp$width)) %in% c("", "NA")]))` unique non-missing values.

- Original height values contain `r sum(is.na(df.tmp$height.original) | trimws(as.character(df.tmp$height.original)) %in% c("", "NA"))` missing values and `r length(unique(df.tmp$height.original[!is.na(df.tmp$height.original) & !trimws(as.character(df.tmp$height.original)) %in% c("", "NA")]))` unique non-missing values. Harmonized height values contain `r sum(is.na(df.tmp$height) | trimws(as.character(df.tmp$height)) %in% c("", "NA"))` missing values and `r length(unique(df.tmp$height[!is.na(df.tmp$height) & !trimws(as.character(df.tmp$height)) %in% c("", "NA")]))` unique non-missing values.

- The harmonized oblong-format indicator classifies `r sum(df.tmp$obl %in% TRUE, na.rm = TRUE)` documents (`r round(100 * mean(df.tmp$obl %in% TRUE, na.rm = TRUE), 1)`%) as oblong and `r sum(df.tmp$obl %in% FALSE, na.rm = TRUE)` documents (`r round(100 * mean(df.tmp$obl %in% FALSE, na.rm = TRUE), 1)`%) as not oblong.

- Harmonized document area contains `r sum(is.na(df.tmp$area) | trimws(as.character(df.tmp$area)) %in% c("", "NA"))` missing values and `r length(unique(df.tmp$area[!is.na(df.tmp$area) & !trimws(as.character(df.tmp$area)) %in% c("", "NA")]))` unique non-missing values.
## Document dimensions comparisons

- Some dimension info is provided in the original raw data for altogether `r ds$n_original` documents (`r ds$p_original`%) but could not be interpreted for `r ds$n_uninterpreted_from_nonempty` documents, i.e. dimension info was successfully estimated for `r ds$p_interpreted_from_nonempty`% of the documents where this field was not empty.

- Document dimensions (area) info was obtained in the final preprocessed data for altogether `r ds$n_area` documents (`r ds$p_area`%). For the remaining `r ds$n_area_missing` documents, critical dimension information was not available or could not be interpreted: [List of entries where document surface could not be estimated](https://github.com/fennicahub/fennica/blob/master/inst/extdata/physical_dimension_incomplete.csv)

- Document gatherings info is originally available for `r ds$n_gatherings_original` documents (`r ds$p_gatherings_original`%), and further estimated up to `r ds$n_gatherings_final` documents (`r ds$p_gatherings_final`%) in the final preprocessed data.

- Document height info is originally available for `r ds$n_height_original` documents (`r ds$p_height_original`%), and further estimated up to `r ds$n_height_final` documents (`r ds$p_height_final`%) in the final preprocessed data.

- Document width info is originally available for `r ds$n_width_original` documents (`r ds$p_width_original`%), and further estimated up to `r ds$n_width_final` documents (`r ds$p_width_final`%) in the final preprocessed data.


```{r}
#| label = "dimensions",
#| echo = FALSE,
#| warning = FALSE,
#| plot-gatherings, 
#| fig.width=20, 
#| fig.height=6

library(dplyr)
library(tidyr)
library(ggplot2)
library(forcats)
library(scales)

plot_gatherings <- function(df, top_n = 10) {
  
  plot_df <- df %>%
    transmute(
      original = gatherings.original,
      final = gatherings
    ) %>%
    pivot_longer(
      cols = everything(),
      names_to = "type",
      values_to = "gatherings"
    ) %>%
    mutate(
      gatherings = trimws(as.character(gatherings)),
      gatherings = na_if(gatherings, ""),
      gatherings = na_if(gatherings, "NA")
    ) %>%
    filter(!is.na(gatherings))
  
  # keep only most common gatherings
  top_levels <- plot_df %>%
    filter(type == "final") %>%
    count(gatherings, sort = TRUE) %>%
    slice_head(n = top_n) %>%
    pull(gatherings)
  
  plot_df <- plot_df %>%
    mutate(
      gatherings = ifelse(
        gatherings %in% top_levels,
        gatherings,
        "Other"
      )
    ) %>%
    count(type, gatherings) %>%
    group_by(type) %>%
    mutate(
      prop = n / sum(n),
      gatherings = fct_reorder(gatherings, prop)
    )
  
  ggplot(plot_df,
         aes(x = prop,
             y = gatherings)) +
    
    geom_col(width = 0.7) +
    
    facet_wrap(~type, ncol = 2) +
    
    scale_x_continuous(
      labels = percent_format(accuracy = 1)
    ) +
    
    labs(
      x = "Share of documents",
      y = NULL,
      title = "",
      subtitle = "Original and harmonized distributions among non-missing values"
    ) +
    
    theme_minimal(base_size = 13) +
    
    theme(
      legend.position = "none",
      panel.grid.minor = element_blank(),
      strip.text = element_text(face = "bold"),
      plot.title = element_text(face = "bold")
    )
}



plot_gatherings(df.tmp)

```

