---
title: "Physical dimensions"
hide-description: false
description: ""
---

```{r}
#| include = FALSE
source("init.R")
source("physical_dimensions.R")
```

MARC: [300c](https://www.loc.gov/marc/bibliographic/bd300.html)

Polish physical dimensions field: [physical_dimensions.R](https://github.com/fennicahub/fennica/blob/master/inst/examples/physical dimensions.R)

Harmonize physical attributes data function: [polish_dimensions.R](https://github.com/fennicahub/fennica/blob/master/R/polish_dimensions.R)

Render physical dimensions field: [physical_dimensions.qmd](https://github.com/fennicahub/fennica/blob/master/inst/examples/physical dimensions.qmd)

## Complete Dataset Overview

-   [Accepted dimension info](dataTable/data_table.html?path=../output.tables/physical_size_accepted.csv)

-   [Discarded dimension info](dataTable/data_table.html?path=../output.tables/physical_size_discarded.csv)


```{r}
#| include = FALSE

library(dplyr)

field <- "physical_size"

is_nonempty <- function(x) {
  !is.na(x) & trimws(as.character(x)) != "" & trimws(as.character(x)) != "NA"
}

pct <- function(n, d) {
  round(100 * n / d, 1)
}

dimension_summary <- function(df) {

  n_total <- nrow(df)

  original_nonempty <- is_nonempty(df[[field]])

  n_original <- sum(original_nonempty)

  n_area <- sum(!is.na(df$area))
  n_gatherings_original <- sum(is_nonempty(df$gatherings.original))
  n_gatherings_final <- sum(is_nonempty(df$gatherings))

  n_height_original <- sum(!is.na(df$height.original))
  n_height_final <- sum(!is.na(df$height))

  n_width_original <- sum(!is.na(df$width.original))
  n_width_final <- sum(!is.na(df$width))

  n_interpreted_from_nonempty <- sum(original_nonempty & !is.na(df$area))
  n_uninterpreted_from_nonempty <- n_original - n_interpreted_from_nonempty

  list(
    n_total = n_total,

    n_original = n_original,
    p_original = pct(n_original, n_total),

    n_uninterpreted_from_nonempty = n_uninterpreted_from_nonempty,

    n_interpreted_from_nonempty = n_interpreted_from_nonempty,
    p_interpreted_from_nonempty = pct(n_interpreted_from_nonempty, n_original),

    n_area = n_area,
    p_area = pct(n_area, n_total),

    n_area_missing = n_total - n_area,

    n_gatherings_original = n_gatherings_original,
    p_gatherings_original = pct(n_gatherings_original, n_total),
    n_gatherings_final = n_gatherings_final,
    p_gatherings_final = pct(n_gatherings_final, n_total),

    n_height_original = n_height_original,
    p_height_original = pct(n_height_original, n_total),
    n_height_final = n_height_final,
    p_height_final = pct(n_height_final, n_total),

    n_width_original = n_width_original,
    p_width_original = pct(n_width_original, n_total),
    n_width_final = n_width_final,
    p_width_final = pct(n_width_final, n_total)
  )
}

ds <- dimension_summary(df.tmp)
```


## Document size comparisons

- Some dimension info is provided in the original raw data for altogether `r ds$n_original` documents (`r ds$p_original`%) but could not be interpreted for `r ds$n_uninterpreted_from_nonempty` documents, i.e. dimension info was successfully estimated for `r ds$p_interpreted_from_nonempty`% of the documents where this field was not empty.

- Document size (area) info was obtained in the final preprocessed data for altogether `r ds$n_area` documents (`r ds$p_area`%). For the remaining `r ds$n_area_missing` documents, critical dimension information was not available or could not be interpreted: [List of entries where document surface could not be estimated](https://github.com/fennicahub/fennica/inst/extdata/physical_dimension_incomplete.csv)

- Document gatherings info is originally available for `r ds$n_gatherings_original` documents (`r ds$p_gatherings_original`%), and further estimated up to `r ds$n_gatherings_final` documents (`r ds$p_gatherings_final`%) in the final preprocessed data.

- Document height info is originally available for `r ds$n_height_original` documents (`r ds$p_height_original`%), and further estimated up to `r ds$n_height_final` documents (`r ds$p_height_final`%) in the final preprocessed data.

- Document width info is originally available for `r ds$n_width_original` documents (`r ds$p_width_original`%), and further estimated up to `r ds$n_width_final` documents (`r ds$p_width_final`%) in the final preprocessed data.


These tables can be used to verify the accuracy of the conversions from the raw data to final estimates:

-   [Dimension conversions from raw data to final estimates](https://github.com/fennicahub/fennica/inst/extdata/conversions_physical_dimension.csv)

-   [Automated tests for dimension conversions](https://github.com/fennicahub/fennica/inst/extdata/tests_dimension_polish.csv)

The estimated dimensions are based on the following auxiliary information sheets:

-   [Document dimension abbreviations](https://github.com/fennicahub/fennica/inst/extdata/document_size_abbreviations.csv)

-   [Standard sheet size estimates](https://github.com/fennicahub/fennica/inst/extdata/sheetsizes.csv)

-   [Document dimension estimates](https://github.com/fennicahub/fennica/inst/extdata/documentdimensions.csv) (used when information is partially missing)

```{r}
#| label = "dimensions",
#| echo = FALSE,
#| warning = FALSE,
#| plot-gatherings, 
#| fig.width=20, 
#| fig.height=6

plot_gatherings(df.tmp)

```

