---
title: "Physical dimensions"
hide-description: false
description: ""
---

```{r}
#| include = FALSE
source("init.R")
```

```{r}
#| include = FALSE
source("physical_dimensions.R")
```

MARC: [300c](https://www.loc.gov/marc/bibliographic/bd300.html)

## Complete Dataset Overview

-   [Accepted dimension info](dataTable/data_table.html?path=../output.tables/physical_dimensions_accepted.csv)

-   [Discarded dimension info](dataTable/data_table.html?path=../output.tables/physical_dimensions_discarded.csv)

-   Some dimension info is provided in the original raw data for altogether 517 documents (51.7%) but could not be interpreted for 259 documents (ie. dimension info was successfully estimated for 49.9 % of the documents where this field was not empty).

-   Document size (area) info was obtained in the final preprocessed data for altogether 479 documents (48%). For the remaining documents, critical dimension information was not available or could not be interpreted: [List of entries where document surface could not be estimated](dataTable/data_table.html?path=../output.tables/physical_dimension_incomplete.csv)

-   Document gatherings info is originally available for 440 documents (44%), and further estimated up to 456 documents (46%) in the final preprocessed data.

-   Document height info is originally available for 39 documents (4%), and further estimated up to 479 documents (48%) in the final preprocessed data.

-   Document width info is originally available for 0 documents (0%), and further estimated up to 479 documents (48%) in the final preprocessed data.

These tables can be used to verify the accuracy of the conversions from the raw data to final estimates:

-   [Dimension conversions from raw data to final estimates](dataTable/data_table.html?path=../output.tables/conversions_physical_dimension.csv)

-   [Automated tests for dimension conversions](https://github.com/fennicahub/fennica/blob/master/inst/extdata/tests_dimension_polish.csv)

The estimated dimensions are based on the following auxiliary information sheets:

-   [Document dimension abbreviations](https://github.com/fennicahub/fennica/blob/master/inst/extdata/document_size_abbreviations.csv)

-   [Standard sheet size estimates](https://github.com/fennicahub/fennica/blob/master/inst/extdata/sheetsizes.csv)

-   [Document dimension estimates](https://github.com/fennicahub/fennica/blob/master/inst/extdata/documentdimensions.csv) (used when information is partially missing)

<<<<<<< HEAD
## Subset 1809-1917

-   [Accepted dimension info](dataTable/data_table.html?path=../output.tables/physical_dimensions_accepted_19.csv)
=======
>>>>>>> a4d6655935b2ac20c49fbee35e57fd74efbb1dc6

-   [Discarded dimension info](dataTable/data_table.html?path=../output.tables/physical_dimensions_discarded_19.csv)
