---
title : "Physical extent / pagecount"
hide-description: false
description: ""
---

```{r}
#| label = "source-index",
#| include = FALSE
source("init.R")
source("physical_extent.R")
```

MARC: [300a](https://www.loc.gov/marc/bibliographic/bd300.html)

Polish physical extent field: [physical_extent.R](https://github.com/fennicahub/fennica/blob/master/inst/examples/physical_extent.R)

Harmonize physical extent data function: [polish_physical_extent.R](https://github.com/fennicahub/fennica/blob/master/R/polish_physical_extent.R)

Render physical extent field: [physical_extent.qmd](https://github.com/fennicahub/fennica/blob/master/inst/examples/physical_extent.qmd)

* [Conversions from raw data to final page count estimates](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/physical_extent_accepted.csv)

* [Discarded entries](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/physical_extent_discarded.csv)

```{r}
#| include = FALSE
library(dplyr)
library(knitr)


df_pagecount %>%
  summarise(
    arabic_pages = sum(!is.na(arabic)),
    roman_pages = sum(!is.na(roman)),
    sheets = sum(!is.na(sheet)),
    plates = sum(!is.na(plate)),
    square_brackets = sum(!is.na(squarebracket)),
    multipliers = sum(!is.na(multiplier)),
    volume_count_info = sum(!is.na(volcount))
  ) %>%
  kable()
n_total <- nrow(df_pagecount)

pagecount_summary <- df_pagecount %>%
  summarise(
    documents = n(),
    pagecount_available = sum(!is.na(pagecount)),
    pagecount_missing = sum(is.na(pagecount)),
    pagecount_available_percent = round(100 * pagecount_available / documents, 1),
    min_pagecount = min(pagecount, na.rm = TRUE),
    max_pagecount = max(pagecount, na.rm = TRUE),
    volcount_available = sum(!is.na(volcount)),
    volcount_missing = sum(is.na(volcount))
  )

pagecount_summary %>%
  kable()
```
## Page counts

* Page count available for `r pagecount_summary$pagecount_available` documents in total (`r pagecount_summary$pagecount_available_percent`%).

* Page count missing for `r pagecount_summary$pagecount_missing` documents.

* Volume count available for `r pagecount_summary$volcount_available` documents.

* Volume count missing for `r pagecount_summary$volcount_missing` documents.

```{r}
#| include = FALSE
df_pagecount %>%
  summarise(
    arabic_pages = sum(!is.na(pagecount.arabic)),
    roman_pages = sum(!is.na(pagecount.roman)),
    sheets = sum(!is.na(pagecount.sheet)),
    plates = sum(!is.na(pagecount.plate)),
    square_brackets = sum(!is.na(pagecount.squarebracket)),
    multipliers = sum(!is.na(pagecount.multiplier)),
    volume_count_info = sum(!is.na(pagecount.volcount))
  ) %>%
  kable()
```

```{r}
#| include = FALSE
df_pagecount %>%
  mutate(
    volume_type = case_when(
      is.na(volcount) ~ "Missing volume count",
      volcount == 1 ~ "Single volume",
      volcount > 1 ~ "Multi-volume"
    )
  ) %>%
  group_by(volume_type) %>%
  summarise(
    documents = n(),
    mean_pagecount = round(mean(pagecount, na.rm = TRUE), 1),
    median_pagecount = median(pagecount, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  kable()
```



