---
title : "Physical extent / pagecount"
hide-description: false
description: ""
---

```{r}
#| label = "source-index",
#| include = FALSE, 
#| message = FALSE


source("init.R")
source("physical_extent.R")
```

MARC: [300a](https://www.loc.gov/marc/bibliographic/bd300.html)

Polish physical extent field: [physical_extent.R](https://github.com/fennicahub/fennica/blob/master/inst/examples/physical_extent.R)

Harmonize physical extent data function: [polish_physical_extent.R](https://github.com/fennicahub/fennica/blob/master/R/polish_physical_extent.R)

Render physical extent field: [physical_extent.qmd](https://github.com/fennicahub/fennica/blob/master/inst/examples/physical_extent.qmd)

* [Conversions from raw data to final page count estimates](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/physical_extent_accepted.csv)

* [Discarded entries](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/physical_extent_discarded.csv)

```{r}
#| include = FALSE, 
#| message = FALSE
#
pagecount_summary <- data.frame(
  total_documents = nrow(df.tmp),

  original_available = sum(!is.na(df.orig$physical_extent) & df.orig$physical_extent != ""),
  original_missing = sum(is.na(df.orig$physical_extent) | df.orig$physical_extent == ""),

  pagecount_available = sum(!is.na(df.tmp$pagecount)),
  pagecount_missing = sum(is.na(df.tmp$pagecount)),

  volcount_available = sum(!is.na(df.tmp$volcount)),
  volcount_missing = sum(is.na(df.tmp$volcount))
)

pagecount_summary <- pagecount_summary %>%
  mutate(
    original_available_percent = round(100 * original_available / total_documents, 1),
    original_missing_percent = round(100 * original_missing / total_documents, 1),
    pagecount_available_percent = round(100 * pagecount_available / total_documents, 1),
    pagecount_missing_percent = round(100 * pagecount_missing / total_documents, 1),
    volcount_available_percent = round(100 * volcount_available / total_documents, 1)
  )
```


## Page counts

- The original physical-extent field is available for `r pagecount_summary$original_available` documents (`r pagecount_summary$original_available_percent`%) and missing for `r pagecount_summary$original_missing` documents (`r pagecount_summary$original_missing_percent`%).

- A harmonized page-count estimate is available for `r pagecount_summary$pagecount_available` documents (`r pagecount_summary$pagecount_available_percent`%) and missing for `r pagecount_summary$pagecount_missing` documents (`r pagecount_summary$pagecount_missing_percent`%).

- Volume-count information is available for `r pagecount_summary$volcount_available` documents (`r pagecount_summary$volcount_available_percent`%) and missing for `r pagecount_summary$volcount_missing` documents.

```{r}
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| error = FALSE,

df_pagecount <- df.tmp %>%
  summarise(
    arabic_pages = sum(pagecount.arabic > 0, na.rm = TRUE),
    roman_pages = sum(pagecount.roman > 0, na.rm = TRUE),
    sheets = sum(pagecount.sheet > 0, na.rm = TRUE),
    plates = sum(pagecount.plate > 0, na.rm = TRUE),
    square_brackets = sum(pagecount.squarebracket > 0, na.rm = TRUE),
    multiplier_applied = sum(pagecount.multiplier > 1, na.rm = TRUE),
    volume_count_info = sum(!is.na(volcount)),
    parts_info = sum(!is.na(parts))
  )

kable(df_pagecount)
```

```{r}
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| error = FALSE,
df_volume_summary <- df.tmp %>%
  mutate(
    volume_type = case_when(
      is.na(volcount) ~ "Missing volume count",
      volcount == 1 ~ "Single volume",
      volcount > 1 ~ "Multi-volume"
    )
  ) %>%
  group_by(volume_type) %>%
  summarise(
    documents = n(),
    mean_pagecount = round(mean(pagecount, na.rm = TRUE), 1),
    median_pagecount = median(pagecount, na.rm = TRUE),
    .groups = "drop"
  )

kable(df_volume_summary)
```

```{r}
#| include = FALSE,
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| error = FALSE,
pagecount_conversion <- data.frame(
  original_available = sum(!is.na(df.orig$physical_extent) & df.orig$physical_extent != ""),

  successfully_converted = sum(
    !is.na(df.orig$physical_extent) &
    df.orig$physical_extent != "" &
    !is.na(df.tmp$pagecount)
  ),

  original_but_no_pagecount = sum(
    !is.na(df.orig$physical_extent) &
    df.orig$physical_extent != "" &
    is.na(df.tmp$pagecount)
  )
) %>%
  mutate(
    conversion_percent = round(
      100 * successfully_converted / original_available,
      1
    )
  )
```

Of records containing original physical-extent information, `r pagecount_conversion$successfully_converted` (`r pagecount_conversion$conversion_percent`%) yielded a harmonized page-count estimate, while `r pagecount_conversion$original_but_no_pagecount` records contained physical-extent information but did not yield a page-count estimate.

```{r}
#| label = "physext2",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| error = FALSE,
#| fig.width = 9,
#| fig.height = 6

df_pagecount_groups <- df.tmp %>%
  mutate(
    pagecount_group = case_when(
      is.na(pagecount) ~ "Missing",
      pagecount <= 10 ~ "1–10",
      pagecount <= 50 ~ "11–50",
      pagecount <= 100 ~ "51–100",
      pagecount <= 200 ~ "101–200",
      pagecount <= 300 ~ "201–300",
      pagecount <= 500 ~ "301–500",
      pagecount <= 1000 ~ "501–1,000",
      pagecount > 1000 ~ ">1,000"
    ),
    pagecount_group = factor(
      pagecount_group,
      levels = c(
        "1–10", "11–50", "51–100", "101–200",
        "201–300", "301–500", "501–1,000",
        ">1,000", "Missing"
      )
    )
  ) %>%
  count(pagecount_group) %>%
  mutate(
    percent = round(100 * n / sum(n), 1)
  )


f <- ggplot(
  df_pagecount_groups,
  aes(x = pagecount_group, y = n)
) +
  geom_col() +
  labs(
    x = "Estimated page count",
    y = "Number of documents",
    title = "Documents by estimated page count"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 1
    )
  )

print(f)
```

