```{r source-publication-place, include=FALSE, eval=knit_bookdown}
# Publication place field and derived country- and geoinformation
source("publication_place.R")
```

# Publication place preprocessing summary

 * `r length(unique(str_trim(unlist(strsplit(as.character(df$publication_place), ";")))))` [unique publication places](dataTable/data_table.html?path=../output.tables/publication_place_accepted.csv); available for `r sum(!is.na(df$publication_place))` documents (`r round(100*mean(!is.na(df$publication_place)))`%).
 * `r length(readLines(paste0("output.tables/publication_place_ambiguous.csv"))) - 1` [ambiguous publication places](dataTable/data_table.html?path=../output.tables/publication_place_ambiguous.csv); some of these can be possibly resolved by checking that the the [synonyme list](dataTable/data_table.html?path=../output.tables/PublicationPlaceSynonymes.csv) does not contain multiple versions of the final name (case sensitive). 
 * `r try(length(readLines(paste0("output.tables/publication_place_todo.csv"))))` [unknown place names](dataTable/data_table.html?path=../output.tables/publication_place_todo.csv) These terms do not map to any known place on the [synonyme list](dataTable/data_table.html?path=../output.tables/PublicationPlaceSynonymes.csv); either because they require further cleaning or have not yet been encountered in the analyses. Terms that are clearly not place names can be added to [stopwords](dataTable/data_table.html?path=../output.tables/stopwords_for_place.csv); borderline cases that are not accepted as place names can be added as NA on the [synonyme list](dataTable/data_table.html?path=../output.tables/PublicationPlaceSynonymes.csv).
 * `r length(readLines(paste0("output.tables/publication_place_discarded.csv"))) - 1` [discarded place names](dataTable/data_table.html?path=../output.tables/publication_place_discarded.csv) These terms are potential place names but with a closer check have been explicitly rejected on the [synonyme list](dataTable/data_table.html?path=../output.tables/PublicationPlaceSynonymes.csv)
 * [Conversions from the original to the accepted place names](dataTable/data_table.html?path=../output.tables/publication_place_conversion_nontrivial.csv) 
<!-- * [Unit tests for place names](https://github.com/COMHIS/fennica/blob/master/inst/extdata/tests_place.csv) are automatically checked during package build -->

Top-`r ntop` publication places are shown together with the number of documents.

```{r summaryplace, echo=FALSE, message=FALSE, warning=FALSE, error= FALSE, fig.width=9, fig.height=6}
p <- top_plot(df, "publication_place", ntop)
p <- p + ggtitle(paste("Top publication places"))
p <- p + scale_y_log10()
p <- p + ylab("Title count")
print(p)

p <- top_plot(df, "publication_country", ntop)
p <- p + ggtitle(paste("Top publication countries"))
p <- p + scale_y_log10()
p <- p + ylab("Title count")
print(p)
```


## Publication countries	

 * `r length(unique(df$publication_country))` [unique publication countries](dataTable/data_table.html?path=../output.tables/publication_country_accepted.csv); available for `r sum(!is.na(df$publication_country))` documents (`r round(100*mean(!is.na(df$publication_country)))`%).
 * `r length(na.omit(unique(subset(df, is.na(publication_country))$publication_place)))` [places with unknown publication country](dataTable/data_table.html?path=../output.tables/publication_place_missingcountry.csv) (`r round(100 * length(na.omit(unique(subset(df, is.na(publication_country))$publication_place))) / length(na.omit(unique(df$publication_place))), 1)`% of the unique places; can be added to [country mappings](dataTable/data_table.html?path=../output.tables/reg2country.csv))
 * `r length(readLines(paste0("output.tables/publication_country_ambiguous.csv"))) - 1` [potentially ambiguous region-country mappings](dataTable/data_table.html?path=../output.tables/publication_country_ambiguous.csv) (these may occur in the data in various synonymes and the country is not always clear when multiple countries have a similar place name; the default country is listed first). NOTE: possible improvements should not be done in this output summary but instead in the [country mapping file](dataTable/data_table.html?path=../output.tables/reg2country.csv).

```{r summaryplace3, echo=FALSE, results='asis'}
tab <- top(df, "publication_country", output = "data.frame", round = 1)
colnames(tab) <- c("Country", "Documents (n)", "Fraction (%)")
library(knitr)
kable(head(tab))
```


## Geocoordinates

 * `r round(100*mean(!is.na(df$latitude) & !is.na(df$longitude)), 1)`% of the documents were matched to geographic coordinates (based on COMHIS geomapping process).
 * `r length(unique(df$publication_place[(is.na(df$latitude))]))` unique places (`r round(100 * length(unique(df$publication_place[(is.na(df$latitude))]))/length(unique(df$publication_place)), 1)`% of all unique places and `r round(100 * mean(is.na(df$latitude) | is.na(df$longitude)), 2)`% of all documents) are missing geocoordinates. See [list of places missing geocoordinate information](output.tables/absentgeocoordinates.csv).
 

