---
title : "Publication time"
hide-description: false
description: ""
---

```{r}
#| label = "source-index",
#| include = FALSE
source("init.R")
source("publication_time.R")
```

MARC: [260c](https://www.loc.gov/marc/bibliographic/bd260.html)

The publication years section offers a comprehensive summary of the dataset's years of publication, providing anunderstanding of the temporal distribution of titles. The inclusion of links to uniquely accepted and discarded output tables adds a layer of transparency, allowing for detailed exploration of the refined and excluded data.

## Complete Data Overview

[Publication year conversions](dataTable/data_table.html?path=../output.tables/publication_time_conversion.csv)

[Publication year discarded](dataTable/data_table.html?path=../output.tables/publication_time_discarded.csv)

Publication years фку available for `r sum(!is.na(df_pub_time$publication_year))` documents (`r round(100*mean(!is.na(df_pub_time$publication_year)))`%). The publication years span is `r paste(range(na.omit(as.numeric(df_pub_time$publication_year))), collapse = "-")`.

## Subset Analysis: 1809-1917

[Publication year conversions](dataTable/data_table.html?path=../output.tables/publication_time_conversion_19.csv)

[Publication year discarded](dataTable/data_table.html?path=../output.tables/publication_time_discarded_19.csv)

### Title count per decade

A plot depicting title counts per decade from 1809 to 1917 enriches the analysis by visually capturing the trends and fluctuations in literary output over this historical period.

```{r}
#| label = "summarypublicationyear",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 8,
#| fig.height = 6


df2 <- df_pubtime19 %>% group_by(publication_decade) %>% filter(publication_decade < 2010) 
p <- ggplot(df2, aes(publication_decade)) +
     geom_bar() + scale_y_log10() +
     ggtitle("Title count timeline")
print(p)
```
