---
title: "Publisher"
hide-description: false
description: ""
---

```{r}
#| label = "source-index",
#| include = FALSE
source("init.R")
source("publisher.R")
```

MARC: [260b](https://www.loc.gov/marc/bibliographic/bd260.html)


## Complete Dataset Overview

-   `r length(unique(df$publisher))` [unique publishers](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/publisher_accepted.csv)

-   `r sum(!is.na(df$publisher))` documents have unambiguous publisher information (`r round(100*mean(!is.na(df$publisher)), 1)`%). This includes documents identified as self-published; the author name is used as the publisher in those cases (if known).

-   [Discarded publisher entries](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/publisher_discarded.csv)

-   [Conversions from original to final names](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/publisher_conversion_nontrivial.csv) (only non-trivial conversions shown)

## Subset Analysis: 1809-1917

-   `r length(unique(df_19$publisher))` [unique publishers](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/publisher_accepted_19.csv)

-   `r sum(!is.na(df_19$publisher))` documents have unambiguous publisher information (`r round(100*mean(!is.na(df_19$publisher)), 1)`%). This includes documents identified as self-published; the author name is used as the publisher in those cases (if known).

-   [Discarded publisher entries](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/publisher_discarded_19.csv)

The `r ntop` most common publishers from 1809 to 1917 are shown with the number of documents.

```{r}
#| label = "summarypublisher2",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 12,
#| fig.height = 9
p <- top_plot(df_19, "publisher", ntop)
p <- p + ggtitle(paste("Top publishers"))
p <- p + scale_y_log10()
p <- p + ylab("Documents")
print(p)
```
