---
title: "Signum"
hide-description: false
description: ""
---

```{r}
#| include = FALSE
source("init.R")
source("signum.R")
```

A signum data, also known as a call number, is a unique combination of numbers and letters employed to indicate the specific location of a book within a library. This data was verified and provided to us by the National Library of Finland.

## Complete Dataset Overview

[Unique accepted entries]: `r length(unique(df$signum_harmonized))`

Original documents with titles: `r sum(!is.na(df$signum_harmonized))` / `r nrow(df)` (`r round(100*mean(!is.na(df$signum_harmonized)), 1)`%)

Original documents with missing (NA) titles `r sum(is.na(df$signum_harmonized))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$signum_harmonized)), 1)`%)

[Signum accepted for the whole Fennica](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/output.tables/signum_accepted.csv)

[Signum discarded for the whole Fennica](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/signum_discarded.csv)

### Top-`r ntop` signum

```{r}
#| label = "summary_signum_table",
#| echo = FALSE,
#| warning = FALSE,
#| results = "asis"
x <- top(df$signum_harmonized, "signum_harmonized")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("Signum", "Entries (n)", "Fraction (%)")
kable(head(tab, 10))
```

## Subset Analysis: 1809-1917

Original documents with titles: `r sum(!is.na(df_19$signum_harmonized))` / `r nrow(df)` (`r round(100*mean(!is.na(df_19$signum_harmonized)), 1)`%)

Original documents with missing (NA) titles `r sum(is.na(df_19$signum_harmonized))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$signum_harmonized)), 1)`%)

[Signum accepted for 1809-1917](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/signum_accepted_19.csv)

[Signum discarded for 1809-1917](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/signum_discarded_19.csv)

### Top-`r ntop` signum for 1809-1917

```{r}
#| label = "summary_signum_table2",
#| echo = FALSE,
#| warning = FALSE,
#| results = "asis"
x <- top(df_19$signum_harmonized, "signum_harmonized")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("Signum", "Entries (n)", "Fraction (%)")
kable(head(tab, 10))
```

