--- 
title: "Uniform Title"
hide-description: false
description: ""
---

```{r}
#| label = "source-index",
#| include = FALSE
source("init.R")
source("title-.uniform.R")
```

## Complete Dataset Overview


* [Unique accepted entries](dataTable/data_table.html?path=../`r file_accepted`): `r length(unique(df[[field]]))`
* [Unique discarded entries in original data](dataTable/data_table.html?path=../`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)


## Subset Analysis: 1809-1917


* [Unique accepted entries](dataTable/data_table.html?path=../`r file_accepted`): `r length(unique(df_19[[field]]))`
* [Unique discarded entries in original data](dataTable/data_table.html?path=../`r file_discarded_19`) (excluding NA cases): `r as.vector(countLines(file_discarded_19) - 1)`


Top-`r ntop` titles and their title counts for 1809-1917 period.

```{r}
#| label = "summarytitle-title-uniform",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 8,
#| fig.height = 6
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df_19, "title_uniform", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```



