---
title : "Title"
hide-description: false
description: ""
---

```{r}
#| label = "source-index",
#| include = FALSE
source("init.R")
source("title.R")
```

MARC: [245a](https://www.loc.gov/marc/bibliographic/bd245.html)


## Complete Dataset Overview

[Unique accepted entries]: `r length(unique(df[[field]]))`

Original documents with titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)

Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)

[Unique discarded entries in original data](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/title_discarded.csv): `r as.vector(countLines(file_discarded) - 1)`

[Download title field harmonized dataset](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/title.csv)

### Top-`r ntop` titles

```{r}
#| label = "summary_title_table",
#| echo = FALSE,
#| results = "asis"
x <- top(df, "title")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("Title", "Entries (n)", "Fraction (%)")
kable(head(tab, 15))
```

### Top-`r ntop` titles for "Language material" content type 

In the Fennica dataset, language material makes up the majority of the content, comprising 91.6% of the entire dataset. This includes written texts, documents, books, articles, and any other content primarily composed of language. The remaining 8.4% consists of non-language material, such as maps, music, computer files, and other types of content that do not primarily rely on language. For a more detailed breakdown of the different types of content within the dataset, you can refer to [summaries of type of records in Fennica](https://fennica-fennica.rahtiapp.fi/content_type.html).


```{r}
#| label = "summary_title_table4",
#| echo = FALSE,
#| results = "asis"

#pick melindas for language material content types
df_lang_material <- df.orig %>%
  filter(type_of_record == "Language material") %>%
  select(melinda_id)

#filter language material melindas 
df_language_mat <- df %>%
  filter(melinda_id %in% df_lang_material$melinda_id)

x <- top(df_language_mat, "title")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("Title", "Entries (n)", "Fraction (%)")
kable(head(tab, 15))
```

## Subset Analysis: 1809-1917

[Unique accepted entries (1809-1917)](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/title_accepted_19.csv): `r length(unique(df_19[[field]]))`

Original documents with non-NA titles: `r sum(!is.na(df_19[[field]]))` / `r nrow(df_19)` (`r round(100*mean(!is.na(df_19[[field]])), 1)`%)

Original documents with missing (NA) titles `r sum(is.na(df_19[[field]]))` / `r nrow(df_19)` documents (`r round(100*mean(is.na(df_19[[field]])), 1)`%)


[Download title field harmonized dataset(1809-1917)](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/title_19.csv)

### Top-`r ntop` titles for years 1809-1917 

```{r}
#| label = "summary_title_table2",
#| echo = FALSE,
#| results = "asis"
x <- top(df_19, "title")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df_19)), 1))
colnames(tab) <- c("Title", "Entries (n)", "Fraction (%)")
kable(head(tab, 15))
```


### Top-`r ntop` titles for years 1809-1917 / "Language material" content type 

```{r}
#| label = "summary_title_table3",
#| echo = FALSE,
#| results = "asis"

#pick melindas for language material content types
df_lang_material <- df.orig %>%
  filter(type_of_record == "Language material") %>%
  select(melinda_id)

#filter language material melindas for 1809-1917 years 
df_19_language_mat <- df_19 %>%
  filter(melinda_id %in% df_lang_material$melinda_id)

x <- top(df_19_language_mat, "title")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df_19)), 1))
colnames(tab) <- c("Title", "Entries (n)", "Fraction (%)")
kable(head(tab, 15))
```