---
title : "Remainder of title"
hide-description: false
description: ""
---

```{r}
#| label = "source-index",
#| include = FALSE
source("init.R")
source("publication_time.R")
source("title_remainder.R")
```

MARC: [245b](https://www.loc.gov/marc/bibliographic/bd245.html)


## Complete Dataset Overview

[Unique accepted entries]: `r length(unique(df[[field]]))`

Original documents with title_remainders: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)

Original documents with missing (NA) title_remainders `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)

[Unique discarded entries in original data](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/title_remainder_discarded.csv): `r as.vector(countLines(file_discarded) - 1)`

[Download title_remainder field harmonized dataset](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/title_remainder.csv)

### Top-`r ntop` title_remainders

```{r}
#| label = "summary_title_remainder_table",
#| echo = FALSE,
#| results = "asis"
x <- top(df, "title_remainder")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("Remainder of title", "Entries (n)", "Fraction (%)")
kable(head(tab, 10))
```
### Top-`r ntop` remainders of title for "Language material" content type 

In the Fennica dataset, language material makes up the majority of the content, comprising 91.6% of the entire dataset. This includes written texts, documents, books, articles, and any other content primarily composed of language. The remaining 8.4% consists of non-language material, such as maps, music, computer files, and other types of content that do not primarily rely on language. For a more detailed breakdown of the different types of content within the dataset.

```{r}
#| label = "summary_title_remainder_table4",
#| echo = FALSE,
#| results = "asis"

#pick melindas for language material content types
df_lang_material <- df.orig %>%
  filter(type_of_record == "Language material") %>%
  select(melinda_id)

#filter language material melindas 
df_language_mat <- df %>%
  filter(melinda_id %in% df_lang_material$melinda_id)

x <- top(df_language_mat, "title_remainder")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("Remainder of Title", "Entries (n)", "Fraction (%)")
kable(head(tab, 10))
```
### Remainder of Title Length Over Time (1488-2020)

This plot visualizes the variation in title_remainder lengths across publication decades from 1488 to 2020. The title_remainder lengths range from  `r min(df$title_remainder_length, na.rm = TRUE)` to`r max(df$title_remainder_length, na.rm = TRUE)` , highlighting how the length of title_remainders has evolved over time.N = `r nrow(df)`.

```{r}
#| label = "summary_title_remainder_length_pic",
#| echo = FALSE,
#| warning = FALSE,
df$publication_decade <- df_pubtime$publication_decade

df2 <- df %>% 
  group_by(publication_decade) %>% 
  filter(publication_decade <= 2030) 
df2 <- df2 %>% 
  filter(!is.na(publication_decade) & !is.na(title_remainder_length))  # Remove NA values

ggplot(df2, aes(x = publication_decade, y = title_remainder_length)) +
  geom_point(alpha = 0.5, color = "#666666") +  # Scatter plot for individual points
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), color = "black", se = FALSE) + 
  scale_x_continuous(
    limits = c(1550, 2000),  
    breaks = seq(1550, 2000, by = 50),  
    labels = as.character(seq(1550, 2000, by = 50))
  ) +
  labs(x = "Publication Decade", y = "Remainder of Title Length") +
  theme_minimal()
```

### Remainder of Title Word Count Over Time (1488-2020)

This plot visualizes the variation in title_remainder word counts across publication decades from 1488 to 2020. The title_remainder lengths range from  `r min(df$title_remainder_word_count, na.rm = TRUE)` to`r max(df$title_remainder_word_count, na.rm = TRUE)` , highlighting how the length of title_remainders has evolved over time.N = `r nrow(df)`.

```{r}
#| label = "summary_title_remainder_word_count_pic",
#| echo = FALSE,
#| warning = FALSE,
df$publication_decade <- df_pubtime$publication_decade

df2 <- df %>% 
  group_by(publication_decade) %>% 
  filter(publication_decade <= 2030) 
df2 <- df2 %>% 
  filter(!is.na(publication_decade) & !is.na(title_remainder_word_count))  # Remove NA values

ggplot(df2, aes(x = publication_decade, y = title_remainder_word_count)) +
  geom_point(alpha = 0.5, color = "#666666") +  # Scatter plot for individual points
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), color = "black", se = FALSE) +  
  scale_x_continuous(
    limits = c(1550, 2000),  
    breaks = seq(1550, 2000, by = 50),  
    labels = as.character(seq(1550, 2000, by = 50))
  ) +
  labs(x = "Publication Decade", y = "Remainder of Title Word Count") +
  theme_minimal()
```

## Subset Analysis: 1809-1917

[Unique accepted entries (1809-1917)](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/title_remainder_accepted_19.csv): `r length(unique(df_19[[field]]))`

Original documents with non-NA title_remainders: `r sum(!is.na(df_19[[field]]))` / `r nrow(df_19)` (`r round(100*mean(!is.na(df_19[[field]])), 1)`%)

Original documents with missing (NA) title_remainders `r sum(is.na(df_19[[field]]))` / `r nrow(df_19)` documents (`r round(100*mean(is.na(df_19[[field]])), 1)`%)


[Download title_remainder field harmonized dataset(1809-1917)](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/title_remainder_19.csv)

### Top-`r ntop` title_remainders for years 1809-1917  

```{r}
#| label = "summary_title_remainder_remainder_table2",
#| echo = FALSE,
#| results = "asis"
x <- top(df_19, "title_remainder")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df_19)), 1))
colnames(tab) <- c("Remainder of title", "Entries (n)", "Fraction (%)")
kable(head(tab, 10))
```


### Top-`r ntop` title_remainders for years 1809-1917 period / "Language material" content type 

```{r}
#| label = "summary_title_remainder_remainder_table3",
#| echo = FALSE,
#| results = "asis"

#pick melindas for language material content types
df_lang_material <- df.orig %>%
  filter(type_of_record == "Language material") %>%
  select(melinda_id)

#filter language material melindas for 1809-1917 years 
df_19_language_mat <- df_19 %>%
  filter(melinda_id %in% df_lang_material$melinda_id)

x <- top(df_19_language_mat, "title_remainder")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df_19)), 1))
colnames(tab) <- c("Remainder of title", "Entries (n)", "Fraction (%)")
kable(head(tab, 10))
```

### Remainder of Title Length Over Time (1809-1917)
This plot visualizes the variation in title_remainder lengths across publication years from 1809 to 1917. The title_remainder lengths range from  `r min(df_19$title_remainder_length, na.rm = TRUE)` to`r max(df_19$title_remainder_length, na.rm = TRUE)`. N = `r nrow(df_19)`.

```{r}
#| label = "summary_title_remainder_length_pic1",
#| echo = FALSE,
#| warning = FALSE,
df_19$publication_year <- df_pubtime19$publication_year

df2 <- df_19 %>% 
  group_by(publication_year) %>% 
  filter(publication_year <= 1920) 
df2 <- df2 %>% 
  filter(!is.na(publication_year) & !is.na(title_remainder_length))  # Remove NA values

ggplot(df2, aes(x = publication_year, y = title_remainder_length)) +
  geom_point(alpha = 0.5, color = "#555") +  # Scatter plot for individual points
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), color = "black", se = FALSE) + 
  scale_x_continuous(
    limits = c(1810, 1920),  
    breaks = seq(1810, 1920, by = 20),  
    labels = as.character(seq(1810, 1920, by = 20))
  ) +
  labs(x = "Publication Year", y = "Remainder of Title Length") +
  theme_minimal()
```

### Remainder of Title Word Count (1809-1917)
This plot visualizes the variation in title_remainder lengths across publication years from 1809 to 1917. The title_remainder lengths range from  `r min(df_19$title_remainder_word_count, na.rm = TRUE)` to`r max(df_19$title_remainder_word_count, na.rm = TRUE)`. N = `r nrow(df_19)`.

```{r}
#| label = "summary_title_remainder_word_count_pic1",
#| echo = FALSE,
#| warning = FALSE,
df_19$publication_year <- df_pubtime19$publication_year

df2 <- df_19 %>% 
  group_by(publication_year) %>% 
  filter(publication_year <= 1920) 
df2 <- df2 %>% 
  filter(!is.na(publication_year) & !is.na(title_remainder_word_count))  # Remove NA values

ggplot(df2, aes(x = publication_year, y = title_remainder_word_count)) +
  geom_point(alpha = 0.5, color = "#555") +  # Scatter plot for individual points
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), color = "black", se = FALSE) + 
  scale_x_continuous(
    limits = c(1810, 1920),  
    breaks = seq(1810, 1920, by = 20),  
    labels = as.character(seq(1810, 1920, by = 20))
  ) +
  labs(x = "Publication Year", y = "Remainder of Title Word Count") +
  theme_minimal()
```