# Title 

```{r}
#| label = "source-index",
#| include = FALSE
source("init.R")
source("title.R")
```

MARC: [245a,b](https://www.loc.gov/marc/bibliographic/bd245.html)


## Complete Dataset Overview

[Unique accepted entries](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/title_accepted.csv): `r length(unique(df[[field]]))`

Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)

Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)

[Download title field harmonized dataset](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/title.csv)

### Top-`r ntop` titles and their title counts 

```{r}
#| label = "summary_title_table",
#| echo = FALSE,
#| results = "asis"
x <- top(df, "title")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("Title", "Entries (n)", "Fraction (%)")
kable(head(tab, 20))
```


## Subset Analysis: 1809-1917

[Unique accepted entries (1809-1917)](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/title_accepted_19.csv): `r length(unique(df_19[[field]]))`

Original documents with non-NA titles: `r sum(!is.na(df_19[[field]]))` / `r nrow(df_19)` (`r round(100*mean(!is.na(df_19[[field]])), 1)`%)

Original documents with missing (NA) titles `r sum(is.na(df_19[[field]]))` / `r nrow(df_19)` documents (`r round(100*mean(is.na(df_19[[field]])), 1)`%)

[Download title field harmonized dataset](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/title_19.csv)

### Top-`r ntop` titles and their title counts for the 1809-1917 period for every content type 

```{r}
#| label = "summary_title_table2",
#| echo = FALSE,
#| results = "asis"
x <- top(df_19, "title")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df_19)), 1))
colnames(tab) <- c("Title", "Entries (n)", "Fraction (%)")
kable(head(tab, 20))
```


### Top-`r ntop` titles and their title counts for the 1809-1917 period for "Language material" content type 

```{r}
#| label = "summary_title_table3",
#| echo = FALSE,
#| results = "asis"

#pick melindas for language material content types
df_lang_material <- df.orig %>%
  filter(type_of_record == "Language material") %>%
  select(melinda_id)

#filter language material melindas for 1809-1917 years 
df_19_language_mat <- df_19 %>%
  filter(melinda_id %in% df_lang_material$melinda_id)

x <- top(df_19_language_mat, "title")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df_19)), 1))
colnames(tab) <- c("Title", "Entries (n)", "Fraction (%)")
kable(head(tab, 20))
```




