---
title: "UDC"
hide-description: false
description: ""
---

```{r}
#| include = FALSE
source("init.R")
source("melindas_19.R")
source("udk.R")

```

MARC: [080a](https://www.loc.gov/marc/bibliographic/bd080.html)

## Complete Dataset Overview

[Unique UDC](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/UDK_accepted.csv):  `r length(unique(unlist(strsplit(as.character(df$converted), ";"))))-1` 

`r sum((df$udk_count > 1), na.rm = TRUE)` single-UDC entries (`r round(100 * mean(df$udk_count > 1, na.omit = TRUE), 2)`%)

`r sum(df$udk_count == 1, na.rm = TRUE)` multi-UDC entries (`r round(100 * mean(df$udk_count == 1, na.omit = TRUE), 2)`%)

[Unrecognized UDC](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/udk_discarded.csv):  `r length(unique(df.tmp1$udk))`

[Download UDC harmonized dataset](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/UDK.csv)

Language codes are from [The National Library of Finland](https://www.kiwi.fi/display/Kansallisbibliografiapalvelut/Monografia-aineiston+UDK-luokituskaavio); new custom abbreviations can be added in [this table](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/udk_monografia.csv).

```{r}
#| label = "summaryudk1",
#| echo = FALSE,
#| results = "asis"
x <- top(df.tmp2, "explanation")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("UDC", "Entries (n)", "Fraction (%)")
kable(head(tab, 20))
```
```{r}
#| label = "summaryudk2",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 19,
#| fig.height = 16
top_plot(df.tmp2, "explanation", ntop = ntop, log10 = TRUE) + labs(y = "Entries (n)")
```

## Subset Analysis: 1809-1917

[Unique UDC (1809-1917)](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/UDK_accepted_19.csv): `r length(unique(unlist(strsplit(as.character(df_19$converted), ";"))))-1`

UDC is available for `r sum(!is.na(df$cleaned))` documents  (`r round(100*mean(!is.na(df$cleaned)))`%). 

`r sum((df_19$udk_count > 1), na.rm = TRUE)` single-UDC entries (`r round(100 * mean(df_19$udk_count > 1, na.omit = TRUE), 2)`%)

`r sum(df_19$udk_count == 1, na.rm = TRUE)` multi-UDC entries (`r round(100 * mean(df_19$udk_count == 1, na.omit = TRUE), 2)`%)

[Unrecognized UDC (1809-1917)](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/UDK_discarded_19.csv): `r length(unique(df.tmp1_19$udk))`

[Download UDC harmonized dataset (1809-1917)](https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/UDK_19.csv)

### Top languages for 1809-1917

Number of titles assigned with each UDC (top-10). For a complete list, see [accepted UDC (1809-1917)](dataTable/data_table.html?path=https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/output.tables/UDK_accepted_19.csv).

```{r}
#| label = "summaryudk3",
#| echo = FALSE,
#| results = "asis"
x <- top(df.tmp2_19, "explanation")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("UDC", "Entries (n)", "Fraction (%)")
kable(head(tab, 20))
```

Title count per language (including multi-language documents; note the log10 scale):

```{r}
#| label = "summaryudk4",
#| echo = FALSE,
#| message = FALSE,
#| warning = FALSE,
#| fig.width = 19,
#| fig.height = 16
top_plot(df.tmp2_19, "explanation", ntop = ntop, log10 = TRUE) + labs(y = "Entries (n)")
```
