---
title: "Genre and publishing metadata: exploratory association tests and probabilistic modeling"
format: html
execute:
  echo: true
  warning: false
  message: false
---

# Introduction

This Quarto notebook documents a step-by-step workflow for assessing whether **genre** is associated with selected bibliographic metadata variables before fitting a full multivariable model. The response variable is **genre**, and the predictors are **gender**, **language**, **publication_place**, and **publisher_size** (large/medium/small). All variables are categorical.

The workflow is intentionally staged. First, simple descriptive summaries and association tests are used to evaluate whether relationships are present at all. Next, models are introduced only after basic structure has been established. The final stage estimates genre probabilities under a Bayesian framework, enabling probabilistic interpretation and uncertainty quantification.

Criteria: books published in Finland, Sweden or Russia in 1809-1917.
Genre (outcome)	Nominal categorical (K>2)
Gender	Categorical
Language	Categorical
Publication place	Categorical (20 cities)
Publisher size	Categorical (3 levels)


Gender	male vs female
Language	Finnish vs Swedish
Publisher size	small / medium / large
Place	19 dummies (reference = largest city)

multinomial logistic regression for each k 
P(genre=k∣gender, language, place, publisher)
# Data and setup

## Packages

```{r}
#| message: FALSE
#| warning: FALSE

library(dplyr)
library(tidyr)
library(stringr)
library(janitor)     # tabyl()
library(ggplot2) 
library(nnet)
library(forcats)
```


## Load the data
```{r}
#| message: FALSE
#| warning: FALSE
# # Download the csv file
url <- "https://a3s.fi/swift/v1/AUTH_3c0ccb602fa24298a6fe3ae224ca022f/fennica-container/harmonized/books_19th.tsv"

df <- read.table(
  file = url, 
  sep = "\t",
  header = TRUE,
  colClasses = "character",
  fileEncoding = "UTF-8",
  quote = "\"",
  comment.char = "",
  stringsAsFactors = FALSE
)

head(df, 10)
```


## Cross-tabs and proportions

```{r}
df <- df %>%
mutate(
gender = factor(gender_primary, levels = c("male", "female"))
)

df <- df %>%
  mutate(
    profession_primary = trimws(sub(",.*", "", author_profession))
  )

df$profession_primary <- fct_lump_n(
  factor(df$profession_primary),
  n = 10,
  other_level = "Other"
)
```


### Genre X Gender
```{r}
tab_gender <- janitor::tabyl(df, genre, gender)
tab_gender
janitor::adorn_percentages(tab_gender, "row") %>% janitor::adorn_pct_formatting()
```
```{r}
tab_language <- janitor::tabyl(df, genre, profession_primary)
tab_language
janitor::adorn_percentages(tab_language, "row") %>% janitor::adorn_pct_formatting()
```




```{r}
ggplot(df, aes(x = gender, fill = genre)) +
geom_bar(position = "fill") +
labs(y = "Proportion", x = "Gender", fill = "Genre") +
theme_minimal()
```

```{r}
ggplot(df, aes(x = profession_primary, fill = genre)) +
  geom_bar(position = "fill") +
  labs(y = "Proportion", x = "", fill = "Genre") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 50, vjust = 0.5, hjust = 1)
  )

```



# multinomial linear regression


```{r}

df$gender      <- fct_explicit_na(factor(df$gender), na_level = "Unknown")
df$profession <- fct_explicit_na(factor(df$profession_primary), na_level = "Unknown")



model_freq <- multinom(
  genre ~ gender + profession,
  data = df
)

summary(model_freq)
```

```{r}
RRR <- exp(coef(model_freq))
RRR
```